### 2021-07-22 paper/paper.tex
add draft of paper

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
\renewcommand{\baselinestretch}{1.1} 
%
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{ulem}
% \usepackage{geometry}
% \usepackage{marginnote}

% Fix link colors
\hypersetup{
    colorlinks = true,
    linkcolor=red,
    citecolor=red,
    urlcolor=blue,
    linktocpage % so that page numbers are clickable in toc
}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\newcommand{\TG}[1]{\noindent{\color{blue}[\textsc{From Tristan:} #1]}\xspace}
\newcommand{\Ali}[1]{\noindent{\color{green}[\textsc{From Ali:} #1]}\xspace}
\newcommand{\GK}[1]{\noindent{\color{purple}[\textsc{From Greg:} #1]}\xspace}
\newcommand{\YC}[1]{\noindent{\color{orange}[\textsc{From Yohan:} #1]}\xspace}
\newcommand{\anonymous}[1]{***\xspace}

\lstdefinestyle{customC}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  xleftmargin=\parindent,
  language=C,
  showstringspaces=false,
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\bfseries\color[rgb]{0.580, 0.000, 0.827},
  %{purple!40!lightgray},
  commentstyle=\textit{\color{green!40!black}},
  identifierstyle=\bfseries\color{cyan!75!black},
  stringstyle=\color{orange},
  deletekeywords={double,float},
  classoffset=1, % starting new class
  otherkeywords={double,float},
  morekeywords={double,float},
  keywordstyle=\bfseries\color{green!55!black},
  classoffset=0
}

\begin{document}

\title{Comparing tool variability and numerical variability in fMRI analyses}

\author{Ali Salari$^1$, Co-authors$^2$, Tristan Glatard$^1$}

\authorrunning{Salari et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.

\institute{$^1$ Anonymous Organization1\\
  $^2$ Anonymous Organization2\\ **@******.***}

\institute{$^1$ Department of Computer Science and Software Engineering, Concordia University\\
  $^2$ Co-authors Organization\\  Montréal, QC, Canada}

\maketitle              % typeset the header of the contribution

\begin{abstract}
abstract\dots

%  \keywords{Computational reproducibility  \and Neuroimaging pipelines \and Monte-Carlo arithmetic.}
\end{abstract}

\section{Introduction}

\begin{description}
  \item[$\bullet$ ] Methodological choice can influence the final determining areas of brain activation. This opens so results flexibility~\cite{bowring2019exploring}.

  \item[$\bullet$ ] We presented a framework that can investigate the numerical instability of the pipelines based on Monte-Carlo arithmetic
                    by creating a Fuzzy environment, so that instrument mathematical functions implemented in mathematical system libraries (libmath).

  \item[$\bullet$ ] In this paper, we aim to answer the questions 1) how the fMRI analyses are numerically stable?
                    2) how the numerical variability is in comparison with the tool variability?
\end{description}

\section{Methodology}

\subsection{libmath Fuzzy System}

\begin{description}
  \item[$\bullet$ ] libmath Fuzzy allows you to study the numerical stability of tools and pipelines. 
  \item[$\bullet$ ] It is based on MCA perturbations so that applies slight noise on floating-point operations.
  \item[$\bullet$ ] It does not need source code modification or recompilation, and simply works using the Linux LD\_PRELOAD environment variable.
  \item[$\bullet$ ] The library call interposition technique enables us to assess the tools that are dynamically linked to the mathematical library.
\end{description}

\subsection{fMRI analyses \& Dataset}

\begin{description}
  \item[$\bullet$ ] We replicate the fMRI analyses used in~\cite{bowring2019exploring} using the three most popular packages 
                    for fMRI data processing including FSL, AFNI, and SPM.

  \item[$\bullet$ ] The functional fMRI studies have been chosen for reanalysis with the publicly available data repositories.
                    The used dataset is available at https://openneuro.org/datasets/ds000001.

  \item[$\bullet$ ] For the ds000001 study, 16 healthy adult subjects participated in a balloon analogue risk task over three scanning sessions.
                    This analysis consists of several common processes. A full description of each analysis is included in~\cite{bowring2019exploring}.

  \item[$\bullet$ ] In the original study, a number of preprocessing steps such as motion correction, segmentation, brain extraction, and registration 
                    were applied in all of the analyses to ensure that results from each software package could be compared objectively.

\end{description}

\subsection{Data processing}

\begin{description}
  \item[$\bullet$ Containerization] building Docker images for three of the most popular software packages in neuroimaging including FSL, AFNI, and SPM.
                  We ensured that the software versions and all the requisites for running analyses used in all experiments 
                  are identical to the original study.

  \item[$\bullet$ Between tool variability] check and confirm that obtained results are perfectly replicated comparing to the original study.

  \item[$\bullet$ Numerical variability] running 3 MCA samples in each condition using the Fuzzy libmath environment. 
                  The conditions could be varying between tools, software versions, or the instrumented precisions. 
    \begin{description}
      \item[$\ast$ Varying precisions] a) only perturbing maximum precisions (OS-level), p=53 bits for double-precision and p=24 bits for single-precision.
                                       This would help to compare uncertainty between tool variability and numerical instability at the OS-level. 
                                       b) perturbing precisions from p=53 bits to p=1 bits by steps of 2 iteratively. 
                                       This would help to find the most similar uncertainty distribution between tool variability and numerical variability.
    \end{description}

  \item[$\bullet$ Image types] the fMRI result images that we are investigating are thresholded and unthresholded of the group level activation maps.

  \item[$\bullet$ Comparison metrics] comparing variabilities statistically by computing correlations between T-statistic values, Dice coefficient, 
                  and the number of significant digits.

  \item[$\bullet$ Configuration table] showing the detail of the configurations used for replicating the fMRI results.
\end{description}

\section{Results}

\begin{description}
  \item[$\bullet$ Figure 1: Showing results visually] make an overlay of 3 samples of un/thresholded activations maps for each condition.

  \item[$\bullet$ Table 1: Summary of statistics] mean differences and correlations between T-statistic values for each pair of results in each condition.

  \item[$\bullet$ Figure 2: Bland-Altman] comparing unthresholded group level maps, 2D histogram, computed each pair of tools in both conditions.
                  Measures similarity between statistic values.
                  This plots difference between the statistic values (y-axis) and the mean statistic value (x-axis) for all voxels.

  \item[$\bullet$ Figure 3: Dice Coefficient] comparing the thresholded group level maps computed each pair of tools in both conditions.
                  Measures the overlap of voxels which assess the spatial similarity between activated maps.

  \item[$\bullet$ Figure 4: Significant digits] comparing the distribution of SD across 3 samples (unthresholded images) for each condition. 
                  Find and show results at the precision that creates the most similar numerical uncertainty with between tool variability.  
\end{description}

% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
% are responsible for disparities between pair of images.

\section{Conclusion \& Discussion}
conclusions\dots
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{biblio}

\end{document}

### 2021-08-23 paper/paper.tex
Add result figures in paper

@@
 \usepackage{graphicx}
-\usepackage{xcolor}
+\usepackage[table]{xcolor}
 \usepackage{xspace}
@@
 \usepackage{ulem}
+
+\usepackage[para,online,flushleft]{threeparttable}
+\usepackage{booktabs}
+\usepackage{multirow}
 % \usepackage{geometry}
@@
                   and the number of significant digits.    
+% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
+% are responsible for disparities between pair of images.
 
@@
 
+% \subsection{Comparing between tool and numerical variability}
 \begin{description}
-  \item[$\bullet$ Figure 1: Showing results visually] make an overlay of 3 samples of un/thresholded activations maps for each condition.
+  \item[$\bullet$ Table 1: Summary of statistics] mean and standard deviation of the differences, and correlations 
+                  between t-statistic values for each pair of results in each condition.
 
-  \item[$\bullet$ Table 1: Summary of statistics] mean differences and correlations between T-statistic values for each pair of results in each condition.
+  \item[$\bullet$ Figure 1 and 2: Surface maps of std.] comparing standard deviations on surface map template (ICBM-152)
+                  computed between pair of software (tool variation), and different Fuzzy samples on each software (numerical variation).
+                  Figure 1 shows results for group level thresholded t-statistics, and 
+                  Figure 2 shows maps for group level unthresholded t values. The numerical variation
 
-  \item[$\bullet$ Figure 2: Bland-Altman] comparing unthresholded group level maps, 2D histogram, computed each pair of tools in both conditions.
-                  Measures similarity between statistic values.
-                  This plots difference between the statistic values (y-axis) and the mean statistic value (x-axis) for all voxels.
+  \item[$\bullet$ Figure 3 and 4: Dice Coefficients] comparing region-by-region Dice coefficients of group level thresholded maps between tools.
+                  This measures the overlap of voxels which assess the spatial similarity between activated maps.
+                  In bewteen tool similarity, the Dice values correspond to the mean of Dices computed for each pair of that specific tool,
+                  for example, Dice value for SPM is calculated by averaging Dices in SPM-AFNI and SPM-FSL pairs.
+                  Similarly, Dice values are computed between three Fuzzy samples obtained from each tool in numerical variation.
+                  Figure 3 shows bar plots of Dices for negative and positive activated regions.
+                  Figure 4 shows surface maps of Dices for the activated regions.
 
-  \item[$\bullet$ Figure 3: Dice Coefficient] comparing the thresholded group level maps computed each pair of tools in both conditions.
-                  Measures the overlap of voxels which assess the spatial similarity between activated maps.
+  % \item[$\bullet$ Figure 2: Bland-Altman] comparing unthresholded group level maps, 2D histogram, computed each pair of tools in both conditions.
+  % Measures similarity between statistic values.
+  % This plots difference between the statistic values (y-axis) and the mean statistic value (x-axis) for all voxels.
 
-  \item[$\bullet$ Figure 4: Significant digits] comparing the distribution of SD across 3 samples (unthresholded images) for each condition. 
-                  Find and show results at the precision that creates the most similar numerical uncertainty with between tool variability.  
+  % \item[$\bullet$ Figure 4: Significant digits] comparing the distribution of SD across 3 samples (unthresholded images) for each condition. 
+  %                 Find and show results at the precision that creates the most similar numerical uncertainty with between tool variability.
+
 \end{description}
 
-% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
-% are responsible for disparities between pair of images.
+%%%%%%%%%% Summary of statstics %%%%%%%%
+\setlength{\tabcolsep}{10pt}
+\begin{table}[h]
+    \centering
+    \begin{tabular}{cccc|ccc}
+        \toprule
+        \multirow{2}{*}{} & \multicolumn{3}{c}{Thresholded} & \multicolumn{3}{c}{Unthresholded} \\
+        \cmidrule{2-4} \cmidrule{5-7} \\
+        {} & Mean diff. & Std. diff. & Corr. & Mean diff. & Std. diff. & Corr.  \\
+        \midrule
+        \rowcolor{lightgray}
+        FSL vs. SPM          &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        \rowcolor{lightgray}
+        FSL vs. AFNI         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        \rowcolor{lightgray}
+        AFNI vs. SPM         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        Fuzzy SPM            &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        Fuzzy FSL            &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        Fuzzy AFNI           &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        \bottomrule
+    \end{tabular}
+    \caption{Summary of t-statistics mean and standard deviation of differences and correlations of each pair of tools.}
+    \label{table:pipeline-stats}
+\end{table}
+
+%%%%%%%%%% STD. of Thresh %%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-stdmaps1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-mca-thresh(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-stdmaps2}
+  \end{subfigure}
+  \caption{Surface maps of standard deviation of thresholded t-statistics.}
+  \label{fig:thresh-stdmaps}
+  \end{minipage}}
+\end{figure}
+
+%%%%%%%%%% STD. of Unthresh %%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-tool(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-stdmaps1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-mca1(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-stdmaps2}
+  \end{subfigure}
+  \caption{Surface maps of standard deviation of unthresholded t-statistics.}
+  \label{fig:thresh-stdmaps}
+  \end{minipage}}
+\end{figure}
+
+%%%%%%%%%% Bar plots of Dices from Thresh %%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+
+      \begin{subfigure}[t]{0.5\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{figures/spm-exc_set_file.png}
+        \label{fig:fsl-dices}
+      \end{subfigure}
+      \hfill
+      \begin{subfigure}[t]{0.5\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{figures/spm-exc_set_file_neg.png}
+        \label{fig:spm-dices}
+      \end{subfigure}    
+  \hfill
+    \begin{subfigure}[t]{0.5\linewidth}
+      \centering
+      \includegraphics[width=\linewidth]{figures/fsl-exc_set_file.png}
+      \label{fig:fsl-dices}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.5\linewidth}
+      \centering
+      \includegraphics[width=\linewidth]{figures/fsl-exc_set_file_neg.png}
+      \label{fig:spm-dices}
+    \end{subfigure}  
+  \hfill
+    \begin{subfigure}[t]{0.5\linewidth}
+      \centering
+      \includegraphics[width=\linewidth]{figures/afni-exc_set_file.png}
+      \label{fig:fsl-dices}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{0.5\linewidth}
+      \centering
+      \includegraphics[width=\linewidth]{figures/afni-exc_set_file_neg.png}
+      \label{fig:spm-dices}
+    \end{subfigure}
+
+  \caption{Bar plots of Dice coefficients of activated regions between pair of tools (BT) and fuzzy samples (FL) from the thresholded t-statistics.
+  Right plots show the negative maps, and left plots show the positive maps. 
+  Region numbers correspond to the 180 areas of cortical parcellation (HCP-MMP1.0)~\cite{Glasser-nature}.}
+  \label{fig:unthresh-dices}
+  \end{minipage}}
+\end{figure}
+
+%%%%%%%%%% Surf maps of Dices from Thresh %%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-SPM(dice).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-stdmaps1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-FSL(dice).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-stdmaps1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-AFNI(dice).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-stdmaps2}
+  \end{subfigure}
+  \caption{Surface maps of Dice coefficients of thresholded t-statistics region-by-region.}
+  \label{fig:unthresh-dices}
+  \end{minipage}}
+\end{figure}
+
+% \subsection{The precision that Fuzzy FSL tool can simulate the between tool variations}
+% \begin{description}
+%   \item[$\bullet$ Figure 5:] Repeat Fig 1-4 for the results of Fuzzy FSL on the precision that simulate mostly betwen tool varions.
+% \end{description}
 

### 2021-09-14 paper/paper.tex
update result section

--- 2021-07-22 paper/paper.tex
@@
 
-\begin{description}
-  \item[$\bullet$ Figure 1: Showing results visually] make an overlay of 3 samples of un/thresholded activations maps for each condition.
+All scripts and results to create the figures in this section are available on GitHub repository
+in \url{https://github.com/ali4006/fuzzy-neurotools}.
+Replication of all analyses was visually assessed to be the same as the original findings.
+We ensured that fMRI analyses were processed successfully.
+In this section, we call the cross-software variation and numerical variation,
+between tool (BT) and within tool (WT) variability, respectively. 
+The within tool variability shows results among different fuzzy libmath
+samples for the specific version of the tools, and it is not within tool versions.
 
-  \item[$\bullet$ Table 1: Summary of statistics] mean differences and correlations between T-statistic values for each pair of results in each condition.
+A summary of the statistic values from the group-level (un)thresholded T-statistics is conducted in
+Table~\ref{table:pipeline-stats}.
+The variability between images in each condition was measured using mean and standard deviation of absolute differences,
+and Pearson correlation coefficient.
+% Overally, we see that values in between tools are comparable to values in within tool results.
+% The distribution of the pairwise differences in T-statistic..
+% The standard deviations exceeding 2.0 in magnitude..
+% Pairwise correlations ranged from 0.43 to 0.7 for within tool variability..
 
-  \item[$\bullet$ Figure 2: Bland-Altman] comparing unthresholded group level maps, 2D histogram, computed each pair of tools in both conditions.
-                  Measures similarity between statistic values.
-                  This plots difference between the statistic values (y-axis) and the mean statistic value (x-axis) for all voxels.
+%%%%%%%%%% Summary of statstics %%%%%%%%
+\setlength{\tabcolsep}{10pt}
+\begin{table}[h]
+    \centering
+    \begin{tabular}{cccc|ccc}
+        \toprule
+        \multirow{2}{*}{} & \multicolumn{3}{c}{Thresholded} & \multicolumn{3}{c}{Unthresholded} \\
+        \cmidrule{2-4} \cmidrule{5-7} \\
+        {} & Mean diff. & Std. diff. & Corr. & Mean diff. & Std. diff. & Corr.  \\
+        \midrule
+        \rowcolor{lightgray}
+        FSL vs. SPM          &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        \rowcolor{lightgray}
+        FSL vs. AFNI         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        \rowcolor{lightgray}
+        AFNI vs. SPM         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        Fuzzy FSL and SPM    &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        Fuzzy FSL and AFNI   &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        Fuzzy AFNI and SPM   &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        \bottomrule
+    \end{tabular}
+    \caption{Summary of T-statistics mean and standard deviation of differences and correlations of each pair of tools.}
+    \label{table:pipeline-stats}
+\end{table}
 
-  \item[$\bullet$ Figure 3: Dice Coefficient] comparing the thresholded group level maps computed each pair of tools in both conditions.
-                  Measures the overlap of voxels which assess the spatial similarity between activated maps.
+% \subsection{Comparing disparity in BT and WT}
+\subsection{Spatial localization of disparity in BT and WT}
+% Fig message: showing the magnitude of differences and correlated area
+% Fig message: showing numerically dependent parts of the brain
 
-  \item[$\bullet$ Figure 4: Significant digits] comparing the distribution of SD across 3 samples (unthresholded images) for each condition. 
-                  Find and show results at the precision that creates the most similar numerical uncertainty with between tool variability.  
-\end{description}
+Comparisons of standard deviations between results in WT and BT
+on the brain surface are shown in Figure~\ref{fig:thresh-varmaps} and Figure~\ref{fig:unthresh-varmaps}.
+Figure~\ref{fig:thresh-varmaps} shows maps for group-level thresholded T-statistics, and
+Figure~\ref{fig:unthresh-varmaps} shows maps for group-level unthresholded T-statistic values.
+While we observe substantial variations in BT (average std. dev. $\approx$ 1.5),
+the order of magnitude of variations in WT is much lower (average std. dev. $\approx$ 0.5),
+as was anticipated. However, numerical variability is still significant in WT results.
+Moreover, we see the same order of magnitude in WT variations compared to BT variations
+in some regions in the thresholded images.
+For instance, we see the temporal lobe in anterior view for almost all pairs and the fusiform gyrus in inferior view
+for the pairs of FSL-SPM and FSL-AFNI in Figure~\ref{fig:unthresh-varmaps}
+that are perfectly replicated using the numerical perturbations. 
+Although the unthresholded statistic maps from our analyses also show a different magnitude of
+the order of variations in both conditions, std. dev. ranges from $\approx$ 0.12 to $\approx$ 0.5 on average in WT and BT;
+there is great comparability between results.
+Generally, we obtained more uncertainty on thresholded results, probably due to different thresholding
+methods used in different tools.
+This can raise further investigations on the thresholding techniques toward stability.
 
-% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
-% are responsible for disparities between pair of images.
+%%%%%%%%%% Var. of Thresh %%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-tool(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-varmaps1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-fuzzy(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-varmaps2}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-ratio(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-ratio}
+  \end{subfigure}
+  \caption{Surface maps of standard deviation of thresholded T-statistics. First and second rows show
+  results on between-tool and within-tool results, respectively. Third row represents the ratio of differences
+  in between and within tools so that brigher areas indicate more similar order of magnitude of variations in both conditions,
+  and vise versa for the darkder regions.}
+  \label{fig:thresh-varmaps}
+  \end{minipage}}
+\end{figure}
+
+%%%%%%%%%% Var. of Unthresh %%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-tool(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:unthresh-varmaps1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-fuzzy(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:unthresh-varmaps2}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-ratio(std).pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:unthresh-ratio}
+  \end{subfigure}
+  \caption{Surface maps of standard deviation of unthresholded T-statistics.}
+  \label{fig:unthresh-varmaps}
+  \end{minipage}}
+\end{figure}
+
+The scatter plot in Figure~\ref{fig:correlations} represents the correlation of standard deviation between conditions.
+We found three major clusters, including upper, lower, and identity.
+The identity cluster corresponds to the correlations between 0.9 and 1.1; the upper cluster shows correlations where BT $\approx$ 0;
+and the lower cluster represents correlations where WT $\approx$ 0.
+The identity area is also represented on the surface maps in the second row in Figure~\ref{fig:correlations}.
+This figure shows the spatial localization of the parts of the brain that are numerically dependent.
+We can see regions such as the occipital lobe in the posterior view and the frontal lobe in the interior view 
+that are highly correlated in BT and WT results.
+This refines the presented results in Figure~\ref{fig:unthresh-varmaps},
+which indicates how spatial variabilities are simulated using numerical perturbations in some areas.
+% Spatial localization of significant activation in the thresholded images also varied across software packages.
+% Moreover, results show that pair of FSL-SPM has the least correlation of variability in within tool and between tool.
+% This will implies that ... which can help for further investigations.
+
+%%%%%%%%%% Corr. plot of tstats%%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+    \begin{subfigure}[t]{\linewidth}
+      \centering
+      \includegraphics[width=\linewidth]{figures/std-corr-unthresh-plot.png}
+      %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \label{fig:unthresh-corrplot}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{\linewidth}
+      \centering
+      \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-tool(corr).pdf}
+      %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \label{fig:unthresh-corrmaps}
+    \end{subfigure}
+  \caption{Correlation of variability in BT and WT variations in unthresholded maps. First row plots the correlations
+  voxel by voxel, which is highlighted with different colors for three major clusters including upper cluster (purple color),
+  lower cluster (yellow color), and correlated cluster (green color) which are mapped on surface in the second row.}
+  \label{fig:correlations}
+  \end{minipage}}
+\end{figure}
+
+\subsection{Region-based similarity in BT and WT}
+In Figure~\ref{fig:dice-thresh}, we compare region-by-region Dice coefficients of
+the group level thresholded maps in BT and WT for all pairs of software packages.
+This measures the overlap of voxels which assess the spatial similarity between activated maps.
+In WT similarity, the Dice values correspond to the average of Dices computed among three
+Fuzzy samples for each pair of tools.
+Results show that the similarity between tool variations is correlated with the numerical variations,
+which implies that similar anatomical regions are activated, and also the topology of the activation patterns
+is preserved between results from two types of variations.
+% This correlation highly increases when normalizing Dice scores by the region sizes.
+% which reduces the effect of small regions.
+
+% This implies that region by region similarity between two type of variations are preserved.
+% Results show that similar anatomical regions are activated in both conditions. 
+% This plot suggests the similar topologies of the activation patterns in each condition.
+% The average of Dice scores range from to 
+% FSL-AFNI variations has the most similarity correlations which means that the results of these two tools are more \dots
+
+% In response to the out of border activated voxels can say:
+% This is likely due to the fact that SPM consistently had the smallest analysis mask out of the three packages,
+% while FSL had the largest. Number of activated voxels prove this fact.
+
+%%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \centering
+  \includegraphics[width=\textwidth]{figures/dices_corr.png}
+  \caption{Correlation of Dice coefficients of activated regions between pair of tools and fuzzy samples
+  from the thresholded T-statistics. Different pairs are illustrated in different colors. 
+  Regression lines are normalized by the region sizes on the right plot.
+  Regions correspond to the 360 areas of cortical parcellation (HCP-MMP1.0)~\cite{Glasser-nature}.}
+  \label{fig:dice-thresh}
+\end{minipage}}
+\end{figure}
+
+% %%%%%%%%%% Summary of statstics %%%%%%%%
+% \setlength{\tabcolsep}{10pt}
+% \begin{table}[h]
+%     \centering
+%     \begin{tabular}{cccc}
+%         \toprule
+%         {} & Mean diff. & Std. diff. & Corr. \\
+%         \midrule
+%         \rowcolor{lightgray}
+%         FSL vs. SPM          &  0.242       & 0.534      & 0.599  \\
+%         \rowcolor{lightgray}
+%         FSL vs. AFNI         &  0.302       & 0.674      & 0.591  \\
+%         \rowcolor{lightgray}
+%         AFNI vs. SPM         &  0.254       & 0.659      & 0.562  \\
+%         Fuzzy FSL and SPM    &  0.00       & 0.00      & 0.00  \\
+%         Fuzzy FSL and AFNI   &  0.00       & 0.00      & 0.00  \\
+%         Fuzzy AFNI and SPM   &  0.00       & 0.00      & 0.00  \\
+%         \bottomrule
+%     \end{tabular}
+%     \caption{Summary of T-statistics mean and standard deviation of differences and correlation coefficients
+%     across three sets of results in two conditions.}
+%     \label{table:pipeline-stats}
+% \end{table}
+
+% \subsection{The precision that Fuzzy FSL tool can simulate the between tool variations}
+% \begin{description}
+%   \item[$\bullet$ Figure 5:] Repeat Fig 1-4 for the results of Fuzzy FSL on the precision that simulate mostly betwen tool varions.
+% \end{description}
 
 \section{Conclusion \& Discussion}
-conclusions\dots
+% In this study, we represented the magnitude of differences in between tool and within tool results.
+% Also we showed the numerically dependent parts of the brain, and explained how between tool variations
+% are correlated with numerical variability. Moreover, we indicated the spatial similarity between results so that
+% numerical perturbations preserve the topology of the avtivation patterns across all three sets of packages in both conditions.
+
+% Further studies can be evaluating the numerical stabilities within tool by focusing on the particular parts of 
+% the pipeline that has been identified as the mian sources of variations in~\cite{bowring2019exploring}.
+
 %

### 2021-09-22 paper/paper.tex
Update figures

@@
 
-\subsection{libmath Fuzzy System}
+\subsection{Fuzzy libmath environment}
 
-\begin{description}
-  \item[$\bullet$ ] libmath Fuzzy allows you to study the numerical stability of tools and pipelines. 
-  \item[$\bullet$ ] It is based on MCA perturbations so that applies slight noise on floating-point operations.
-  \item[$\bullet$ ] It does not need source code modification or recompilation, and simply works using the Linux LD\_PRELOAD environment variable.
-  \item[$\bullet$ ] The library call interposition technique enables us to assess the tools that are dynamically linked to the mathematical library.
-\end{description}
+% To simulate the machine level uncertainty, we used the method introduced in~\cite{FL-MICAII-paper} called Fuzzy libmath (FL).
+% FL uses Monte Carlo Arithmetic (MCA) to introduce a controlled amounts of noise in the floating-point operations,
+% which models floating-point rounding and catasrophic cancellation errors.
+% This is automated using Verificarlo tool~\cite{denis2015verificarlo} that implements MCA in the compilation time.
+% The perturbation is introduced in a given number of least-significant bits so that
+% the number of bits in the mantissa that will not be perturbed is defined as the virtual precision.​
+
+% % MCA models floating-point roundoff and cancellations errors through random
+% % perturbations, allowing for the estimation of error distributions from
+% % independent random result samples. MCA simulates computations at a given
+% % \emph{virtual precision} using the following perturbation:
+% % \begin{equation} \label{eq:mca_inexact}
+% %   inexact(x) = x + 2^{e_x-t}\xi
+% %   \label{mcadefinition}
+% % \end{equation}
+% % where $e_x$ is the exponent in the floating-point representation of $x$,
+% % $t$ is the virtual precision and $\xi$ is a random uniform variable of
+% % $(-\frac{1}{2}, \frac{1}{2})$.
+
+% % MCA allows for three perturbation modes: Random Rounding (RR) introduces the
+% % perturbation in function outputs, simulating roundoff errors; Precision Bounding
+% % (PB) introduces the perturbation in function operands, allowing for the
+% % detection of catastrophic cancellations; and, Full MCA combines RR and PB,
+% % resulting in the following perturbation:
+% % \begin{equation} \label{eq:mca_modes}
+% %   mca\_mode(x \circ y) = inexact_{RR}(  inexact_{PB}(x) \circ inexact_{PB}(y) )
+% % \end{equation}
+
+% % We instrumented the GNU mathematical library with MCA using
+% % Verificarlo~\cite{denis2015verificarlo}, a tool that (1) uses the Clang
+% % compiler to generate an LLVM (\url{http://llvm.org}) Intermediate
+% % Representation (IR) of the source code, (2) replaces floating-point operations
+% % in the IR by a call to the Verificarlo API, and (3) compiles the modified IR to
+% % an executable using LLVM. The perturbation applied by the Verificarlo API
+% % can be configured at runtime, for instance to change the virtual
+% % precision applied to single- and double-precision floating-point values.
+
+% In this framework, mathematical functions embeded in the operating system GNU mathematical library (libmath)
+% are targeted to be instrumented.
+% It instrument the functions by wrapping them so that only the output of the original functions be perturbed
+% instead of input or their implementation.
+% This is achieved by adding a floating-point zero to the output of the original function which results into perturbations.
+% Script~\ref{script1} shows an example of this wrapping for the log function.
+% This functionality helps to avoid of some issues in deterministic arithmetics like producing results out of the function definition.
+
+% % To simulate OS updates, we introduce random perturbations in the GNU
+% % mathematical library, the main mathematical library in GNU/Linux systems.
+% % Instrumenting mathematical libraries with MCA raises a number of issues as
+% % many functions assume deterministic arithmetic. For instance, applying random
+% % perturbations around a discontinuity or within piecewise approximations
+% % results in large variations and a total loss of significance that are not
+% % relevant in our context. Therefore, we have applied MCA to proxy
+% % mathematical functions wrapping those in the original library, such that only
+% % the outputs of the original functions were perturbed but not their inputs or
+% % the implementations themselves. This technique allows us to control the
+% % magnitude of the perturbation as perceived by the application.
+
+% \lstset{
+%   language=C,                % choose the language of the code
+%   numbers=left,                   % where to put the line-numbers
+%   stepnumber=1,                   % the step between two line-numbers.        
+%   numbersep=5pt,                  % how far the line-numbers are from the code
+%   backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
+%   showspaces=false,               % show spaces adding particular underscores
+%   showstringspaces=false,         % underline spaces within strings
+%   showtabs=false,                 % show tabs within strings adding particular underscores
+%   tabsize=2,                      % sets default tabsize to 2 spaces
+%   captionpos=b,                   % sets the caption-position to bottom
+%   breaklines=true,                % sets automatic line breaking
+%   breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
+% %  title=\lstname,                 % show the filename of files included with \lstinputlisting;
+% }
+% \lstinputlisting{wrapper.c}
+% %\lstinputlisting{wrapper2.c}
+
+% The instrumented math functions so called ``fuzzy libmath", is loaded in the pipeline using LD\_PRELOAD, a Linux mechanism
+% to force load a shared library into an executable. ​
+% As a result, functions defined in fuzzy libmath transparently overload the original ones without the need to modify or
+% recompile the analysis pipeline.​
+% Also, this technique allows measuring the effect of numerical noise by running a program multiple times.​
+% It is important to review the software dependencies of the pipelines to be sure that are involved with the same library that
+% we arep erturbing.
+
+% % The resulting MCA-instrumented mathematical library, ``fuzzy libmath" (FL), is
+% % loaded in the pipeline using \texttt{LD\_PRELOAD}, a Linux mechanism to
+% % force-load a shared library into an executable. As a result, functions defined in fuzzy libmath
+% % transparently overload the original ones without the need to modify
+% % or recompile the analysis pipeline. Fuzzy libmath functions call the original
+% % functions through \texttt{dlsym}, a function that returns the memory address of
+% % a symbol. To trigger MCA instrumentation, a floating-point zero is added to the
+% % output of the original function and the result of this sum is perturbed and
+% % returned.
+
+% % \begin{description}
+% %   \item[$\bullet$ ] libmath Fuzzy allows you to study the numerical stability of tools and pipelines. 
+% %   \item[$\bullet$ ] It is based on MCA perturbations so that applies slight noise on floating-point operations.
+% %   \item[$\bullet$ ] It does not need source code modification or recompilation, and simply works using the Linux LD\_PRELOAD environment variable.
+% %   \item[$\bullet$ ] The library call interposition technique enables us to assess the tools that are dynamically linked to the mathematical library.
+% % \end{description}
 
@@
 
-\begin{description}
-  \item[$\bullet$ ] We replicate the fMRI analyses used in~\cite{bowring2019exploring} using the three most popular packages 
-                    for fMRI data processing including FSL, AFNI, and SPM.
-
-  \item[$\bullet$ ] The functional fMRI studies have been chosen for reanalysis with the publicly available data repositories.
-                    The used dataset is available at https://openneuro.org/datasets/ds000001.
-
-  \item[$\bullet$ ] For the ds000001 study, 16 healthy adult subjects participated in a balloon analogue risk task over three scanning sessions.
-                    This analysis consists of several common processes. A full description of each analysis is included in~\cite{bowring2019exploring}.
-
-  \item[$\bullet$ ] In the original study, a number of preprocessing steps such as motion correction, segmentation, brain extraction, and registration 
-                    were applied in all of the analyses to ensure that results from each software package could be compared objectively.
-
-\end{description}
+% We replicate the fMRI analysis (ds000001 study) used in~\cite{bowring2019exploring} with the publicly available
+% data repository in~\href{https://openneuro.org/datasets/ds000001}{OpenNeuro}
+% using the three most popular packages for fMRI data processing including FSL, AFNI, and SPM. 
+% We selected this publication to replicate the fMRI analysis because it is an state of the art study
+% which compares between tool variability, and included all the sources and dataset available
+% so that we can easility reanalyse tests using Fuzzy framework.
+% A full description of the procedure of analysis is included in~\cite{bowring2019exploring,schonberg2012decreasing};
+% we give a brief overview of the pipeline processes in this section.
+% In this study, 16 healthy adult subjects participated in the balloon analogue risk task to measure risk-taking behavior
+% over three scanning sessions.
+% %The analysis was scripted using three different tools so that 
+% In the original study, a number of preprocessing steps which are widely accepted within the community
+% such as motion correction, segmentation, brain extraction, and registration 
+% were applied in all of the analyses to ensure that results from each software package could be compared objectively.
+% % The steps that are taken in the procedure of analysis for each tool is specified in table~\ref{table:fmri-steps}.
+% The analysis includes preprocessing, first-level, and second-level steps (Table~\ref{table:fmri-steps}) in all three software\dots
 
@@
 
-\begin{description}
-  \item[$\bullet$ Containerization] building Docker images for three of the most popular software packages in neuroimaging including FSL, AFNI, and SPM.
-                  We ensured that the software versions and all the requisites for running analyses used in all experiments 
-                  are identical to the original study.
+% The fMRI analysis pipeline was processed using three of the most popular software packages in neuroimaging
+% including FSL (version 5.0.10), AFNI (version 18.1.09), and SPM (version SPM12, r7771) on Octave (version 5.2).
+% The analyses were conducted on the same operating system, CentOS 7.3.
+% We ensured that the software versions and all the requisites for running analyses used in all experiments 
+% are similar to the original study, and were encapsulated in Docker images.
+% We could replicate results of the original study except for AFNI with slightly differences due to the parallelization\dots
+% We also used SPM/Octave instead of Matlab to be able to run analysis in HPC and also perturb mathmetical functions
+% because Matlab has no dependencies on the GNU mathematical library, and it uses its libraries\dots
 
-  \item[$\bullet$ Between tool variability] check and confirm that obtained results are perfectly replicated comparing to the original study.
+% In addition, we processed the same pipeline analyses with the same configurations in Fuzzy libmath environment
+% to capture the numerical variability results. 
+% We only perturbed the maximum precisions to compare uncertainty between tool variability and numerical instability at the level of OS.
+% For this purpose, we instrumented to the virtual precision (t) of 53 bits for double-precision variable,
+% and 24 bits for single-precision variable. We generated three Fuzzy samples in these precisions to match the number of tool samples.
 
-  \item[$\bullet$ Numerical variability] running 3 MCA samples in each condition using the Fuzzy libmath environment. 
-                  The conditions could be varying between tools, software versions, or the instrumented precisions. 
-    \begin{description}
-      \item[$\ast$ Varying precisions] a) only perturbing maximum precisions (OS-level), p=53 bits for double-precision and p=24 bits for single-precision.
-                                       This would help to compare uncertainty between tool variability and numerical instability at the OS-level. 
-                                       b) perturbing precisions from p=53 bits to p=1 bits by steps of 2 iteratively. 
-                                       This would help to find the most similar uncertainty distribution between tool variability and numerical variability.
-    \end{description}
+% We compare variability between (un)thresholded of group-level activation maps.
+% We statistically compute standard deviations between T-statistic values in the pair of tools.
+% We calculate standard deviations between fuzzy samples as the square root of summation of variances between Fuzzy samples in each tool.
+% We then compare the correlation of changes in both conditions.
+% Moreover, we compute region-by-region Dice coefficients for the thresholded maps for the all pairs of tools.
+% This measures the overlap of voxels which assess the spatial similarity between activated maps.
+% The Dice values between Fuzzy samples correspond to the average of Dices computed among three Fuzzy samples for each pair of tools.
+% We then compare the correlation of Dice scores which normalized by the region sizes in both conditions.
 
-  \item[$\bullet$ Image types] the fMRI result images that we are investigating are thresholded and unthresholded of the group level activation maps.
-
-  \item[$\bullet$ Comparison metrics] comparing variabilities statistically by computing correlations between T-statistic values, Dice coefficient, 
-                  and the number of significant digits.    
-% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
-% are responsible for disparities between pair of images.
-
-  \item[$\bullet$ Configuration table] showing the detail of the configurations used for replicating the fMRI results.
-\end{description}
+% % EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
+% % are responsible for disparities between pair of images.
 
@@
 Table~\ref{table:pipeline-stats}.
-The variability between images in each condition was measured using mean and standard deviation of absolute differences,
-and Pearson correlation coefficient.
+The variability between pair of images in each condition was measured using the mean and standard deviation of absolute differences.
 % Overally, we see that values in between tools are comparable to values in within tool results.
@@
     \centering
-    \begin{tabular}{cccc|ccc}
+    \begin{tabular}{ccc|cc}
         \toprule
-        \multirow{2}{*}{} & \multicolumn{3}{c}{Thresholded} & \multicolumn{3}{c}{Unthresholded} \\
-        \cmidrule{2-4} \cmidrule{5-7} \\
-        {} & Mean diff. & Std. diff. & Corr. & Mean diff. & Std. diff. & Corr.  \\
+        \multirow{2}{*}{} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c}{Unthresholded} \\
+        \cmidrule{2-3} \cmidrule{4-5} \\
+        {} & Mean diff. & Std. diff. & Mean diff. & Std. diff. \\
         \midrule
         \rowcolor{lightgray}
-        FSL vs. SPM          &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        FSL vs. SPM          &  0.043       & 1.282      & 0.242     & 0.443  \\
         \rowcolor{lightgray}
-        FSL vs. AFNI         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        FSL vs. AFNI         &  0.099       & 1.548      & 0.302     & 0.547  \\
         \rowcolor{lightgray}
-        AFNI vs. SPM         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
-        Fuzzy FSL and SPM    &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
-        Fuzzy FSL and AFNI   &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
-        Fuzzy AFNI and SPM   &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        AFNI vs. SPM         &  0.079       & 1.475      & 0.254     & 0.608  \\
+        Fuzzy FSL and SPM    &  0.005       & 0.358      & 0.030     & 0.099  \\
+        Fuzzy FSL and AFNI   &  0.011       & 0.475      & 0.038     & 0.155  \\
+        Fuzzy AFNI and SPM   &  0.011       & 0.458      & 0.033     & 0.144  \\
         \bottomrule
     \end{tabular}
-    \caption{Summary of T-statistics mean and standard deviation of differences and correlations of each pair of tools.}
+    \caption{Summary of T-statistics mean and standard deviation of differences for each pair of tools.}
     \label{table:pipeline-stats}
@@
 
+%Fig 1,3
 Comparisons of standard deviations between results in WT and BT
@@
 
-%%%%%%%%%% Var. of Thresh %%%%%%%%
-\begin{figure}[b]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-tool(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:thresh-varmaps1}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-fuzzy(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:thresh-varmaps2}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-ratio(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:thresh-ratio}
-  \end{subfigure}
-  \caption{Surface maps of standard deviation of thresholded T-statistics. First and second rows show
-  results on between-tool and within-tool results, respectively. Third row represents the ratio of differences
-  in between and within tools so that brigher areas indicate more similar order of magnitude of variations in both conditions,
-  and vise versa for the darkder regions.}
-  \label{fig:thresh-varmaps}
-  \end{minipage}}
-\end{figure}
-
-%%%%%%%%%% Var. of Unthresh %%%%%%%%
-\begin{figure}[b]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-tool(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:unthresh-varmaps1}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-fuzzy(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:unthresh-varmaps2}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-ratio(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:unthresh-ratio}
-  \end{subfigure}
-  \caption{Surface maps of standard deviation of unthresholded T-statistics.}
-  \label{fig:unthresh-varmaps}
-  \end{minipage}}
-\end{figure}
-
-The scatter plot in Figure~\ref{fig:correlations} represents the correlation of standard deviation between conditions.
-We found three major clusters, including upper, lower, and identity.
-The identity cluster corresponds to the correlations between 0.9 and 1.1; the upper cluster shows correlations where BT $\approx$ 0;
-and the lower cluster represents correlations where WT $\approx$ 0.
-The identity area is also represented on the surface maps in the second row in Figure~\ref{fig:correlations}.
-This figure shows the spatial localization of the parts of the brain that are numerically dependent.
-We can see regions such as the occipital lobe in the posterior view and the frontal lobe in the interior view 
-that are highly correlated in BT and WT results.
-This refines the presented results in Figure~\ref{fig:unthresh-varmaps},
-which indicates how spatial variabilities are simulated using numerical perturbations in some areas.
-% Spatial localization of significant activation in the thresholded images also varied across software packages.
-% Moreover, results show that pair of FSL-SPM has the least correlation of variability in within tool and between tool.
-% This will implies that ... which can help for further investigations.
-
-%%%%%%%%%% Corr. plot of tstats%%%%%%%%
-\begin{figure}[b]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-    \begin{subfigure}[t]{\linewidth}
-      \centering
-      \includegraphics[width=\linewidth]{figures/std-corr-unthresh-plot.png}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \label{fig:unthresh-corrplot}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{\linewidth}
-      \centering
-      \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-tool(corr).pdf}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \label{fig:unthresh-corrmaps}
-    \end{subfigure}
-  \caption{Correlation of variability in BT and WT variations in unthresholded maps. First row plots the correlations
-  voxel by voxel, which is highlighted with different colors for three major clusters including upper cluster (purple color),
-  lower cluster (yellow color), and correlated cluster (green color) which are mapped on surface in the second row.}
-  \label{fig:correlations}
-  \end{minipage}}
-\end{figure}
-
-\subsection{Region-based similarity in BT and WT}
+% Fig2
 In Figure~\ref{fig:dice-thresh}, we compare region-by-region Dice coefficients of
 the group level thresholded maps in BT and WT for all pairs of software packages.
-This measures the overlap of voxels which assess the spatial similarity between activated maps.
-In WT similarity, the Dice values correspond to the average of Dices computed among three
-Fuzzy samples for each pair of tools.
 Results show that the similarity between tool variations is correlated with the numerical variations,
@@
 
+% Fig4
+The scatter plot in Figure~\ref{fig:correlations} represents the correlation of standard deviation between conditions.
+We found three major clusters, including upper, lower, and identity.
+The identity cluster corresponds to the correlations between 0.9 and 1.1; the upper cluster shows correlations where BT $\approx$ 0;
+and the lower cluster represents correlations where WT $\approx$ 0.
+The identity area is also represented on the surface maps in the second row in Figure~\ref{fig:correlations}.
+This figure shows the spatial localization of the parts of the brain that are numerically dependent.
+We can see regions such as the occipital lobe in the posterior view and the frontal lobe in the interior view 
+that are highly correlated in BT and WT results.
+This refines the presented results in Figure~\ref{fig:unthresh-varmaps},
+which indicates how spatial variabilities are simulated using numerical perturbations in some areas.
+% Spatial localization of significant activation in the thresholded images also varied across software packages.
+% Moreover, results show that pair of FSL-SPM has the least correlation of variability in within tool and between tool.
+% This will implies that ... which can help for further investigations.
+
+% Mentioning P-values as well.
+% Percentage of voxels in each cluster of Fig4
+% fsl-spm
+% Fraction of green: %9.9
+% Fraction of purple: %0.7
+
+% fsl-afni
+% Fraction of green: %17.5
+% Fraction of purple: %0.6
+
+% afni-spm
+% Fraction of green: %13.9
+% Fraction of purple: %0.5
+
+%%%%%%%%%% Var. of Thresh %%%%%%%%
+\begin{figure}[ht]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/plots/bt-wt-thresh-std.pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-varmaps1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/plots/ratio-thresh-std.pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:thresh-ratiomaps}
+  \end{subfigure}
+  \caption{Maps of standard deviation of thresholded T-statistics. First and second rows show
+  maps on between-tool and within-tool results, respectively. Third row represents the ratio of differences
+  in between and within tools.}
+  % so that bright blue areas indicate more similar order of magnitude of variations in both conditions,
+  %and vise versa for the darkder regions.}
+  \label{fig:thresh-varmaps}
+  \end{minipage}}
+\end{figure}
+
 %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
@@
   from the thresholded T-statistics. Different pairs are illustrated in different colors. 
-  Regression lines are normalized by the region sizes on the right plot.
   Regions correspond to the 360 areas of cortical parcellation (HCP-MMP1.0)~\cite{Glasser-nature}.}
@@
 
-% %%%%%%%%%% Summary of statstics %%%%%%%%
-% \setlength{\tabcolsep}{10pt}
-% \begin{table}[h]
-%     \centering
-%     \begin{tabular}{cccc}
-%         \toprule
-%         {} & Mean diff. & Std. diff. & Corr. \\
-%         \midrule
-%         \rowcolor{lightgray}
-%         FSL vs. SPM          &  0.242       & 0.534      & 0.599  \\
-%         \rowcolor{lightgray}
-%         FSL vs. AFNI         &  0.302       & 0.674      & 0.591  \\
-%         \rowcolor{lightgray}
-%         AFNI vs. SPM         &  0.254       & 0.659      & 0.562  \\
-%         Fuzzy FSL and SPM    &  0.00       & 0.00      & 0.00  \\
-%         Fuzzy FSL and AFNI   &  0.00       & 0.00      & 0.00  \\
-%         Fuzzy AFNI and SPM   &  0.00       & 0.00      & 0.00  \\
-%         \bottomrule
-%     \end{tabular}
-%     \caption{Summary of T-statistics mean and standard deviation of differences and correlation coefficients
-%     across three sets of results in two conditions.}
-%     \label{table:pipeline-stats}
-% \end{table}
+%%%%%%%%%% Var. of Thresh %%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/plots/bt-wt-unthresh-std.pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:unthresh-varmaps1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/plots/ratio-unthresh-std.pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \label{fig:unthresh-ratiomaps}
+  \end{subfigure}
+  \caption{Maps of standard deviation of unthresholded T-statistics. First and second rows show
+  maps on between-tool and within-tool results, respectively. Third row represents the ratio of differences
+  in between and within tools.}
+  \label{fig:unthresh-varmaps}
+  \end{minipage}}
+\end{figure}
+
+%%%%%%%%%% Corr. plot of tstats%%%%%%%%
+\begin{figure}[b]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+    \begin{subfigure}[t]{\linewidth}
+      \centering
+      \includegraphics[width=\linewidth]{figures/std-corr-unthresh-plot.png}
+      %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \label{fig:unthresh-corrplot}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{\linewidth}
+      \centering
+      \includegraphics[width=\linewidth]{figures/plots/corr-unthresh-std.pdf}
+      %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \label{fig:unthresh-corrmaps}
+    \end{subfigure}
+    \caption{Correlation of variability in between-tool and within-tool variations in unthresholded maps. First row plots the correlations
+  voxel by voxel, which is highlighted with different colors for two major clusters including upper cluster (purple color) and
+  correlated cluster (green color) which are mapped on the brain in the second row.}
+  \label{fig:correlations}
+  \end{minipage}}
+\end{figure}
 

### 2021-09-22 computs.py

@@ -1,3 +1,5 @@
+#!/usr/bin/env python3
+
 from nibabel.processing import resample_from_to
 import scipy
 import scipy.spatial
@@ -11,7 +13,7 @@ import pickle as pkl
 import inspect
 import os
 from nilearn.image import math_img
-import seaborn as sns
+#import seaborn as sns
 import pandas as pd
 from mpl_toolkits.axes_grid1 import make_axes_locatable
 from lib import bland_altman
@@ -24,32 +26,33 @@ from statistics import mean
 def compute_var(f1, f2, file_name, f3=None):
     # Compute std. between tool image samples
     f1 = nib.load(f1)
-    #f1_mask = set_zero_to_nan(f1)
     f2 = nib.load(f2)
-    #f2_mask = set_zero_to_nan(f2)
-    #bg_ = np.logical_and(np.isnan(f1_mask.get_fdata()), np.isnan(f2_mask.get_fdata()))
     img_concat = nib.funcs.concat_images([f1, f2], check_affines=True, axis=None)
     img_std = np.std(img_concat.get_fdata(), axis=3)
+    # Extract background
+    # f1_mask = set_zero_to_nan(f1)
+    # f2_mask = set_zero_to_nan(f2)
+    # bg_ = np.logical_and(np.isnan(f1_mask.get_fdata()), np.isnan(f2_mask.get_fdata()))
 
     # Compute variance between fuzzy image samples
     if f3 is not None:
-        f3 = nib.load(f3)
-        #f3_mask = set_zero_to_nan(f3)
-        #bg_ = np.logical_and(np.isnan(f1_mask.get_fdata()), np.isnan(f2_mask.get_fdata()), np.isnan(f3_mask.get_fdata()))
+        # f3 = nib.load(f3)
+        # f3_mask = set_zero_to_nan(f3)
+        # bg_ = np.logical_and(np.isnan(f1_mask.get_fdata()), np.isnan(f2_mask.get_fdata()), np.isnan(f3_mask.get_fdata()))
         img_concat = nib.funcs.concat_images([f1, f2, f3], check_affines=True, axis=None)
         img_var = np.var(img_concat.get_fdata(), axis=3)
         # set background voxels as nan to not display later
-        #img_var[bg_] = np.nan
+        # img_var[bg_] = np.nan
         nft_img = nib.Nifti1Image(img_var, f1.affine, header=f1.header)
[…]

### 2021-09-23 paper/paper.tex
Update paper format

--- 2021-09-14 paper/paper.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\documentclass[runningheads]{llncs}
-\renewcommand{\baselinestretch}{1.1} 
-%
+ \documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+%\usepackage{hyphenat}
+\usepackage[ruled,vlined]{algorithm2e}
+\usepackage{amsmath}
+\usepackage{xspace}
+\usepackage[binary-units=true]{siunitx}
+\usepackage{ulem}
+%\usepackage{censor}
+\usepackage[table]{xcolor}
 \usepackage{graphicx}
-\usepackage[table]{xcolor}
-\usepackage{xspace}
 \usepackage{hyperref}
+\usepackage{tabularx}
+
 \usepackage{subcaption}
-\usepackage{listings}
-\usepackage{ulem}
-
-\usepackage[para,online,flushleft]{threeparttable}
 \usepackage{booktabs}
 \usepackage{multirow}
-% \usepackage{geometry}
-% \usepackage{marginnote}
+\usepackage{listings}
 
-% Fix link colors
 \hypersetup{
-    colorlinks = true,
-    linkcolor=red,
-    citecolor=red,
-    urlcolor=blue,
-    linktocpage % so that page numbers are clickable in toc
-}
+    colorlinks=true,
+    linkcolor=black,
+    citecolor=blue,
+    filecolor=black,
+    urlcolor=blue}
 
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-\newcommand{\TG}[1]{\noindent{\color{blue}[\textsc{From Tristan:} #1]}\xspace}
-\newcommand{\Ali}[1]{\noindent{\color{green}[\textsc{From Ali:} #1]}\xspace}
-\newcommand{\GK}[1]{\noindent{\color{purple}[\textsc{From Greg:} #1]}\xspace}
-\newcommand{\YC}[1]{\noindent{\color{orange}[\textsc{From Yohan:} #1]}\xspace}
-\newcommand{\anonymous}[1]{***\xspace}
-
-\lstdefinestyle{customC}{
-  belowcaptionskip=1\baselineskip,
-  breaklines=true,
-  xleftmargin=\parindent,
-  language=C,
-  showstringspaces=false,
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\bfseries\color[rgb]{0.580, 0.000, 0.827},
-  %{purple!40!lightgray},
-  commentstyle=\textit{\color{green!40!black}},
-  identifierstyle=\bfseries\color{cyan!75!black},
-  stringstyle=\color{orange},
-  deletekeywords={double,float},
-  classoffset=1, % starting new class
-  otherkeywords={double,float},
-  morekeywords={double,float},
-  keywordstyle=\bfseries\color{green!55!black},
-  classoffset=0
-}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
@@
 
+\newcommand{\fslspm}{FSL-SPM\xspace}
+\newcommand{\fslafni}{FSL-AFNI\xspace}
+\newcommand{\afnispm}{AFNI-SPM\xspace}
+
 \title{Comparing tool variability and numerical variability in fMRI analyses}
 
-\author{Ali Salari$^1$, Co-authors$^2$, Tristan Glatard$^1$}
+\author{Ali Salari$^1$, Other Authors$^1$, Tristan Glatard$^1$ \\ 
+$^1$ Department of Computer-Science and Software Engineering, Concordia University, Montreal, Canada}
 
-\authorrunning{Salari et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
+\maketitle
+\begin{abstract}
 
-\institute{$^1$ Anonymous Organization1\\
-  $^2$ Anonymous Organization2\\ **@******.***}
+\end{abstract}
 
-\institute{$^1$ Department of Computer Science and Software Engineering, Concordia University\\
-  $^2$ Co-authors Organization\\  Montréal, QC, Canada}
-
-\maketitle              % typeset the header of the contribution
-
-\begin{abstract}
-abstract\dots
-
-%  \keywords{Computational reproducibility  \and Neuroimaging pipelines \and Monte-Carlo arithmetic.}
-\end{abstract}
+\begin{IEEEkeywords}
+\end{IEEEkeywords}
 
@@
 
-\begin{description}
-  \item[$\bullet$ ] Methodological choice can influence the final determining areas of brain activation. This opens so results flexibility~\cite{bowring2019exploring}.
-
-  \item[$\bullet$ ] We presented a framework that can investigate the numerical instability of the pipelines based on Monte-Carlo arithmetic
+\begin{itemize}
+    \item We presented a framework that can investigate the numerical instability of the pipelines based on Monte-Carlo arithmetic
     by creating a Fuzzy environment, so that instrument mathematical functions implemented in mathematical system libraries (libmath).
 
-  \item[$\bullet$ ] In this paper, we aim to answer the questions 1) how the fMRI analyses are numerically stable?
+    \item Methodological choice can influence the final determining areas of brain activation.
+    This opens so results flexibility~\cite{bowring2019exploring,bowring2021isolating}.
+
+    \item In this paper, we aim to answer the questions 1) how the fMRI analyses are numerically stable?
     2) how the numerical variability is in comparison with the tool variability?
-\end{description}
+\end{itemize}
 
-\section{Methodology}
+\section{Materials and Methods}
 
-\subsection{libmath Fuzzy System}
+\subsection{Fuzzy libmath environment}
 
-\begin{description}
-  \item[$\bullet$ ] libmath Fuzzy allows you to study the numerical stability of tools and pipelines. 
-  \item[$\bullet$ ] It is based on MCA perturbations so that applies slight noise on floating-point operations.
-  \item[$\bullet$ ] It does not need source code modification or recompilation, and simply works using the Linux LD\_PRELOAD environment variable.
-  \item[$\bullet$ ] The library call interposition technique enables us to assess the tools that are dynamically linked to the mathematical library.
-\end{description}
+To simulate the machine level uncertainty, we used the method introduced in~\cite{salari2021accurate} called Fuzzy libmath (FL).
+FL uses Monte Carlo Arithmetic (MCA) to introduce a controlled amounts of noise in the floating-point operations,
+which models floating-point rounding and catasrophic cancellation errors.
+This is automated using Verificarlo tool~\cite{denis2015verificarlo} that implements MCA in the compilation time.
+The perturbation is introduced in a given number of least-significant bits so that
+the number of bits in the mantissa that will not be perturbed is defined as the virtual precision.​
+
+% MCA models floating-point roundoff and cancellations errors through random
+% perturbations, allowing for the estimation of error distributions from
+% independent random result samples. MCA simulates computations at a given
+% \emph{virtual precision} using the following perturbation:
+% \begin{equation} \label{eq:mca_inexact}
+%   inexact(x) = x + 2^{e_x-t}\xi
+%   \label{mcadefinition}
+% \end{equation}
+% where $e_x$ is the exponent in the floating-point representation of $x$,
+% $t$ is the virtual precision and $\xi$ is a random uniform variable of
+% $(-\frac{1}{2}, \frac{1}{2})$.
+
+% MCA allows for three perturbation modes: Random Rounding (RR) introduces the
+% perturbation in function outputs, simulating roundoff errors; Precision Bounding
+% (PB) introduces the perturbation in function operands, allowing for the
+% detection of catastrophic cancellations; and, Full MCA combines RR and PB,
+% resulting in the following perturbation:
+% \begin{equation} \label{eq:mca_modes}
+%   mca\_mode(x \circ y) = inexact_{RR}(  inexact_{PB}(x) \circ inexact_{PB}(y) )
+% \end{equation}
+
+% We instrumented the GNU mathematical library with MCA using
+% Verificarlo~\cite{denis2015verificarlo}, a tool that (1) uses the Clang
+% compiler to generate an LLVM (\url{http://llvm.org}) Intermediate
+% Representation (IR) of the source code, (2) replaces floating-point operations
+% in the IR by a call to the Verificarlo API, and (3) compiles the modified IR to
+% an executable using LLVM. The perturbation applied by the Verificarlo API
+% can be configured at runtime, for instance to change the virtual
+% precision applied to single- and double-precision floating-point values.
+
+In this framework, mathematical functions embeded in the operating system GNU mathematical library (libmath)
+are targeted to be instrumented.
+It instrument the functions by wrapping them so that only the output of the original functions be perturbed
+instead of input or their implementation.
+This is achieved by adding a floating-point zero to the output of the original function which results into perturbations.
+Listing~\ref{algo:wrapper} shows an example of this wrapping for the log function in both single and double precisions.
+This functionality helps to avoid of some issues in deterministic arithmetics like producing results out of the function definition.
+
+% To simulate OS updates, we introduce random perturbations in the GNU
+% mathematical library, the main mathematical library in GNU/Linux systems.
+% Instrumenting mathematical libraries with MCA raises a number of issues as
+% many functions assume deterministic arithmetic. For instance, applying random
+% perturbations around a discontinuity or within piecewise approximations
+% results in large variations and a total loss of significance that are not
+% relevant in our context. Therefore, we have applied MCA to proxy
+% mathematical functions wrapping those in the original library, such that only
+% the outputs of the original functions were perturbed but not their inputs or
+% the implementations themselves. This technique allows us to control the
+% magnitude of the perturbation as perceived by the application.
+
+The instrumented math functions so called ``fuzzy libmath", is loaded in the pipeline using LD\_PRELOAD, a Linux mechanism
+to force load a shared library into an executable. ​
+As a result, functions defined in fuzzy libmath transparently overload the original ones without the need to modify or
+recompile the analysis pipeline.​
+Also, this technique allows measuring the effect of numerical noise by running a program multiple times.​
+It is important to review the software dependencies of the pipelines to be sure that are involved with the same library that
+we arep erturbing.
+
+% The resulting MCA-instrumented mathematical library, ``fuzzy libmath" (FL), is
+% loaded in the pipeline using \texttt{LD\_PRELOAD}, a Linux mechanism to
+% force-load a shared library into an executable. As a result, functions defined in fuzzy libmath
+% transparently overload the original ones without the need to modify
+% or recompile the analysis pipeline. Fuzzy libmath functions call the original
+% functions through \texttt{dlsym}, a function that returns the memory address of
+% a symbol. To trigger MCA instrumentation, a floating-point zero is added to the
+% output of the original function and the result of this sum is perturbed and
+% returned.
+
+% \begin{description}
+%   \item[$\bullet$ ] libmath Fuzzy allows you to study the numerical stability of tools and pipelines. 
+%   \item[$\bullet$ ] It is based on MCA perturbations so that applies slight noise on floating-point operations.
+%   \item[$\bullet$ ] It does not need source code modification or recompilation, and simply works using the Linux LD\_PRELOAD environment variable.
+%   \item[$\bullet$ ] The library call interposition technique enables us to assess the tools that are dynamically linked to the mathematical library.
+% \end{description}
+
+% \lstdefinestyle{customc}{
+%   belowcaptionskip=1\baselineskip,
+%   breaklines=true,
+%   frame=L,
+%   xleftmargin=\parindent,
+%   language=C,
+%   showstringspaces=false,
+%   basicstyle=\footnotesize\ttfamily,
+%   keywordstyle=\bfseries\color{green!40!black},
+%   commentstyle=\itshape\color{purple!40!black},
+%   identifierstyle=\color{blue},
+%   stringstyle=\color{orange},
+% }
+
+\lstdefinestyle{customasm}{
+  belowcaptionskip=1\baselineskip,
+  frame=L,
+  xleftmargin=\parindent,
+  language=[x86masm]Assembler,
+  basicstyle=\footnotesize\ttfamily,
+  commentstyle=\itshape\color{purple!40!black},
+}
+\lstinputlisting[caption=Example wrapper script, label=algo:wrapper, style=customasm]{wrapper.c}
+%\lstinputlisting[caption=Scheduler, style=customc]{../wrapper2.c}
 
@@
 
-\begin{description}
-  \item[$\bullet$ ] We replicate the fMRI analyses used in~\cite{bowring2019exploring} using the three most popular packages 
-                    for fMRI data processing including FSL, AFNI, and SPM.
-
-  \item[$\bullet$ ] The functional fMRI studies have been chosen for reanalysis with the publicly available data repositories.
-                    The used dataset is available at https://openneuro.org/datasets/ds000001.
-
-  \item[$\bullet$ ] For the ds000001 study, 16 healthy adult subjects participated in a balloon analogue risk task over three scanning sessions.
-                    This analysis consists of several common processes. A full description of each analysis is included in~\cite{bowring2019exploring}.
-
-  \item[$\bullet$ ] In the original study, a number of preprocessing steps such as motion correction, segmentation, brain extraction, and registration 
+We replicate the fMRI analysis (ds000001 study) used in~\cite{bowring2019exploring} with the publicly available
+data repository in~\href{https://openneuro.org/datasets/ds000001}{OpenNeuro}
+using the three most popular packages for fMRI data processing including FSL, AFNI, and SPM. 
+We selected this publication to replicate the fMRI analysis because it is an state of the art study
+which compares between tool variability, and included all the sources and dataset available
+so that we can easility reanalyse tests using Fuzzy framework.
+A full description of the procedure of analysis is included in~\cite{bowring2019exploring,schonberg2012decreasing};
+we give a brief overview of the pipeline processes in this section.
+In this study, 16 healthy adult subjects participated in the balloon analogue risk task to measure risk-taking behavior
+over three scanning sessions.
+%The analysis was scripted using three different tools so that 
+In the original study, a number of preprocessing steps which are widely accepted within the community
+such as motion correction, segmentation, brain extraction, and registration 
 were applied in all of the analyses to ensure that results from each software package could be compared objectively.
-
-\end{description}
+% The steps that are taken in the procedure of analysis for each tool is specified in table~\ref{table:fmri-steps}.
+The analysis includes preprocessing, first-level, and second-level steps (Table~\ref{table:fmri-steps}) in all three software\dots
 
@@
 
-\begin{description}
-  \item[$\bullet$ Containerization] building Docker images for three of the most popular software packages in neuroimaging including FSL, AFNI, and SPM.
+The fMRI analysis pipeline was processed using three of the most popular software packages in neuroimaging
+including FSL (version 5.0.10), AFNI (version 18.1.09), and SPM (version SPM12, r7771) on Octave (version 5.2).
+The analyses were conducted on the same operating system, CentOS 7.3.
 We ensured that the software versions and all the requisites for running analyses used in all experiments 
-                  are identical to the original study.
+are similar to the original study, and were encapsulated in Docker images.
+We could replicate results of the original study except for AFNI with slightly differences due to the parallelization\dots
+We also used SPM/Octave instead of Matlab to be able to run analysis in HPC and also perturb mathmetical functions
+because Matlab has no dependencies on the GNU mathematical library, and it uses its libraries\dots
 
-  \item[$\bullet$ Between tool variability] check and confirm that obtained results are perfectly replicated comparing to the original study.
+In addition, we processed the same pipeline analyses with the same configurations in Fuzzy libmath environment
+to capture the numerical variability results. 
+We only perturbed the maximum precisions to compare uncertainty between tool variability and numerical instability at the level of OS.
+For this purpose, we instrumented to the virtual precision (t) of 53 bits for double-precision variable,
+and 24 bits for single-precision variable. We generated three Fuzzy samples in these precisions to match the number of tool samples.
 
-  \item[$\bullet$ Numerical variability] running 3 MCA samples in each condition using the Fuzzy libmath environment. 
-                  The conditions could be varying between tools, software versions, or the instrumented precisions. 
-    \begin{description}
-      \item[$\ast$ Varying precisions] a) only perturbing maximum precisions (OS-level), p=53 bits for double-precision and p=24 bits for single-precision.
-                                       This would help to compare uncertainty between tool variability and numerical instability at the OS-level. 
-                                       b) perturbing precisions from p=53 bits to p=1 bits by steps of 2 iteratively. 
-                                       This would help to find the most similar uncertainty distribution between tool variability and numerical variability.
-    \end{description}
+We compare variability between (un)thresholded of group-level activation maps.
+We statistically compute standard deviations between T-statistic values in the pair of tools.
+We calculate standard deviations between fuzzy samples as the square root of summation of variances between Fuzzy samples in each tool.
+We then compare the correlation of changes in both conditions.
+Moreover, we compute region-by-region Dice coefficients for the thresholded maps for the all pairs of tools.
+This measures the overlap of voxels which assess the spatial similarity between activated maps.
+The Dice values between Fuzzy samples correspond to the average of Dices computed among three Fuzzy samples for each pair of tools.
+We then compare the correlation of Dice scores which normalized by the region sizes in both conditions.
 
-  \item[$\bullet$ Image types] the fMRI result images that we are investigating are thresholded and unthresholded of the group level activation maps.
-
-  \item[$\bullet$ Comparison metrics] comparing variabilities statistically by computing correlations between T-statistic values, Dice coefficient, 
-                  and the number of significant digits.    
 % EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
@@
 
-  \item[$\bullet$ Configuration table] showing the detail of the configurations used for replicating the fMRI results.
-\end{description}
-
 \section{Results}
-
 All scripts and results to create the figures in this section are available on GitHub repository
@@
 Table~\ref{table:pipeline-stats}.
-The variability between images in each condition was measured using mean and standard deviation of absolute differences,
-and Pearson correlation coefficient.
+The variability between pair of images in each condition was measured using the mean and standard deviation of absolute differences.
+Overall, the distribution of the pairwise variations in WT is an order of magnitude lower than BT in both means and standard deviations.
+While the most variability was observed in pair of \fslafni, pair of \fslspm made the least variations for all conditions.
 % Overally, we see that values in between tools are comparable to values in within tool results.
@@
 %%%%%%%%%% Summary of statstics %%%%%%%%
-\setlength{\tabcolsep}{10pt}
+\setlength{\tabcolsep}{5pt}
 \begin{table}[h]
     \centering
-    \begin{tabular}{cccc|ccc}
+    \begin{tabular}{ccc|cc}
         \toprule
-        \multirow{2}{*}{} & \multicolumn{3}{c}{Thresholded} & \multicolumn{3}{c}{Unthresholded} \\
-        \cmidrule{2-4} \cmidrule{5-7} \\
-        {} & Mean diff. & Std. diff. & Corr. & Mean diff. & Std. diff. & Corr.  \\
+        \multirow{2}{*}{} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c}{Unthresholded} \\
+        \cmidrule{2-3} \cmidrule{4-5} \\
+        {} & Mean diff. & Std. diff. & Mean diff. & Std. diff. \\
         \midrule
         \rowcolor{lightgray}
-        FSL vs. SPM          &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        FSL vs. SPM          &  0.043       & 1.282      & 0.242     & 0.443  \\
         \rowcolor{lightgray}
-        FSL vs. AFNI         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        FSL vs. AFNI         &  0.099       & 1.548      & 0.302     & 0.547  \\
         \rowcolor{lightgray}
-        AFNI vs. SPM         &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
-        Fuzzy FSL and SPM    &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
-        Fuzzy FSL and AFNI   &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
-        Fuzzy AFNI and SPM   &  0.00       & 0.00      & 0.00       & 0.00     & 0.00       & 0.00 \\
+        AFNI vs. SPM         &  0.079       & 1.475      & 0.254     & 0.608  \\
+        Fuzzy FSL and SPM    &  0.005       & 0.358      & 0.030     & 0.099  \\
+        Fuzzy FSL and AFNI   &  0.011       & 0.475      & 0.038     & 0.155  \\
+        Fuzzy AFNI and SPM   &  0.011       & 0.458      & 0.033     & 0.144  \\
         \bottomrule
     \end{tabular}
-    \caption{Summary of T-statistics mean and standard deviation of differences and correlations of each pair of tools.}
+    \caption{Summary of T-statistics mean and standard deviation of differences for each pair of tools.}
     \label{table:pipeline-stats}
@@
 % \subsection{Comparing disparity in BT and WT}
-\subsection{Spatial localization of disparity in BT and WT}
+%\subsection{Spatial localization of disparity in BT and WT}
+\subsection{Group-level thresholded maps}
 % Fig message: showing the magnitude of differences and correlated area
@@
 
-Comparisons of standard deviations between results in WT and BT
-on the brain surface are shown in Figure~\ref{fig:thresh-varmaps} and Figure~\ref{fig:unthresh-varmaps}.
-Figure~\ref{fig:thresh-varmaps} shows maps for group-level thresholded T-statistics, and
-Figure~\ref{fig:unthresh-varmaps} shows maps for group-level unthresholded T-statistic values.
+  %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
+  \begin{figure}[b]
+    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
+    \centering
+    \includegraphics[width=\columnwidth]{figures/dices_corr.png}
+    \caption{Correlation of Dice coefficients of activated regions between pair of tools and fuzzy samples
+    from the thresholded T-statistics. Different pairs are illustrated in different colors. 
+    Regions correspond to the 360 areas of cortical parcellation (HCP-MMP1.0)~\cite{glasser2016multi}.}
+    \label{fig:dice-thresh}
+    \end{minipage}}
+  \end{figure}
+
+%Fig 1
+Comparisons of standard deviations between thresholded images in WT and BT
+on MNI space are shown in Figure~\ref{fig:thresh-varmaps}.
 While we observe substantial variations in BT (average std. dev. $\approx$ 1.5),
@@
 in some regions in the thresholded images.
-For instance, we see the temporal lobe in anterior view for almost all pairs and the fusiform gyrus in inferior view
-for the pairs of FSL-SPM and FSL-AFNI in Figure~\ref{fig:unthresh-varmaps}
-that are perfectly replicated using the numerical perturbations. 
-Although the unthresholded statistic maps from our analyses also show a different magnitude of
-the order of variations in both conditions, std. dev. ranges from $\approx$ 0.12 to $\approx$ 0.5 on average in WT and BT;
-there is great comparability between results.
-Generally, we obtained more uncertainty on thresholded results, probably due to different thresholding
-methods used in different tools.
-This can raise further investigations on the thresholding techniques toward stability.
+For instance, we see parts of the frontal lobe in the sagittal plane for almost all pairs and the occipital lobe in the axial plane
+for the pairs of \fslspm and \fslafni in Figure~\ref{fig:unthresh-varmaps}
+that are closely simulated using the numerical perturbations.
 
 %%%%%%%%%% Var. of Thresh %%%%%%%%
-\begin{figure}[b]
+\begin{figure*}[ht]
     \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-  \begin{subfigure}[t]{\linewidth}
+    \begin{subfigure}[t]{\textwidth}
       \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-tool(std).pdf}
+      \includegraphics[width=\textwidth]{figures/bt-wt-thresh-std.pdf}
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
@@
     \hfill
-  \begin{subfigure}[t]{\linewidth}
+    \begin{subfigure}[t]{\textwidth}
       \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-fuzzy(std).pdf}
+      \includegraphics[width=\textwidth]{figures/ratio-thresh-std.pdf}
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:thresh-varmaps2}
+      \label{fig:thresh-ratiomaps}
     \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-thresh-ratio(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:thresh-ratio}
-  \end{subfigure}
-  \caption{Surface maps of standard deviation of thresholded T-statistics. First and second rows show
-  results on between-tool and within-tool results, respectively. Third row represents the ratio of differences
-  in between and within tools so that brigher areas indicate more similar order of magnitude of variations in both conditions,
-  and vise versa for the darkder regions.}
+    \caption{Maps of standard deviation of thresholded T-statistics. First and second rows show
+    maps on between-tool and within-tool results, respectively. Third row represents the ratio of differences
+    in between and within tools.}
+    % so that bright blue areas indicate more similar order of magnitude of variations in both conditions,
+    %and vise versa for the darkder regions.}
     \label{fig:thresh-varmaps}
     \end{minipage}}
-\end{figure}
+  \end{figure*}
 
-%%%%%%%%%% Var. of Unthresh %%%%%%%%
-\begin{figure}[b]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-tool(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:unthresh-varmaps1}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-fuzzy(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:unthresh-varmaps2}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-ratio(std).pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \label{fig:unthresh-ratio}
-  \end{subfigure}
-  \caption{Surface maps of standard deviation of unthresholded T-statistics.}
-  \label{fig:unthresh-varmaps}
-  \end{minipage}}
-\end{figure}
-
-The scatter plot in Figure~\ref{fig:correlations} represents the correlation of standard deviation between conditions.
-We found three major clusters, including upper, lower, and identity.
-The identity cluster corresponds to the correlations between 0.9 and 1.1; the upper cluster shows correlations where BT $\approx$ 0;
-and the lower cluster represents correlations where WT $\approx$ 0.
-The identity area is also represented on the surface maps in the second row in Figure~\ref{fig:correlations}.
-This figure shows the spatial localization of the parts of the brain that are numerically dependent.
-We can see regions such as the occipital lobe in the posterior view and the frontal lobe in the interior view 
-that are highly correlated in BT and WT results.
-This refines the presented results in Figure~\ref{fig:unthresh-varmaps},
-which indicates how spatial variabilities are simulated using numerical perturbations in some areas.
-% Spatial localization of significant activation in the thresholded images also varied across software packages.
-% Moreover, results show that pair of FSL-SPM has the least correlation of variability in within tool and between tool.
-% This will implies that ... which can help for further investigations.
-
-%%%%%%%%%% Corr. plot of tstats%%%%%%%%
-\begin{figure}[b]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-    \begin{subfigure}[t]{\linewidth}
-      \centering
-      \includegraphics[width=\linewidth]{figures/std-corr-unthresh-plot.png}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \label{fig:unthresh-corrplot}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{\linewidth}
-      \centering
-      \includegraphics[width=\linewidth]{figures/maps-on-surf-unthresh-tool(corr).pdf}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \label{fig:unthresh-corrmaps}
-    \end{subfigure}
-  \caption{Correlation of variability in BT and WT variations in unthresholded maps. First row plots the correlations
-  voxel by voxel, which is highlighted with different colors for three major clusters including upper cluster (purple color),
-  lower cluster (yellow color), and correlated cluster (green color) which are mapped on surface in the second row.}
-  \label{fig:correlations}
-  \end{minipage}}
-\end{figure}
-
-\subsection{Region-based similarity in BT and WT}
+% Fig2
 In Figure~\ref{fig:dice-thresh}, we compare region-by-region Dice coefficients of
-the group level thresholded maps in BT and WT for all pairs of software packages.
-This measures the overlap of voxels which assess the spatial similarity between activated maps.
-In WT similarity, the Dice values correspond to the average of Dices computed among three
-Fuzzy samples for each pair of tools.
-Results show that the similarity between tool variations is correlated with the numerical variations,
-which implies that similar anatomical regions are activated, and also the topology of the activation patterns
-is preserved between results from two types of variations.
-% This correlation highly increases when normalizing Dice scores by the region sizes.
-% which reduces the effect of small regions.
-
-% This implies that region by region similarity between two type of variations are preserved.
-% Results show that similar anatomical regions are activated in both conditions. 
-% This plot suggests the similar topologies of the activation patterns in each condition.
+the group-level thresholded maps for all pairs of software packages in BT and WT.
+This shows a linear correlation between Dice values in BT and WT,
+which implies that the variability of activated voxels in both conditions is similar.
+Also, small P-values across all three pairs, including 1x10e-10 for \fslafni, 6x10e-04 for \fslspm,
+and 2x10e-05 for \afnispm, confirms this correlation of similarities.
+The vertical line where the Dice score is zero in BT shows regions in the brain with no overlaps between activated voxels in BT but WT.
+For instance, left/right `V1\_ROI' in \fslafni and \fslspm, and left/right `TGd\_ROI' in \afnispm results.
+The regression line is computed over Dices where BT and WT are not zero.
 % The average of Dice scores range from to 
@@
 
-%%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
-\begin{figure}[b]
+\subsection{Group-level unthresholded maps}
+
+% Fig3
+Figure~\ref{fig:unthresh-varmaps} shows the brain maps of standard deviations for group-level unthresholded T-statistics in WT and BT.
+Results show a different magnitude of
+the order of variations in WT and BT with standard deviation ranges from $\approx$ 0.12 to $\approx$ 0.5 on average, respectively.
+The maps show regions in the brain where the magnitude of standard deviation is close to zero in WT but it exceeds 2.0 in BT,
+such as the limbic and frontal lobes in the sagittal plane.
+However, there are voxels with a significant correlation between WT and BT that are uniformly distributed across the brain maps.
+
+%%%%%%%%%% Var. of Thresh %%%%%%%%
+\begin{figure*}[b]
     \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+    \begin{subfigure}[t]{\textwidth}
       \centering
-  \includegraphics[width=\textwidth]{figures/dices_corr.png}
-  \caption{Correlation of Dice coefficients of activated regions between pair of tools and fuzzy samples
-  from the thresholded T-statistics. Different pairs are illustrated in different colors. 
-  Regression lines are normalized by the region sizes on the right plot.
-  Regions correspond to the 360 areas of cortical parcellation (HCP-MMP1.0)~\cite{Glasser-nature}.}
-  \label{fig:dice-thresh}
+      \includegraphics[width=\textwidth]{figures/bt-wt-unthresh-std.pdf}
+      %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \label{fig:unthresh-varmaps1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[t]{\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{figures/ratio-unthresh-std.pdf}
+      %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \label{fig:unthresh-ratiomaps}
+    \end{subfigure}
+    \caption{Maps of standard deviation of unthresholded T-statistics. First and second rows show
+    maps on between-tool and within-tool results, respectively. Third row represents the ratio of differences
+    in between and within tools.}
+    \label{fig:unthresh-varmaps}
     \end{minipage}}
-\end{figure}
+  \end{figure*}
 
-% %%%%%%%%%% Summary of statstics %%%%%%%%
-% \setlength{\tabcolsep}{10pt}
-% \begin{table}[h]
-%     \centering
-%     \begin{tabular}{cccc}
-%         \toprule
-%         {} & Mean diff. & Std. diff. & Corr. \\
-%         \midrule
-%         \rowcolor{lightgray}
-%         FSL vs. SPM          &  0.242       & 0.534      & 0.599  \\
-%         \rowcolor{lightgray}
-%         FSL vs. AFNI         &  0.302       & 0.674      & 0.591  \\
-%         \rowcolor{lightgray}
-%         AFNI vs. SPM         &  0.254       & 0.659      & 0.562  \\
-%         Fuzzy FSL and SPM    &  0.00       & 0.00      & 0.00  \\
-%         Fuzzy FSL and AFNI   &  0.00       & 0.00      & 0.00  \\
-%         Fuzzy AFNI and SPM   &  0.00       & 0.00      & 0.00  \\
-%         \bottomrule
-%     \end{tabular}
-%     \caption{Summary of T-statistics mean and standard deviation of differences and correlation coefficients
-%     across three sets of results in two conditions.}
-%     \label{table:pipeline-stats}
-% \end{table}
+% Fig4
+The scatter plot in Figure~\ref{fig:correlations} represents the correlation of standard deviation in WT and BT variability.
+We found two major clusters, including the identity cluster that corresponds to the correlations
+between BT and WT with the ratio of $0.5 < BT/WT < 1.5$,
+and the upper cluster that shows voxels where BT $\approx$ 0.
+The percentage of voxels included in the identity cluster is \%9.9 in \fslspm, \%17.3 in \fslafni, and \%13.8 in \afnispm,
+and total voxels in the upper cluster are $\approx$ \%1.
+The identity area is also represented on the MNI space in the second row in Figure~\ref{fig:correlations}.
+This figure shows the spatial localization of the parts of the brain that BT variability is correlated with the numerical variability.
+This refines the presented results in Figure~\ref{fig:unthresh-varmaps},
+which indicates how correlation is uniformly distributed across the brain.
+% Spatial localization of significant activation in the thresholded images also varied across software packages.
+% Moreover, results show that pair of FSL-SPM has the least correlation of variability in within tool and between tool.
+% This will implies that ... which can help for further investigations.
 
-% \subsection{The precision that Fuzzy FSL tool can simulate the between tool variations}
-% \begin{description}
-%   \item[$\bullet$ Figure 5:] Repeat Fig 1-4 for the results of Fuzzy FSL on the precision that simulate mostly betwen tool varions.
-% \end{description}
+  %%%%%%%%%% Corr. plot of tstats%%%%%%%%
+  \begin{figure*}[b]
+    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+      \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/std-corr-unthresh-plot.png}
+        %\caption{Standard deviation of thresholded t-statistics map on template surface}
+        \label{fig:unthresh-corrplot}
+      \end{subfigure}
+      \hfill
+      \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/corr-unthresh-std.pdf}
+        %\caption{Standard deviation of thresholded t-statistics map on template surface}
+        \label{fig:unthresh-corrmaps}
+      \end{subfigure}
+      \caption{Correlation of variability in between-tool and within-tool variations in unthresholded maps. First row plots the correlations
+    voxel by voxel, which is highlighted with different colors for two major clusters including upper cluster (purple color) and
+    correlated cluster (green color) which are mapped on the brain in the second row.}
+    \label{fig:correlations}
+    \end{minipage}}
+  \end{figure*}
 
 \section{Conclusion \& Discussion}
-% In this study, we represented the magnitude of differences in between tool and within tool results.
-% Also we showed the numerically dependent parts of the brain, and explained how between tool variations
-% are correlated with numerical variability. Moreover, we indicated the spatial similarity between results so that
-% numerical perturbations preserve the topology of the avtivation patterns across all three sets of packages in both conditions.
 
-% Further studies can be evaluating the numerical stabilities within tool by focusing on the particular parts of 
-% the pipeline that has been identified as the mian sources of variations in~\cite{bowring2019exploring}.
+\begin{itemize}
+    \item[$\bullet$ ] In this study, we represented the magnitude of differences in between tool and within tool results.
+    We obtained more instability in BT compared to WT. Also we showed how between tool variations
+    are correlated with numerical variability.
 
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\bibliographystyle{splncs04}
+    \item[$\bullet$ ] Generally, we obtained more uncertainty on thresholded results, probably due to different thresholding
+    methods used in different tools. This can raise further investigations on the thresholding techniques toward stability.
+
+    \item[$\bullet$ ] Further studies can be evaluating the numerical stabilities within tool by focusing on the particular parts of 
+    the pipeline that has been identified as the main sources of variations in~\cite{bowring2021isolating}.
+    Also, we can invetigate the precision in WT variability that simulates mostly BT variability in the furure study.
+
+\end{itemize}
+
+\section{Acknowledgments}
+
+%%
+%% The next two lines define the bibliography style to be used, and
+%% the bibliography file.
+\bibliographystyle{plain}
 \bibliography{biblio}
@@
 \end{document}
+\endinput
+%%
+%% End of file `sample-authordraft.tex'.

### 2021-09-23 paper/wrapper.c

@@ -1,0 +1,17 @@
+#include <dlfcn.h>
+#include <math.h>
+
+static double (*real_log)(double dbl);
+static float (*real_logf)(float dbl);
+
+// Override
+double log(double dbl);
+{
+	real_log = dlsym(RTLD_NEXT, "log");
+	return real_log(dbl) + 0.0;
+}
+float logf(float dbl);
+{
+        real_logf = dlsym(RTLD_NEXT, "logf");
+        return real_logf(dbl) + 0.0f;
+}

### 2021-09-23 computs.py
update scripts

@@ -294,11 +294,11 @@ def plot_pair_corr_variance(bt, wt, type_, ind_, ax, tool_=None, append_=None):
         #ax[ind_[0]].set_xscale('log')
 
         # fraction of clusters
-        data1[data1 == 0] = np.nan
-        all_corr_count = np.count_nonzero(~np.isnan(data1))
-        corr_map[np.isnan(bt_)] = np.nan
+        data2[(data2 == 0) & (data1 == 0)] = np.nan
+        all_corr_count = np.count_nonzero(~np.isnan(data2))
+        corr_map[np.isnan(bt_) & np.isnan(wt_)] = np.nan
         corr_count = np.count_nonzero(~np.isnan(corr_map))
-        upper_map[np.isnan(bt_)] = np.nan
+        upper_map[np.isnan(bt_) & np.isnan(wt_)] = np.nan
         upper_count = np.count_nonzero(~np.isnan(upper_map))
         #print('{}\nall voxels:{}\ncorrelated voxels: {}\nupper voxels: {}\nFraction of green: %{:.1f}\nFraction of purple: %{:.1f}'.format(tool_, all_corr_count, corr_count, upper_count, (corr_count/all_corr_count)*100, (upper_count/all_corr_count)*100))
         print('{}\nFraction of green: %{:.1f}\nFraction of purple: %{:.1f}'.format(tool_, (corr_count/all_corr_count)*100, (upper_count/all_corr_count)*100))
@@ -613,10 +613,12 @@ def plot_dices(dices_):
             # Get region sizes
             tool_list = np.nan_to_num(tool_list)
             r_sizes = []
+            r_name = []
             for i in range(len(tool_list)):
                 l_ = list(dices_.keys())
                 s = dices_[l_[i]]['size']
                 r_sizes.append(s)
+                r_name.append(l_[i])
     
             # Plot Normalize dice values by region size
             tool_norm = np.array(tool_list)*np.array(r_sizes)
@@ -625,6 +627,11 @@ def plot_dices(dices_):
             tool_norm = (tool_norm - np.min(tool_norm)) / (np.max(tool_norm) - np.min(tool_norm))
             mca_norm = (mca_norm - np.min(mca_norm)) / (np.max(mca_norm) - np.min(mca_norm))
 
+            # regions that BT=0 and WT>0.93
+            x = np.where((tool_norm == 0) & (mca_norm > 0.93) , r_name, None)
+            res = [i for i in x if i]
[…]

### 2021-09-23 paper/paper.tex
Update method and result sections

@@
 \usepackage{listings}
+\usepackage{dingbat}
 
@@
 
-To simulate the machine level uncertainty, we used the method introduced in~\cite{salari2021accurate} called Fuzzy libmath (FL).
-FL uses Monte Carlo Arithmetic (MCA) to introduce a controlled amounts of noise in the floating-point operations,
-which models floating-point rounding and catasrophic cancellation errors.
+To simulate the machine-level uncertainty, we used the method introduced in~\cite{salari2021accurate} called Fuzzy libmath (FL).
+FL uses Monte Carlo Arithmetic (MCA) to introduce a controlled amount of noise in the floating-point operations
+through the following perturbation model:
+\begin{equation} \label{eq:mca_inexact}
+  inexact(x) = x + 2^{e_x-t}\xi
+\end{equation}
+where $e_x$ is the exponent in the floating-point representation of $x$,
+$t$ is the virtual precision, the number of bits in mantissa that will not be perturbed,
+and $\xi$ is a random uniform variable of $(-\frac{1}{2}, \frac{1}{2})$.
+The perturbation is applied in a given number of least-significant bits,
+which models floating-point rounding and catastrophic cancellation errors.
 This is automated using Verificarlo tool~\cite{denis2015verificarlo} that implements MCA in the compilation time.
-The perturbation is introduced in a given number of least-significant bits so that
-the number of bits in the mantissa that will not be perturbed is defined as the virtual precision.​
 
-% MCA models floating-point roundoff and cancellations errors through random
-% perturbations, allowing for the estimation of error distributions from
-% independent random result samples. MCA simulates computations at a given
-% \emph{virtual precision} using the following perturbation:
-% \begin{equation} \label{eq:mca_inexact}
-%   inexact(x) = x + 2^{e_x-t}\xi
-%   \label{mcadefinition}
-% \end{equation}
-% where $e_x$ is the exponent in the floating-point representation of $x$,
-% $t$ is the virtual precision and $\xi$ is a random uniform variable of
-% $(-\frac{1}{2}, \frac{1}{2})$.
-
-% MCA allows for three perturbation modes: Random Rounding (RR) introduces the
-% perturbation in function outputs, simulating roundoff errors; Precision Bounding
-% (PB) introduces the perturbation in function operands, allowing for the
-% detection of catastrophic cancellations; and, Full MCA combines RR and PB,
-% resulting in the following perturbation:
-% \begin{equation} \label{eq:mca_modes}
-%   mca\_mode(x \circ y) = inexact_{RR}(  inexact_{PB}(x) \circ inexact_{PB}(y) )
-% \end{equation}
-
-% We instrumented the GNU mathematical library with MCA using
-% Verificarlo~\cite{denis2015verificarlo}, a tool that (1) uses the Clang
-% compiler to generate an LLVM (\url{http://llvm.org}) Intermediate
-% Representation (IR) of the source code, (2) replaces floating-point operations
-% in the IR by a call to the Verificarlo API, and (3) compiles the modified IR to
-% an executable using LLVM. The perturbation applied by the Verificarlo API
-% can be configured at runtime, for instance to change the virtual
-% precision applied to single- and double-precision floating-point values.
-
-In this framework, mathematical functions embeded in the operating system GNU mathematical library (libmath)
-are targeted to be instrumented.
-It instrument the functions by wrapping them so that only the output of the original functions be perturbed
-instead of input or their implementation.
-This is achieved by adding a floating-point zero to the output of the original function which results into perturbations.
+With the goal of OS-level perturbations, this framework instruments mathematical functions embedded
+in the mathematical library in GNU operating systems, libmath.
+To avoid some pitfalls in deterministic arithmetics like producing results out of the function definition,
+FL instruments the functions by wrapping them so that only the original functions' output
+is perturbed instead of input or their implementation.
+This is achieved by adding a floating-point zero to the output of the original function so that the result of this summation
+is perturbed and returned.
 Listing~\ref{algo:wrapper} shows an example of this wrapping for the log function in both single and double precisions.
-This functionality helps to avoid of some issues in deterministic arithmetics like producing results out of the function definition.
-
-% To simulate OS updates, we introduce random perturbations in the GNU
-% mathematical library, the main mathematical library in GNU/Linux systems.
-% Instrumenting mathematical libraries with MCA raises a number of issues as
-% many functions assume deterministic arithmetic. For instance, applying random
-% perturbations around a discontinuity or within piecewise approximations
-% results in large variations and a total loss of significance that are not
-% relevant in our context. Therefore, we have applied MCA to proxy
-% mathematical functions wrapping those in the original library, such that only
-% the outputs of the original functions were perturbed but not their inputs or
-% the implementations themselves. This technique allows us to control the
-% magnitude of the perturbation as perceived by the application.
-
-The instrumented math functions so called ``fuzzy libmath", is loaded in the pipeline using LD\_PRELOAD, a Linux mechanism
-to force load a shared library into an executable. ​
-As a result, functions defined in fuzzy libmath transparently overload the original ones without the need to modify or
-recompile the analysis pipeline.​
-Also, this technique allows measuring the effect of numerical noise by running a program multiple times.​
-It is important to review the software dependencies of the pipelines to be sure that are involved with the same library that
-we arep erturbing.
-
-% The resulting MCA-instrumented mathematical library, ``fuzzy libmath" (FL), is
-% loaded in the pipeline using \texttt{LD\_PRELOAD}, a Linux mechanism to
-% force-load a shared library into an executable. As a result, functions defined in fuzzy libmath
-% transparently overload the original ones without the need to modify
-% or recompile the analysis pipeline. Fuzzy libmath functions call the original
-% functions through \texttt{dlsym}, a function that returns the memory address of
-% a symbol. To trigger MCA instrumentation, a floating-point zero is added to the
-% output of the original function and the result of this sum is perturbed and
-% returned.
-
-% \begin{description}
-%   \item[$\bullet$ ] libmath Fuzzy allows you to study the numerical stability of tools and pipelines. 
-%   \item[$\bullet$ ] It is based on MCA perturbations so that applies slight noise on floating-point operations.
-%   \item[$\bullet$ ] It does not need source code modification or recompilation, and simply works using the Linux LD\_PRELOAD environment variable.
-%   \item[$\bullet$ ] The library call interposition technique enables us to assess the tools that are dynamically linked to the mathematical library.
-% \end{description}
+In this script, the original functions are called by \texttt{dlsym}, a function that returns the memory address of a symbol
+using the handle of \texttt{RTLD\_NEXT}.
+This allows one to provide a wrapper around a function in another shared library.
 
@@
 }
-\lstinputlisting[caption=Example wrapper script, label=algo:wrapper, style=customasm]{wrapper.c}
+\lstinputlisting[caption=Sample wrapper script, label=algo:wrapper, style=customasm]{wrapper.c}
 %\lstinputlisting[caption=Scheduler, style=customc]{../wrapper2.c}
 
-\subsection{fMRI analyses \& Dataset}
+Finally, the instrumented functions are loaded in the pipeline using LD\_PRELOAD, a Linux environment variable
+to force load a shared library into an executable. ​
+This allows functions defined in FL to transparently
+overload the original ones without the need to modify or recompile the analysis pipeline.​
 
-We replicate the fMRI analysis (ds000001 study) used in~\cite{bowring2019exploring} with the publicly available
-data repository in~\href{https://openneuro.org/datasets/ds000001}{OpenNeuro}
-using the three most popular packages for fMRI data processing including FSL, AFNI, and SPM. 
-We selected this publication to replicate the fMRI analysis because it is an state of the art study
-which compares between tool variability, and included all the sources and dataset available
-so that we can easility reanalyse tests using Fuzzy framework.
-A full description of the procedure of analysis is included in~\cite{bowring2019exploring,schonberg2012decreasing};
-we give a brief overview of the pipeline processes in this section.
-In this study, 16 healthy adult subjects participated in the balloon analogue risk task to measure risk-taking behavior
-over three scanning sessions.
-%The analysis was scripted using three different tools so that 
-In the original study, a number of preprocessing steps which are widely accepted within the community
-such as motion correction, segmentation, brain extraction, and registration 
-were applied in all of the analyses to ensure that results from each software package could be compared objectively.
-% The steps that are taken in the procedure of analysis for each tool is specified in table~\ref{table:fmri-steps}.
-The analysis includes preprocessing, first-level, and second-level steps (Table~\ref{table:fmri-steps}) in all three software\dots
+This technique allows measuring the effect of numerical variability by running a program multiple times
+with the feature of controlling the magnitude of the perturbations as perceived by the application.
+Moreover, FL enables us to assess the software packages that are dynamically linked to the mathematical libraries.
+So, it is important to trace the tool dependencies of the pipelines to ensure that the specific mathematical library
+is involved during the pipeline executions.
+
+\subsection{fMRI analysis \& Dataset}
+
+We replicated the fMRI analysis described as study `ds000001' in~\cite{bowring2019exploring}
+with the publicly available data repository in~\href{https://openneuro.org/datasets/ds000001}{OpenNeuro}
+using the three well-known software packages for fMRI data processing, including
+FSL~\cite{jenkinson2012fsl}, AFNI~\cite{cox1996afni}, and SPM~\cite{penny2011statistical}.
+We selected this publication to replicate the fMRI analysis because the methods and sources were explicitly
+written to be accessible and reproducible. This enabled us to reanalyze tests using the FL framework and
+compare results with the between tool variability.
+
+In the selected study, 16 healthy adult subjects participated in the balloon analog risk task to measure
+risk-taking behavior over three scanning sessions.
+This study included preprocessing, first-level, and second-level analyses that were implemented with all three software.
+Table~\ref{table:pipeline-steps} shows the steps that were taken in the procedure of analyses for each tool in the original study.
+In the original study, a number of preprocessing steps widely accepted within the community, such as motion correction,
+segmentation, brain extraction, and registration, were applied in all analyses to ensure that results from each software
+package could be compared objectively.
+A full description of the pipelines implemented within three packages is presented in the original
+study~\cite{bowring2019exploring,schonberg2012decreasing}.
+
+%%%%%%%%%% Summary of statstics %%%%%%%%
+\setlength{\tabcolsep}{4pt}
+\begin{table}[h]
+    \centering
+    \begin{tabular}{|c|l|c|c|c|}
+        \hline
+%        \multirow{2}{*}{} & \multicolumn{1}{c}{Thresholded}& & \multicolumn{1}{c}{Unthresholded}& \\
+        \multicolumn{2}{|c|}{} & FSL & AFNI & SPM \\
+        \hline
+        {Preprocessing} & {Motion Correction}                          & \checkmark    & \checkmark     & \checkmark  \\
+        {} & {Segmentation}                               &    &      & \checkmark  \\
+        {} & {Brain Extraction (Anatomical)}              & \checkmark     & \checkmark    & \checkmark  \\
+        {} & {Brain Extraction (Functional)}              &   & \checkmark     &  \\
+        {} & {Intra-subject Coregistration}               & \checkmark    & \checkmark     & \checkmark \\
+        {} & {Inter-subject Registration}                 & \checkmark    & \checkmark     & \checkmark \\
+        {} & {Analysis Voxel Size}                        & \checkmark    & \checkmark     & \checkmark \\
+        {} & {Smoothing}                                  & \checkmark    & \checkmark     & \checkmark  \\
+        \hline
+        {First-level} & {Model Specification}                          & \checkmark    & \checkmark     & \checkmark  \\
+        {} & {Inclusion of 6 Motion Parameters}                               & \checkmark   &  \checkmark    & \checkmark  \\
+        {} & {Model Estimation}                           & &     & \checkmark  \\
+        {} & {Contrasts}                                   &  \checkmark & \checkmark     & \checkmark \\
+        \hline
+        {Second-level} & {Model Specification}                          & \checkmark    & \checkmark     & \checkmark  \\
+        {} & {Model Estimation}                           &      &    & \checkmark  \\
+        {} & {Contrasts}                                   &   & \checkmark     & \checkmark  \\
+        {} & {Second-level Inference}                               &  \checkmark  &    \checkmark  & \checkmark  \\
+        \hline
+
+      \end{tabular}
+    \caption{Software processing steps. This table is adopted from~\cite{bowring2019exploring}.}
+    \label{table:pipeline-steps}
+\end{table}
 
@@
 
-The fMRI analysis pipeline was processed using three of the most popular software packages in neuroimaging
-including FSL (version 5.0.10), AFNI (version 18.1.09), and SPM (version SPM12, r7771) on Octave (version 5.2).
-The analyses were conducted on the same operating system, CentOS 7.3.
+To capture variability between tools, the fMRI analysis pipeline was processed using three of the most popular software
+packages in neuroimaging, including FSL (version 5.0.10), AFNI (version 18.1.09), and SPM (version SPM12, r7771)
+on Octave (version 5.2). The analyses were conducted on the same operating system, CentOS 7.3.
+% The computations were performed on a cluster comprised of ...
 We ensured that the software versions and all the requisites for running analyses used in all experiments 
-are similar to the original study, and were encapsulated in Docker images.
-We could replicate results of the original study except for AFNI with slightly differences due to the parallelization\dots
-We also used SPM/Octave instead of Matlab to be able to run analysis in HPC and also perturb mathmetical functions
-because Matlab has no dependencies on the GNU mathematical library, and it uses its libraries\dots
+were similar to the original study and encapsulated in Docker images.
+% We could replicate results of the original study except for AFNI with slightly differences due to the parallelization\dots
+% We also used SPM/Octave instead of Matlab to be able to run analysis in HPC and also perturb mathmetical functions
+% because Matlab has no dependencies on the GNU mathematical library, and it uses its libraries\dots
 
-In addition, we processed the same pipeline analyses with the same configurations in Fuzzy libmath environment
-to capture the numerical variability results. 
+In addition, the same subjects and fMRI analysis were processed with the same configurations in the Fuzzy libmath environment
+to produce the numerical variability results.
 We only perturbed the maximum precisions to compare uncertainty between tool variability and numerical instability at the level of OS.
-For this purpose, we instrumented to the virtual precision (t) of 53 bits for double-precision variable,
-and 24 bits for single-precision variable. We generated three Fuzzy samples in these precisions to match the number of tool samples.
+For this purpose, we applied instrumentations at the virtual precision (t) of 53 bits for the double-precision variable
+and 24 bits for the single-precision variable. Three Fuzzy samples were generated at these precisions to match the number of tool samples.
 
-We compare variability between (un)thresholded of group-level activation maps.
-We statistically compute standard deviations between T-statistic values in the pair of tools.
-We calculate standard deviations between fuzzy samples as the square root of summation of variances between Fuzzy samples in each tool.
-We then compare the correlation of changes in both conditions.
-Moreover, we compute region-by-region Dice coefficients for the thresholded maps for the all pairs of tools.
-This measures the overlap of voxels which assess the spatial similarity between activated maps.
-The Dice values between Fuzzy samples correspond to the average of Dices computed among three Fuzzy samples for each pair of tools.
-We then compare the correlation of Dice scores which normalized by the region sizes in both conditions.
-
-% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
-% are responsible for disparities between pair of images.
+We evaluated variabilities in (un)thresholded group-level activation maps.
+We statistically computed standard deviations between T-statistic values for each pair of tools
+and then compared the correlation of changes in both conditions.
+The standard deviation between fuzzy samples corresponds to the square root of the summation of variances between samples in each tool.
+Moreover, we determined region-by-region Dice coefficients for the thresholded maps for each pair of tools.
+% This measured the overlap of acitaved voxels which assess the spatial similarity between activated maps.
+The Dice values between Fuzzy samples correspond to the average pair-wise Dices computed among three Fuzzy samples
+for each pair of tools.
+Also, we compared the correlation of Dice scores normalized by the region sizes in both conditions.
 
@@
 in \url{https://github.com/ali4006/fuzzy-neurotools}.
-Replication of all analyses was visually assessed to be the same as the original findings.
+Replication of all analyses was visually assessed to be the same as the original study.
 We ensured that fMRI analyses were processed successfully.
@@
 The within tool variability shows results among different fuzzy libmath
-samples for the specific version of the tools, and it is not within tool versions.
+samples for the specific version of the tools, and it is not within tool versions.c
 
@@
 Overall, the distribution of the pairwise variations in WT is an order of magnitude lower than BT in both means and standard deviations.
-While the most variability was observed in pair of \fslafni, pair of \fslspm made the least variations for all conditions.
+While the most variability was observed in the pair of \fslafni, the pair of \fslspm made the least variations for all conditions.
 % Overally, we see that values in between tools are comparable to values in within tool results.
-% The distribution of the pairwise differences in T-statistic..
-% The standard deviations exceeding 2.0 in magnitude..
-% Pairwise correlations ranged from 0.43 to 0.7 for within tool variability..
 
@@
 \subsection{Group-level thresholded maps}
-% Fig message: showing the magnitude of differences and correlated area
-% Fig message: showing numerically dependent parts of the brain
-
-  %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
-  \begin{figure}[b]
-    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
-    \centering
-    \includegraphics[width=\columnwidth]{figures/dices_corr.png}
-    \caption{Correlation of Dice coefficients of activated regions between pair of tools and fuzzy samples
-    from the thresholded T-statistics. Different pairs are illustrated in different colors. 
-    Regions correspond to the 360 areas of cortical parcellation (HCP-MMP1.0)~\cite{glasser2016multi}.}
-    \label{fig:dice-thresh}
-    \end{minipage}}
-  \end{figure}
 
@@
 on MNI space are shown in Figure~\ref{fig:thresh-varmaps}.
-While we observe substantial variations in BT (average std. dev. $\approx$ 1.5),
-the order of magnitude of variations in WT is much lower (average std. dev. $\approx$ 0.5),
+
+While we observe substantial variations in BT with the average standard deviation $\approx$ 1.5,
+the order of magnitude of variations in WT is much lower with the average standard deviation $\approx$ 0.5,
 as was anticipated. However, numerical variability is still significant in WT results.
-Moreover, we see the same order of magnitude in WT variations compared to BT variations
+%Moreover, the numerical perturbations produces variations in similar order og magnitude in WT compared to BT variations
+Moreover, we see the similar order of magnitude in WT variations compared to BT variations
 in some regions in the thresholded images.
-For instance, we see parts of the frontal lobe in the sagittal plane for almost all pairs and the occipital lobe in the axial plane
+For instance, some parts of the frontal lobe in the sagittal plane for almost all pairs and the occipital lobe in the axial plane
 for the pairs of \fslspm and \fslafni in Figure~\ref{fig:unthresh-varmaps}
-that are closely simulated using the numerical perturbations.
+are closely replicated using the numerical perturbations.
+
+% Fig2
+In Figure~\ref{fig:dice-thresh}, we compare region-by-region Dice coefficients of
+the group-level thresholded maps for all pairs of software packages in BT and WT.
+This shows a linear correlation between Dice values in BT and WT,
+which implies that the variability of activated voxels in both conditions is similar.
+Also, small P-values across all three pairs, including \num{1e-10} for \fslafni, \num{6e-04} for \fslspm,
+and \num{2e-05} for \afnispm, confirms this correlation of similarities.
+The vertical line where the Dice score is zero in BT shows regions in the brain with no overlaps between activated voxels in BT but WT,
+including left/right `V1\_ROI' in \fslafni and \fslspm, and left/right `TGd\_ROI' in \afnispm results.
 
@@
     \end{subfigure}
-    \caption{Maps of standard deviation of thresholded T-statistics. First and second rows show
-    maps on between-tool and within-tool results, respectively. Third row represents the ratio of differences
-    in between and within tools.}
+    \caption{Maps of standard deviation of thresholded T-statistics. The first and second rows show
+    maps on BT and WT results, respectively, and the third row represents maps of the ratio between them.}
     % so that bright blue areas indicate more similar order of magnitude of variations in both conditions,
@@
 
-% Fig2
-In Figure~\ref{fig:dice-thresh}, we compare region-by-region Dice coefficients of
-the group-level thresholded maps for all pairs of software packages in BT and WT.
-This shows a linear correlation between Dice values in BT and WT,
-which implies that the variability of activated voxels in both conditions is similar.
-Also, small P-values across all three pairs, including 1x10e-10 for \fslafni, 6x10e-04 for \fslspm,
-and 2x10e-05 for \afnispm, confirms this correlation of similarities.
-The vertical line where the Dice score is zero in BT shows regions in the brain with no overlaps between activated voxels in BT but WT.
-For instance, left/right `V1\_ROI' in \fslafni and \fslspm, and left/right `TGd\_ROI' in \afnispm results.
-The regression line is computed over Dices where BT and WT are not zero.
-% The average of Dice scores range from to 
-% FSL-AFNI variations has the most similarity correlations which means that the results of these two tools are more \dots
-
-% In response to the out of border activated voxels can say:
-% This is likely due to the fact that SPM consistently had the smallest analysis mask out of the three packages,
-% while FSL had the largest. Number of activated voxels prove this fact.
+  %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
+  \begin{figure}[b]
+    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
+    \centering
+    \includegraphics[width=\columnwidth]{figures/dices_corr.png}
+    \caption{Correlation of Dice coefficients of activated regions in BT and WT
+    from the thresholded T-statistics. Different pairs are illustrated in different colors. 
+    Regions correspond to the 360 areas of cortical parcellation (HCP-MMP1.0)~\cite{glasser2016multi}.}
+    \label{fig:dice-thresh}
+    \end{minipage}}
+  \end{figure}
 
@@
     \end{subfigure}
-    \caption{Maps of standard deviation of unthresholded T-statistics. First and second rows show
-    maps on between-tool and within-tool results, respectively. Third row represents the ratio of differences
-    in between and within tools.}
+    \caption{Maps of standard deviation of unthresholded T-statistics. The first and second rows show
+    maps on BT and WT results, respectively, and the third row represents maps of the ratio between them.}
     \label{fig:unthresh-varmaps}
@@
 which indicates how correlation is uniformly distributed across the brain.
-% Spatial localization of significant activation in the thresholded images also varied across software packages.
-% Moreover, results show that pair of FSL-SPM has the least correlation of variability in within tool and between tool.
-% This will implies that ... which can help for further investigations.
 
@@
       \end{subfigure}
-      \caption{Correlation of variability in between-tool and within-tool variations in unthresholded maps. First row plots the correlations
-    voxel by voxel, which is highlighted with different colors for two major clusters including upper cluster (purple color) and
-    correlated cluster (green color) which are mapped on the brain in the second row.}
+      \caption{Correlation of standard deviations in BT and WT from the unthresholded T-statistics. 
+      The first row plots the correlations voxel by voxel and is highlighted with different colors
+      for two clusters, including the upper cluster (purple color) and the correlated cluster (green color).
+      The second row maps the correlated area on the MNI space.}
     \label{fig:correlations}

### 2021-09-27 paper/paper.tex
Add abstract and intro

@@
 
+Computational environments are known to affect the pipeline results in neuroimaging,
+presumably due to the creation, propagation, and amplification of small numerical errors.
+Numerical instability is a characteristic of the pipelines which amplify numerical errors
+originating in floating-point computations and then hamper reproducibility of the analyses.
+% It has been widely investigated that methodological flexibility can influence the final determined areas of brain activation.
+In particular, errors that highlight numerical instabilities are likely to appear as a result of changes in data analysis software packages.
+This work presents a comparative assessment of the group-level fMRI analysis between tool variability and numerical variability.   
+We characterize the effect of numerical perturbations on the fMRI analysis using the Fuzzy Libmath (FL) framework.
+FL is a technique to instrument the mathematical functions embedded in mathematical libraries based on the Monte-Carlo Arithmetic (MCA).
+We show that by taking advantage of the Fuzzy libmath framework, one can evaluate the numerical uncertainty of the pipelines. 
+We (1) evaluated the numerical stability of the fMRI analysis that has been reproduced using three of the most common tools in neuroimaging, FSL, AFNI, and SPM,
+and (2) compared between tool variability and numerical variability.
+We found a significant numerical variability on both thresholded and unthresholded images;
+results show that the order of magnitude of variations between tools was highly more than numerical variability.
+Also, we found a linear correlation between Dice scores computed region-by-region on thresholded maps in both conditions.
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
+  Numerical Instability, Reproducibility, Monte-Carlo Arithmetic, Neuroimaging
 \end{IEEEkeywords}
@@
 
-\begin{itemize}
-    \item We presented a framework that can investigate the numerical instability of the pipelines based on Monte-Carlo arithmetic
-    by creating a Fuzzy environment, so that instrument mathematical functions implemented in mathematical system libraries (libmath).
+% Data analysis workflows in many scientific domains have become increasingly complex and flexible. 
+Recent studies highlighted the instability of the neuroimaging pipelines depending on the computing platform,
+software package, and even tool versions. Changes in the computational
+environment such as compilers, libraries, operating systems may introduce small numerical errors and create
+significantly different results in unstable pipelines~\cite{Glatard2015,Gronenschild2012,salari2020spot}.
+Moreover, the impact of methodological changes on fMRI analyses has been investigated extensively~\cite{bowring2019exploring,botvinik2020variability,bhagwat2021understanding,carp2012plurality}.
+For instance, in related works, it has been shown that running the same fMRI experiments by different teams can substantially affect
+scientific conclusions~\cite{botvinik2020variability,carp2012plurality};
+replication of fMRI experiments using the three most well-known software packages can influence the final determining areas of
+brain activations~\cite{bowring2019exploring};%bowring2021isolating. 
+also, the choice of preprocessing pipelines on neuroimaging cortical surface analyses is compound with the instabilities~\cite{bhagwat2021understanding}.
+% In the presence of such instabilities, it is often hard to trust the data processing results. % validity of the computational results.
 
-    \item Methodological choice can influence the final determining areas of brain activation.
-    This opens so results flexibility~\cite{bowring2019exploring,bowring2021isolating}.
+In such a heterogeneous environment, numerical instability is an essential issue for reproducibility.
+Numerical instability is a characteristic of pipelines that results from the influence of the floating-point arithmetics
+and iterative convergence of numerical errors~\cite{freitas2002issue}.
+Stochastic arithmetic approaches such as Monte-Carlo Arithmetic (MCA)~\cite{Parker1997-qq} have been used to study the impact of numerical errors
+originating in floating-point computations in mathematical libraries.
+In~\cite{salari2021accurate}, we quantified the numerical stability of the HCP preprocessing pipeline~\cite{glasser2013} based on the MCA method by creating a Fuzzy environment
+, so that instrument mathematical functions are implemented in mathematical system libraries.
+As a result of numerical perturbations, we discovered a very low numerical precision in the result images comparable to the operating system variability.
+In a related study~\cite{kiar2020numerical}, the instability of results was explored by instrumenting a connectome estimation pipeline with the MCA technique.
+These works demonstrate the necessity of numerical uncertainty quantification for understanding related issues that hamper the computational reproducibility of analyses.
 
-    \item In this paper, we aim to answer the questions 1) how the fMRI analyses are numerically stable?
+In this work, we reproduce an fMRI experiment with different neuroimaging software packages in the presence of the Fuzzy environment,
+and then quantify the numerical variability and between tool variability in the results. 
+The primary objective of this study is to answer these two questions: 1) how the fMRI analyses across tools are numerically stable?
 2) how the numerical variability is in comparison with the tool variability?
-\end{itemize}
+This comparative study reveals the importance of numerical variability and motivates research studies to evaluate the numerical uncertainty of the pipelines.
+
+% We start to reproduce an analysis from Bowring, this can be as a practice for reproducibility manner in the community.
+% In particular, we investigate the effect of 1) between software 2) within software (numerical)
+% We present a comparative assessment of group-level analysis of an fMRI pipeline.
 
@@
 Finally, the instrumented functions are loaded in the pipeline using LD\_PRELOAD, a Linux environment variable
-to force load a shared library into an executable. ​
+to force load a shared library into an executable.
 This allows functions defined in FL to transparently
-overload the original ones without the need to modify or recompile the analysis pipeline.​
+overload the original ones without the need to modify or recompile the analysis pipeline.
 
@@
 is involved during the pipeline executions.
+
+% MCA allows for three perturbation modes: Random Rounding (RR) introduces the
+% perturbation in function outputs, simulating roundoff errors; Precision Bounding
+% (PB) introduces the perturbation in function operands, allowing for the
+% detection of catastrophic cancellations; and, Full MCA combines RR and PB,
+% resulting in the following perturbation:
+% \begin{equation} \label{eq:mca_modes}
+%   mca\_mode(x \circ y) = inexact_{RR}(  inexact_{PB}(x) \circ inexact_{PB}(y) )
+% \end{equation}
 
@@
 
+% In this case, differences in the number of threads raised floating point rounding errors.
+% So it's probabilistic to have this issue by changing the hardware architecture like variation in CPU, GPU, APU from intel, AMD, or Nvidia.
+% It still may suffer from Hyper-threading (often on intel CPUs), means a physical CPU core divides into different
+% virtual cores that allows more than one thread to run on each core. It says that you allocated one CPU, but virtually have multi-threads.
+
+% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
+% are responsible for disparities between pair of images.
+
 \section{Results}
@@
 including left/right `V1\_ROI' in \fslafni and \fslspm, and left/right `TGd\_ROI' in \afnispm results.
+% The regression line is computed over Dices where BT and WT are not zero.
+% The average of Dice scores range from to 
+% FSL-AFNI variations has the most similarity correlations which means that the results of these two tools are more \dots
+
+% In response to the out of border activated voxels can say:
+% This is likely due to the fact that SPM consistently had the smallest analysis mask out of the three packages,
+% while FSL had the largest. Number of activated voxels prove this fact.
 
@@
 \subsection{Group-level unthresholded maps}
+% \subsection{Variability of unthresholded statistical maps}
 
@@
 which indicates how correlation is uniformly distributed across the brain.
+% Spatial localization of significant activation in the thresholded images also varied across software packages.
+% Moreover, results show that pair of FSL-SPM has the least correlation of variability in within tool and between tool.
+% This will implies that ... which can help for further investigations.
 
@@
 
+% There are many statistical comparisons, but the neuro-scientific interpretation of results is not on my side.
+
 \begin{itemize}

### 2021-09-27 paper/paper.tex
remove comments
Minor edits on results

@@
 replication of fMRI experiments using the three most well-known software packages can influence the final determining areas of
-brain activations~\cite{bowring2019exploring};%bowring2021isolating. 
-also, the choice of preprocessing pipelines on neuroimaging cortical surface analyses is compound with the instabilities~\cite{bhagwat2021understanding}.
+brain activations~\cite{bowring2019exploring}; %bowring2021isolating.
+also, the choice of preprocessing pipelines on neuroimaging cortical surface analyses is compound with instabilities~\cite{bhagwat2021understanding}.
 % In the presence of such instabilities, it is often hard to trust the data processing results. % validity of the computational results.
@@
 originating in floating-point computations in mathematical libraries.
-In~\cite{salari2021accurate}, we quantified the numerical stability of the HCP preprocessing pipeline~\cite{glasser2013} based on the MCA method by creating a Fuzzy environment
-, so that instrument mathematical functions are implemented in mathematical system libraries.
+In~\cite{salari2021accurate}, we quantified the numerical stability of the HCP preprocessing pipeline~\cite{glasser2013} based on the MCA method
+by creating a Fuzzy environment, so that instrument mathematical functions are implemented in mathematical system libraries.
 As a result of numerical perturbations, we discovered a very low numerical precision in the result images comparable to the operating system variability.
@@
 is involved during the pipeline executions.
-
-% MCA allows for three perturbation modes: Random Rounding (RR) introduces the
-% perturbation in function outputs, simulating roundoff errors; Precision Bounding
-% (PB) introduces the perturbation in function operands, allowing for the
-% detection of catastrophic cancellations; and, Full MCA combines RR and PB,
-% resulting in the following perturbation:
-% \begin{equation} \label{eq:mca_modes}
-%   mca\_mode(x \circ y) = inexact_{RR}(  inexact_{PB}(x) \circ inexact_{PB}(y) )
-% \end{equation}
 
@@
 
-% In this case, differences in the number of threads raised floating point rounding errors.
-% So it's probabilistic to have this issue by changing the hardware architecture like variation in CPU, GPU, APU from intel, AMD, or Nvidia.
-% It still may suffer from Hyper-threading (often on intel CPUs), means a physical CPU core divides into different
-% virtual cores that allows more than one thread to run on each core. It says that you allocated one CPU, but virtually have multi-threads.
-
-% EC is a means to assess whether only superficial scaling differences (differences by a scale factor over all voxels) 
-% are responsible for disparities between pair of images.
-
 \section{Results}
@@
 including left/right `V1\_ROI' in \fslafni and \fslspm, and left/right `TGd\_ROI' in \afnispm results.
-% The regression line is computed over Dices where BT and WT are not zero.
-% The average of Dice scores range from to 
-% FSL-AFNI variations has the most similarity correlations which means that the results of these two tools are more \dots
-
-% In response to the out of border activated voxels can say:
-% This is likely due to the fact that SPM consistently had the smallest analysis mask out of the three packages,
-% while FSL had the largest. Number of activated voxels prove this fact.
 
@@
 We found two major clusters, including the identity cluster that corresponds to the correlations
-between BT and WT with the ratio of $0.5 < BT/WT < 1.5$,
+between BT and WT with the ratio of $0.5 < BT/WT < 1.5$ where the standard deviations are bigger than 0.1,
 and the upper cluster that shows voxels where BT $\approx$ 0.
 The percentage of voxels included in the identity cluster is \%9.9 in \fslspm, \%17.3 in \fslafni, and \%13.8 in \afnispm,
-and total voxels in the upper cluster are $\approx$ \%1.
+and in the upper cluster is $\approx$ \%1 for each pair of tools.
 The identity area is also represented on the MNI space in the second row in Figure~\ref{fig:correlations}.

### 2021-09-28 paper/paper.tex

@@
 \newcommand{\afnispm}{AFNI-SPM\xspace}
+\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}
 
@@
 
-Computational environments are known to affect the pipeline results in neuroimaging,
-presumably due to the creation, propagation, and amplification of small numerical errors.
-Numerical instability is a characteristic of the pipelines which amplify numerical errors
-originating in floating-point computations and then hamper reproducibility of the analyses.
-% It has been widely investigated that methodological flexibility can influence the final determined areas of brain activation.
-In particular, errors that highlight numerical instabilities are likely to appear as a result of changes in data analysis software packages.
-This work presents a comparative assessment of the group-level fMRI analysis between tool variability and numerical variability.   
-We characterize the effect of numerical perturbations on the fMRI analysis using the Fuzzy Libmath (FL) framework.
-FL is a technique to instrument the mathematical functions embedded in mathematical libraries based on the Monte-Carlo Arithmetic (MCA).
-We show that by taking advantage of the Fuzzy libmath framework, one can evaluate the numerical uncertainty of the pipelines. 
-We (1) evaluated the numerical stability of the fMRI analysis that has been reproduced using three of the most common tools in neuroimaging, FSL, AFNI, and SPM,
-and (2) compared between tool variability and numerical variability.
-We found a significant numerical variability on both thresholded and unthresholded images;
-results show that the order of magnitude of variations between tools was highly more than numerical variability.
-Also, we found a linear correlation between Dice scores computed region-by-region on thresholded maps in both conditions.
+Numerical and software variability broadly affect structural, diffusion, and functional MRI analyses. Numerical
+variability originates in software updates or code
+parallelization, whereas software variability reflects discrepancies between
+models implemented in different analysis software packages. While numerical
+and software variability were both shown to impact analysis outcomes, the
+extent to which these sources of variability compare for a given
+analysis remains understudied. This work presents a comparison of
+numerical and software variability for group-level functional MRI analysis
+\tristan{did we give up on individual analyses?}.
+We reproduced a previous comparison between functional MRI analysis 
+software packages FSL, AFNI, and SPM, which we extended to measure 
+numerical variability through Monte-Carlo arithmetic. 
+We find that between-tool variability is an order of magnitude higher than numerical variability.
+\tristan{summarize conclusions}
 

### 2021-09-28 paper/paper.tex
Fix colorbar resolution

@@
 \newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}
+\newcommand{\note}[2]{\color{green}\textbf{Note:} #1\color{black}\xspace}
 
@@
 % Overally, we see that values in between tools are comparable to values in within tool results.
+\note{Add statistics for subject level (first-level) analyses}
 
@@
 We found two major clusters, including the identity cluster that corresponds to the correlations
-between BT and WT with the ratio of $0.5 < BT/WT < 1.5$ where the standard deviations are bigger than 0.1,
+between BT and WT with the ratio of $0.5 < BT/WT < 2$ where the standard deviations are bigger than 0.1,
 and the upper cluster that shows voxels where BT $\approx$ 0.

### 2021-09-30 paper/paper.tex
Comments in methods and first part of results

--- 2021-09-28 paper/paper.tex
@@
 
-To simulate the machine-level uncertainty, we used the method introduced in~\cite{salari2021accurate} called Fuzzy libmath (FL).
-FL uses Monte Carlo Arithmetic (MCA) to introduce a controlled amount of noise in the floating-point operations
+To simulate the machine-level uncertainty \tristan{introduce machine-level
+uncertainty}, we used the method introduced in~\cite{salari2021accurate}
+called Fuzzy libmath (FL). FL uses Monte Carlo Arithmetic (MCA) to
+introduce a controlled amount of noise in the floating-point operations \tristan{not in all of them}
 through the following perturbation model:
@@
 which models floating-point rounding and catastrophic cancellation errors.
-This is automated using Verificarlo tool~\cite{denis2015verificarlo} that implements MCA in the compilation time.
+This is automated using Verificarlo tool~\cite{denis2015verificarlo} that implements MCA at compilation time.
 
-With the goal of OS-level perturbations, this framework instruments mathematical functions embedded
-in the mathematical library in GNU operating systems, libmath.
+With the goal of OS-level perturbations \tristan{what does it mean?}, this framework instruments mathematical functions embedded
+in the mathematical library \tristan{tautology} in GNU operating systems, libmath.
 To avoid some pitfalls in deterministic arithmetics like producing results out of the function definition,
@@
 is perturbed instead of input or their implementation.
-This is achieved by adding a floating-point zero to the output of the original function so that the result of this summation
+This is achieved by adding a floating-point zero to the output of the original function \tristan{no way to understand from the text why adding a zero would introduce noise} so that the result of this summation
 is perturbed and returned.
 Listing~\ref{algo:wrapper} shows an example of this wrapping for the log function in both single and double precisions.
-In this script, the original functions are called by \texttt{dlsym}, a function that returns the memory address of a symbol
+In this script, the original functions are called by \texttt{dlsym} \tristan{this can't be understood unless the ldpreload trick is mentioned before}, a function that returns the memory address of a symbol
 using the handle of \texttt{RTLD\_NEXT}.
@@
 
-This technique allows measuring the effect of numerical variability by running a program multiple times
+FL allows measuring the effect of numerical variability by running a program multiple times
 with the feature of controlling the magnitude of the perturbations as perceived by the application.
-Moreover, FL enables us to assess the software packages that are dynamically linked to the mathematical libraries.
+FL enables us to assess the software packages that are dynamically linked to the mathematical libraries.
 So, it is important to trace the tool dependencies of the pipelines to ensure that the specific mathematical library
-is involved during the pipeline executions.
+is involved during the pipeline executions. \tristan{``is involved'' is required but not sufficient. How do you guarantee that 
+no other math functions are called on the side?}
 
@@
 
-We replicated the fMRI analysis described as study `ds000001' in~\cite{bowring2019exploring}
-with the publicly available data repository in~\href{https://openneuro.org/datasets/ds000001}{OpenNeuro}
-using the three well-known software packages for fMRI data processing, including
-FSL~\cite{jenkinson2012fsl}, AFNI~\cite{cox1996afni}, and SPM~\cite{penny2011statistical}.
-We selected this publication to replicate the fMRI analysis because the methods and sources were explicitly
-written to be accessible and reproducible. This enabled us to reanalyze tests using the FL framework and
-compare results with the between tool variability.
+We replicated the fMRI analysis described as study `ds000001' in~\cite{bowring2019exploring}, relying on
+the data publicly available in OpenNeuro at \url{https://openneuro.org/datasets/ds000001}
+and using the three main software packages for fMRI data processing, namely
+FSL~\cite{jenkinson2012fsl}, AFNI~\cite{cox1996afni}, and SPM~\cite{penny2011statistical} \tristan{expand acronyms}.
+We selected this analysis because the methods and sources \tristan{what do you mean? data?} were explicitly
+written to be accessible and reproducible. This enabled us to reanalyze tests \tristan{``tests'' isn't understandable} using the FL framework and
+compare results with the between tool variability \tristan{``between tool variability isn't understandable"}.
 
@@
 package could be compared objectively.
-A full description of the pipelines implemented within three packages is presented in the original
-study~\cite{bowring2019exploring,schonberg2012decreasing}.
+A full description of the pipelines implemented within three packages is presented in~\cite{bowring2019exploring,schonberg2012decreasing}.
 
@@
       \end{tabular}
-    \caption{Software processing steps. This table is adopted from~\cite{bowring2019exploring}.}
+    \caption{Software processing steps. Table is adapted from~\cite{bowring2019exploring}.}
     \label{table:pipeline-steps}
@@
 packages in neuroimaging, including FSL (version 5.0.10), AFNI (version 18.1.09), and SPM (version SPM12, r7771)
-on Octave (version 5.2). The analyses were conducted on the same operating system, CentOS 7.3.
+executed with GNU/Octave (version 5.2). The analyses were conducted on the same operating system, CentOS 7.3.
 % The computations were performed on a cluster comprised of ...
-We ensured that the software versions and all the requisites for running analyses used in all experiments 
-were similar to the original study and encapsulated in Docker images.
+We ensured that the software versions and all the requisites \tristan{unclear what these are} for running analyses used in all experiments 
+were similar to the original study and we encapsulated them in Docker container images.
 % We could replicate results of the original study except for AFNI with slightly differences due to the parallelization\dots
@@
 
-In addition, the same subjects and fMRI analysis were processed with the same configurations in the Fuzzy libmath environment
+In addition, the same subjects and fMRI analysis were processed with the same configurations in the FL environment
 to produce the numerical variability results.
-We only perturbed the maximum precisions to compare uncertainty between tool variability and numerical instability at the level of OS.
-For this purpose, we applied instrumentations at the virtual precision (t) of 53 bits for the double-precision variable
-and 24 bits for the single-precision variable. Three Fuzzy samples were generated at these precisions to match the number of tool samples.
+We only perturbed the maximum precisions \tristan{``the maximum precisions'' cannot be understood} to compare uncertainty between tool variability and numerical instability at the level of OS.
+For this purpose, we applied instrumentations at the virtual precision (t) of 53 bits for double-precision floating-point values
+and 24 bits for  single-precision values. Three Fuzzy samples were generated, to match the number of tool samples.
 
-We evaluated variabilities in (un)thresholded group-level activation maps.
-We statistically computed standard deviations between T-statistic values for each pair of tools
-and then compared the correlation of changes in both conditions.
-The standard deviation between fuzzy samples corresponds to the square root of the summation of variances between samples in each tool.
-Moreover, we determined region-by-region Dice coefficients for the thresholded maps for each pair of tools.
+We evaluated variabilities \tristan{define them, introduce BT and WT acronyms} in thresholded and unthresholded group-level activation maps.
+We statistically computed \tristan{what's a ``statistical computation''?} voxel-wise standard deviations \tristan{did you check standard error vs standard deviation?} of T-statistic values for each pair of tools
+and then compared the correlation of changes \tristan{idk what's a ``correlation of changes''} in both conditions.
+The standard deviation between fuzzy samples corresponds to the square root of the summation of variances between samples in each tool \tristan{Rephrase: we computed the WT standard deviation as ...}.
+Moreover, we determined region-by-region Dice coefficients for the thresholded maps for each pair of tools \tristan{Explain more. You should add least mention the parcellation used.}.
 % This measured the overlap of acitaved voxels which assess the spatial similarity between activated maps.
@@
 \section{Results}
-All scripts and results to create the figures in this section are available on GitHub repository
-in \url{https://github.com/ali4006/fuzzy-neurotools}.
-Replication of all analyses was visually assessed to be the same as the original study.
-We ensured that fMRI analyses were processed successfully.
+All scripts and results to create the figures in this section are available at \url{https://github.com/ali4006/fuzzy-neurotools}.
+Replication of all analyses was visually assessed \tristan{mention what you checked specifically} to be the same as the original study \tristan{cite}.
+We ensured that fMRI analyses were processed successfully \tristan{how?}.
 In this section, we call the cross-software variation and numerical variation,
-between tool (BT) and within tool (WT) variability, respectively. 
-The within tool variability shows results among different fuzzy libmath
-samples for the specific version of the tools, and it is not within tool versions.c
+between tool (BT) and within tool (WT) variability, respectively \tristan{introduce these notations as early as possible in the methods}. 
+The within tool variability shows results among different fuzzy libmath \tristan{capitalize consistently}
+samples for the specific version of the tools, and it is not within tool versions \tristan{sentence is cryptic}.
 
-A summary of the statistic values from the group-level (un)thresholded T-statistics is conducted in
+Summary statistics for the group-level (un)thresholded T-statistics are shown in
 Table~\ref{table:pipeline-stats}.
-The variability between pair of images in each condition was measured using the mean and standard deviation of absolute differences.
+The variability between pair of images \tristan{images means MRI} in each condition was measured using the mean and standard deviation of absolute differences \tristan{then call them abs diff in the table}.
 Overall, the distribution of the pairwise variations in WT is an order of magnitude lower than BT in both means and standard deviations.
-While the most variability was observed in the pair of \fslafni, the pair of \fslspm made the least variations for all conditions.
+While the highest variability was observed for \fslafni, \fslspm made the least variations for all conditions.
 % Overally, we see that values in between tools are comparable to values in within tool results.
+\tristan{it's unclear what ``Fuzzy X and Y'' represent.}
 
@@
     \end{tabular}
-    \caption{Summary of T-statistics mean and standard deviation of differences for each pair of tools.}
+    \caption{Summary of T-statistics mean and standard deviation of differences for each pair of tools \tristan{only pairs of tools? Add voxel-wise to this caption.}.}
     \label{table:pipeline-stats}

### 2021-09-30 paper/paper.tex

@@
 \tristan{it's unclear what ``Fuzzy X and Y'' represent.}
+\note{Add statistics for subject level (first-level) analyses}
 

### 2021-09-30 paper/paper.tex
Add subject-level results

@@
 %%%%%%%%%% Summary of statstics %%%%%%%%
-\setlength{\tabcolsep}{5pt}
+\setlength{\tabcolsep}{7pt}
 \begin{table}[h]
     \centering
-    \begin{tabular}{ccc|cc}
+    \begin{tabular}{cccc|cc}
         \toprule
-        \multirow{2}{*}{} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c}{Unthresholded} \\
-        \cmidrule{2-3} \cmidrule{4-5} \\
-        {} & Mean diff. & Std. diff. & Mean diff. & Std. diff. \\
+        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c}{Unthresholded} \\
+        \cmidrule{3-4} \cmidrule{5-6} \\
+        {} & {} & Mean & Std. dev. & Mean & Std. dev. \\
         \midrule
         \rowcolor{lightgray}
-        FSL vs. SPM          &  0.043       & 1.282      & 0.242     & 0.443  \\
+        {BT} & FSL vs. SPM          &  0.043       & 1.282      & 0.242     & 0.443  \\
         \rowcolor{lightgray}
-        FSL vs. AFNI         &  0.099       & 1.548      & 0.302     & 0.547  \\
+        {} & FSL vs. AFNI         &  0.099       & 1.548      & 0.302     & 0.547  \\
         \rowcolor{lightgray}
-        AFNI vs. SPM         &  0.079       & 1.475      & 0.254     & 0.608  \\
-        Fuzzy FSL and SPM    &  0.005       & 0.358      & 0.030     & 0.099  \\
-        Fuzzy FSL and AFNI   &  0.011       & 0.475      & 0.038     & 0.155  \\
-        Fuzzy AFNI and SPM   &  0.011       & 0.458      & 0.033     & 0.144  \\
+        {} & AFNI vs. SPM         &  0.079       & 1.475      & 0.254     & 0.608  \\
+        {WT} & FSL and SPM    &  0.005       & 0.358      & 0.030     & 0.099  \\
+        {} & FSL and AFNI   &  0.011       & 0.475      & 0.038     & 0.155  \\
+        {} & AFNI and SPM   &  0.011       & 0.458      & 0.033     & 0.144  \\
         \bottomrule
     \end{tabular}
-    \caption{Summary of T-statistics mean and standard deviation of differences for each pair of tools \tristan{only pairs of tools? Add voxel-wise to this caption.}.}
+    \caption{Summary of voxel-wise mean and standard deviation of absolute differences for each pair of tools
+    in group-level T-statistics.}
     \label{table:pipeline-stats}
@@
 Comparisons of standard deviations between thresholded images in WT and BT
-on MNI space are shown in Figure~\ref{fig:thresh-varmaps}.
+on MNI space are shown in Figure~\ref{fig:thresh-maps}.
 
@@
 in some regions in the thresholded images.
-For instance, some parts of the frontal lobe in the sagittal plane for almost all pairs and the occipital lobe in the axial plane
-for the pairs of \fslspm and \fslafni in Figure~\ref{fig:unthresh-varmaps}
-are closely replicated using the numerical perturbations.
+\note{For instance, some parts of the frontal lobe in the sagittal plane for almost all pairs and the occipital
+lobe in the axial plane for the pairs of \fslspm and \fslafni in Figure~\ref{fig:thresh-maps}
+are closely replicated using the numerical perturbations.}
 
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \label{fig:thresh-varmaps1}
     \end{subfigure}
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \label{fig:thresh-ratiomaps}
     \end{subfigure}
@@
     %and vise versa for the darkder regions.}
-    \label{fig:thresh-varmaps}
+    \label{fig:thresh-maps}
     \end{minipage}}
@@
 % Fig3
-Figure~\ref{fig:unthresh-varmaps} shows the brain maps of standard deviations for group-level unthresholded T-statistics in WT and BT.
+Figure~\ref{fig:unthresh-maps} shows the brain maps of standard deviations for group-level unthresholded T-statistics in WT and BT.
 Results show a different magnitude of
@@
 
-%%%%%%%%%% Var. of Thresh %%%%%%%%
+%%%%%%%%%% Var. of Unthresh %%%%%%%%
 \begin{figure*}[b]
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \label{fig:unthresh-varmaps1}
     \end{subfigure}
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \label{fig:unthresh-ratiomaps}
     \end{subfigure}
@@
     maps on BT and WT results, respectively, and the third row represents maps of the ratio between them.}
-    \label{fig:unthresh-varmaps}
+    \label{fig:unthresh-maps}
     \end{minipage}}
@@
 % Fig4
-The scatter plot in Figure~\ref{fig:correlations} represents the correlation of standard deviation in WT and BT variability.
+The scatter plot in Figure~\ref{fig:unthresh-correlation} represents the correlation of standard deviation in WT and BT variability.
 We found two major clusters, including the identity cluster that corresponds to the correlations
@@
 and in the upper cluster is $\approx$ \%1 for each pair of tools.
-The identity area is also represented on the MNI space in the second row in Figure~\ref{fig:correlations}.
+The identity area is also represented on the MNI space in the second row in Figure~\ref{fig:unthresh-correlation}.
 This figure shows the spatial localization of the parts of the brain that BT variability is correlated with the numerical variability.
-This refines the presented results in Figure~\ref{fig:unthresh-varmaps},
+This refines the presented results in Figure~\ref{fig:unthresh-maps},
 which indicates how correlation is uniformly distributed across the brain.
@@
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
-        \label{fig:unthresh-corrplot}
       \end{subfigure}
@@
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
-        \label{fig:unthresh-corrmaps}
       \end{subfigure}
@@
       The second row maps the correlated area on the MNI space.}
-    \label{fig:correlations}
+    \label{fig:unthresh-correlation}
+    \end{minipage}}
+  \end{figure*}
+
+  \subsection{Subject-level unthresholded maps}
+
+  Table~\ref{table:firstlevel-stats} shows a summary of the statistics from the subject-level analysis results.
+  This table represents the average of the mean and standard deviation of absolute differences of unthresholded T-statistics
+  across 16 subjects for each pair of tools.
+  Results show that subjects 15 and 10 were produced the least and the most variability, respectively, among all pairs, subjects,
+  and both BT and WT.
+  While subject 15 generated results with the mean of $\approx$ 0.093 and standard deviation of $\approx$ 0.174,
+  subject 10 produced results with the mean of $\approx$ 0.183 and standard deviation of $\approx$ 0.341.
+  This observation shows an order of magnitude of variability between subjects.
+  % The most variability for \fslspm appeared in subject 1 in BT and subject 11 in WT, and for \fslafni
+  % and \afnispm subject 10 in BT and subject 5 in WT were the most variable subjects.
+  Moreover, Figure~\ref{fig:unthresh-firstlevel} shows the maps of standard deviations on MNI space in WT and BT for subjects 15 and 10.
+  We can see a significant variability between subjects.
+
+%%%%%%%%%% Summary of statstics %%%%%%%%
+\setlength{\tabcolsep}{5pt}
+\begin{table*}[h]
+    \centering
+    \begin{tabular}{cccc|cc|cc}
+        \toprule
+        \multirow{2}{*}{} &{} & \multicolumn{2}{c}{All Subjects} & \multicolumn{2}{c}{Least variable} & \multicolumn{2}{c}{Most variable} \\
+        \cmidrule{3-4} \cmidrule{5-6} \cmidrule{7-8} \\
+        {} & {} & Mean  & Std. dev.  & Mean & Std. dev. & Mean  & Std. dev. \\
+        \midrule
+        \rowcolor{lightgray}
+        {BT} & FSL vs. SPM           & 0.245     & 0.366       & 0.166     & 0.255    & 0.273    & 0.405  \\
+        \rowcolor{lightgray}
+        {}   & FSL vs. AFNI          & 0.295     & 0.439      & 0.183     & 0.282     & 0.392    & 0.582  \\
+        \rowcolor{lightgray}
+        {}   & AFNI vs. SPM          & 0.238     & 0.491      & 0.150     & 0.314     & 0.310    & 0.642  \\
+        {WT} & FSL and SPM    & 0.033     & 0.092      & 0.018     & 0.050     & 0.036    & 0.099  \\
+        {}   & FSL and AFNI   & 0.040     & 0.136      & 0.021     & 0.075     & 0.048    & 0.165  \\
+        {}   & AFNI and SPM   & 0.033     & 0.124      & 0.019     & 0.071     & 0.039    & 0.155  \\
+        \bottomrule
+    \end{tabular}
+    \caption{Summary of voxel-wise mean and standard deviation of absolute differences for each pair of tools
+    in subject-level T-statistics.}
+    \label{table:firstlevel-stats}
+\end{table*}
+
+  %%%%%%%%%% Var. of Unthresh %%%%%%%%
+  \begin{figure*}[b]
+    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+      \centering
+      \includegraphics[width=\textwidth]{figures/sbj-level-bt-wt-unthresh-std.pdf}
+    \caption{Maps of standard deviation of unthresholded T-statistics from subject 15 in the rows A and B,
+    and subject 10 in the rows C and D.}
+    \label{fig:unthresh-firstlevel}
     \end{minipage}}

### 2021-09-30 computs.py

@@ -5,119 +5,95 @@ import scipy
 import scipy.spatial
 import nibabel as nib
 import numpy as np
-import warnings
 import matplotlib as mpl
 import matplotlib.pyplot as plt
-import math
 import pickle as pkl
 import inspect
-import os
 from nilearn.image import math_img
-#import seaborn as sns
-import pandas as pd
-from mpl_toolkits.axes_grid1 import make_axes_locatable
-from lib import bland_altman
 from lib import dice
 from statistics import mean
+import os
 
 
 ############# COMPUTES STD. DEV.
 
-def compute_var(f1, f2, file_name, f3=None):
+def compute_var(f1, f2, file_name=None, f3=None):
     # Compute std. between tool image samples
     f1 = nib.load(f1)
-    f2 = nib.load(f2)
     img_concat = nib.funcs.concat_images([f1, f2], check_affines=True, axis=None)
     img_std = np.std(img_concat.get_fdata(), axis=3)
-    # Extract background
-    # f1_mask = set_zero_to_nan(f1)
-    # f2_mask = set_zero_to_nan(f2)
-    # bg_ = np.logical_and(np.isnan(f1_mask.get_fdata()), np.isnan(f2_mask.get_fdata()))
 
     # Compute variance between fuzzy image samples
     if f3 is not None:
-        # f3 = nib.load(f3)
-        # f3_mask = set_zero_to_nan(f3)
-        # bg_ = np.logical_and(np.isnan(f1_mask.get_fdata()), np.isnan(f2_mask.get_fdata()), np.isnan(f3_mask.get_fdata()))
         img_concat = nib.funcs.concat_images([f1, f2, f3], check_affines=True, axis=None)
         img_var = np.var(img_concat.get_fdata(), axis=3)
-        # set background voxels as nan to not display later
-        # img_var[bg_] = np.nan
         nft_img = nib.Nifti1Image(img_var, f1.affine, header=f1.header)
-        nib.save(nft_img, './figures/map-on-surf/std/{}-var.nii.gz'.format(file_name))
-        img_std = np.std(img_concat.get_fdata(), axis=3)
+        return nft_img
 
+    # nan bg images
     img_std[img_std == 0] = np.nan
[…]

### 2021-10-04 paper/paper.tex
Edit comments and update subject-level results

@@
 \newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}
-\newcommand{\note}[2]{\color{green}\textbf{Note:} #1\color{black}\xspace}
+\newcommand{\ali}[2]{\color{green}\textbf{Ali:} #1\color{black}\xspace}
 
@@
 \begin{IEEEkeywords}
-  Numerical Instability, Reproducibility, Monte-Carlo Arithmetic, Neuroimaging
+  Numerical Instability, Reproducibility, Monte-Carlo arithmetic, Neuroimaging
 \end{IEEEkeywords}
@@
 and iterative convergence of numerical errors~\cite{freitas2002issue}.
-Stochastic arithmetic approaches such as Monte-Carlo Arithmetic (MCA)~\cite{Parker1997-qq} have been used to study the impact of numerical errors
+Stochastic arithmetic approaches such as Monte-Carlo arithmetic (MCA)~\cite{Parker1997-qq} have been used to study the impact of numerical errors
 originating in floating-point computations in mathematical libraries.
@@
 
-In this work, we reproduce an fMRI experiment with different neuroimaging software packages in the presence of the Fuzzy environment,
-and then quantify the numerical variability and between tool variability in the results. 
+In this work, we reproduce an fMRI analysis in~\cite{bowring2019exploring} with different neuroimaging software packages in the presence of the Fuzzy environment,
+and then quantify the variability across tools and the numerical variability in results.
+We call the cross-software variation and numerical variation, between tool (BT) and within tool (WT) variability, respectively.
+In fact, the WT variability shows results across software packages in the Fuzzy environment.
 The primary objective of this study is to answer these two questions: 1) how the fMRI analyses across tools are numerically stable?
@@
 
-To simulate the machine-level uncertainty \tristan{introduce machine-level
-uncertainty}, we used the method introduced in~\cite{salari2021accurate}
-called Fuzzy libmath (FL). FL uses Monte Carlo Arithmetic (MCA) to
-introduce a controlled amount of noise in the floating-point operations \tristan{not in all of them}
+To simulate uncertainty close to the level of machine error,
+the maximum relative error due to rounding in floating-point arithmetic,
+we used the method introduced in~\cite{salari2021accurate}
+called Fuzzy libmath (FL). FL uses MCA to
+% create an instrumented version of the functions embedded in the mathematical library in GNU operating systems (libmath) in which
+introduce a controlled amount of noise in the floating-point operations embedded
+in the mathematical library in GNU operating systems (libmath)
 through the following perturbation model:
@@
 
-With the goal of OS-level perturbations \tristan{what does it mean?}, this framework instruments mathematical functions embedded
-in the mathematical library \tristan{tautology} in GNU operating systems, libmath.
+The instrumented functions are loaded in the pipeline using LD\_PRELOAD, a Linux environment variable
+to force load a shared library into an executable. This allows functions defined in FL to transparently
+overload the original ones without the need to modify or recompile the analysis pipeline.
+
 To avoid some pitfalls in deterministic arithmetics like producing results out of the function definition,
@@
 is perturbed instead of input or their implementation.
-This is achieved by adding a floating-point zero to the output of the original function \tristan{no way to understand from the text why adding a zero would introduce noise} so that the result of this summation
-is perturbed and returned.
 Listing~\ref{algo:wrapper} shows an example of this wrapping for the log function in both single and double precisions.
-In this script, the original functions are called by \texttt{dlsym} \tristan{this can't be understood unless the ldpreload trick is mentioned before}, a function that returns the memory address of a symbol
-using the handle of \texttt{RTLD\_NEXT}.
+In this script, the original functions are called by \texttt{dlsym},
+a function that returns the memory address of a symbol using the handle of \texttt{RTLD\_NEXT}.
 This allows one to provide a wrapper around a function in another shared library.
+Also, the MCA instrumentation is activated by adding a floating-point zero to the output of the original function
+so that the result of this summation is perturbed and returned.
 
@@
 
-Finally, the instrumented functions are loaded in the pipeline using LD\_PRELOAD, a Linux environment variable
-to force load a shared library into an executable.
-This allows functions defined in FL to transparently
-overload the original ones without the need to modify or recompile the analysis pipeline.
-
 FL allows measuring the effect of numerical variability by running a program multiple times
 with the feature of controlling the magnitude of the perturbations as perceived by the application.
-FL enables us to assess the software packages that are dynamically linked to the mathematical libraries.
-So, it is important to trace the tool dependencies of the pipelines to ensure that the specific mathematical library
-is involved during the pipeline executions. \tristan{``is involved'' is required but not sufficient. How do you guarantee that 
-no other math functions are called on the side?}
+FL enables us to assess the software packages that are dynamically linked to the mathematical library.
+So, it is important to trace the tool dependencies of the pipelines to understand the different libraries
+involved during the pipeline executions.
 
@@
 and using the three main software packages for fMRI data processing, namely
-FSL~\cite{jenkinson2012fsl}, AFNI~\cite{cox1996afni}, and SPM~\cite{penny2011statistical} \tristan{expand acronyms}.
-We selected this analysis because the methods and sources \tristan{what do you mean? data?} were explicitly
-written to be accessible and reproducible. This enabled us to reanalyze tests \tristan{``tests'' isn't understandable} using the FL framework and
-compare results with the between tool variability \tristan{``between tool variability isn't understandable"}.
+FMRIB Software Library (FSL)~\cite{jenkinson2012fsl}, Analysis of Functional NeuroImages (AFNI)~\cite{cox1996afni},
+and Statistical Parametric Mapping(SPM)~\cite{penny2011statistical}.
+We selected this analysis because the methods and datasets were explicitly
+written to be accessible and reproducible. This enabled us to reanalyze fMRI experiments using the FL framework and
+compare WT and BT variabilities.
 
@@
 
-To capture variability between tools, the fMRI analysis pipeline was processed using three of the most popular software
+To capture variability in BT, the fMRI analysis pipeline was processed using three of the most popular software
 packages in neuroimaging, including FSL (version 5.0.10), AFNI (version 18.1.09), and SPM (version SPM12, r7771)
-executed with GNU/Octave (version 5.2). The analyses were conducted on the same operating system, CentOS 7.3.
-% The computations were performed on a cluster comprised of ...
-We ensured that the software versions and all the requisites \tristan{unclear what these are} for running analyses used in all experiments 
-were similar to the original study and we encapsulated them in Docker container images.
-% We could replicate results of the original study except for AFNI with slightly differences due to the parallelization\dots
-% We also used SPM/Octave instead of Matlab to be able to run analysis in HPC and also perturb mathmetical functions
-% because Matlab has no dependencies on the GNU mathematical library, and it uses its libraries\dots
+executed with GNU/Octave (version 5.2). 
+FSL and AFNI scripts were executed in Python 2.7. We also used a fixed number of 7 threads in AFNI executions
+to produce the similar results to the original study in a feasible execution time.
+We also executed SPM with Octave instead of Matlab to enable GNU mathematical library instrumentations
+since Matlab uses its built-in mathematical functions.
+All the analyses were conducted on the same operating system, CentOS 7.3.
+We ensured that the software versions used in all experiments were similar to the original study,
+and encapsulated them in Docker container images with available Dockerfiles at \url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}.
 
 In addition, the same subjects and fMRI analysis were processed with the same configurations in the FL environment
-to produce the numerical variability results.
-We only perturbed the maximum precisions \tristan{``the maximum precisions'' cannot be understood} to compare uncertainty between tool variability and numerical instability at the level of OS.
-For this purpose, we applied instrumentations at the virtual precision (t) of 53 bits for double-precision floating-point values
+to produce results in WT variability.
+We applied instrumentations at the virtual precision (t) of 53 bits for double-precision floating-point values
 and 24 bits for single-precision values. Three Fuzzy samples were generated, to match the number of tool samples.
 
-We evaluated variabilities \tristan{define them, introduce BT and WT acronyms} in thresholded and unthresholded group-level activation maps.
-We statistically computed \tristan{what's a ``statistical computation''?} voxel-wise standard deviations \tristan{did you check standard error vs standard deviation?} of T-statistic values for each pair of tools
-and then compared the correlation of changes \tristan{idk what's a ``correlation of changes''} in both conditions.
-The standard deviation between fuzzy samples corresponds to the square root of the summation of variances between samples in each tool \tristan{Rephrase: we computed the WT standard deviation as ...}.
-Moreover, we determined region-by-region Dice coefficients for the thresholded maps for each pair of tools \tristan{Explain more. You should add least mention the parcellation used.}.
+We evaluated WT and BT variabilities in thresholded and unthresholded group-level activation maps.
+We computed voxel-wise standard deviations
+\tristan{did you check standard error vs standard deviation?}\ali{STD shows variability of data in relation to the mean (what we are looking for here),
+while SE is a type of STD (computed as $\frac{\sigma}{\sqrt{n}}$) for distribution of means (we use it when we are interested in the precision of means in different samples).} of T-statistic values for each pair of tools
+and then compared the distribution of standard deviations in both conditions.
+We computed the WT standard deviation as the square root of the summation of variances between samples in each tool.
+Moreover, we determined region-by-region Dice coefficients for the thresholded maps for each pair of tools.
+We characterized 360 regions that correspond to the cortical parcellation atlas
+in Human Connectome Project Multi-Modal Parcellation version 1.0 (HCP-MMP1.0)~\cite{glasser2016multi}.
+We computed the WT Dice values as the average pair-wise Dices computed among three Fuzzy samples for each pair of tools.
+Also, we compared the correlation of Dice scores normalized by the region sizes in both conditions.
 % This measured the overlap of acitaved voxels which assess the spatial similarity between activated maps.
-The Dice values between Fuzzy samples correspond to the average pair-wise Dices computed among three Fuzzy samples
-for each pair of tools.
-Also, we compared the correlation of Dice scores normalized by the region sizes in both conditions.
 
@@
 All scripts and results to create the figures in this section are available at \url{https://github.com/ali4006/fuzzy-neurotools}.
-Replication of all analyses was visually assessed \tristan{mention what you checked specifically} to be the same as the original study \tristan{cite}.
-We ensured that fMRI analyses were processed successfully \tristan{how?}.
-In this section, we call the cross-software variation and numerical variation,
-between tool (BT) and within tool (WT) variability, respectively \tristan{introduce these notations as early as possible in the methods}. 
-The within tool variability shows results among different fuzzy libmath \tristan{capitalize consistently}
-samples for the specific version of the tools, and it is not within tool versions \tristan{sentence is cryptic}.
+The computations were performed on \href{https://www.computecanada.ca}{the Compute Canada's} Béluga cluster
+with 872 available nodes containing 2× Intel Gold 6148 Skylake @ 2.4 GHz (40 cores/node) CPU and node memory ranging from 92 to 752 GB.
 
-Summary statistics for the group-level (un)thresholded T-statistics are shown in
-Table~\ref{table:pipeline-stats}.
-The variability between pair of images \tristan{images means MRI} in each condition was measured using the mean and standard deviation of absolute differences \tristan{then call them abs diff in the table}.
+We ensured that fMRI analyses were replicated successfully by comparing the result images of the group-level analysis.
+We visually checked the result images to be the same as the original study~\cite{bowring2019exploring}.
+We could replicate the original results with an exception for AFNI with slight differences which might be caused by the hardware variations,
+or the compilation instabilities such as out-of-order execution (dynamic scheduling) paradigm~\cite{duben2014use,demmel2013numerical}.
+In this paradigm, the processors might execute instructions out of the original order they appear based on
+the availability of input data and execution units to use resources efficiently. Therefore, it might
+compute floating-point operations in a different order, which often leads to different results.
+
+Summary statistics for the group-level (un)thresholded T-statistics are shown in Table~\ref{table:pipeline-stats}.
+The variability between results of each pair of tools in each condition was measured using the mean and standard deviation of absolute differences.
 Overall, the distribution of the pairwise variations in WT is an order of magnitude lower than BT in both means and standard deviations.
@@
 % Overally, we see that values in between tools are comparable to values in within tool results.
-\tristan{it's unclear what ``Fuzzy X and Y'' represent.}
-\note{Add statistics for subject level (first-level) analyses}
 
@@
 in some regions in the thresholded images.
-\note{For instance, some parts of the frontal lobe in the sagittal plane for almost all pairs and the occipital
+\ali{For instance, some parts of the frontal lobe in the sagittal plane for almost all pairs and the occipital
 lobe in the axial plane for the pairs of \fslspm and \fslafni in Figure~\ref{fig:thresh-maps}
@@
   across 16 subjects for each pair of tools.
-  Results show that subjects 15 and 10 were produced the least and the most variability, respectively, among all pairs, subjects,
+  Results show the subjects that were produced the least and the most variability among all pairs, subjects,
   and both BT and WT.
-  While subject 15 generated results with the mean of $\approx$ 0.093 and standard deviation of $\approx$ 0.174,
-  subject 10 produced results with the mean of $\approx$ 0.183 and standard deviation of $\approx$ 0.341.
+  While the subject with the least variability generated results with the mean of $\approx$ 0.093 and standard deviation of $\approx$ 0.174,
+  the subject with the most variability produced results with the mean of $\approx$ 0.183 and standard deviation of $\approx$ 0.341.
   This observation shows an order of magnitude of variability between subjects.
@@
   % and \afnispm subject 10 in BT and subject 5 in WT were the most variable subjects.
-  Moreover, Figure~\ref{fig:unthresh-firstlevel} shows the maps of standard deviations on MNI space in WT and BT for subjects 15 and 10.
-  We can see a significant variability between subjects.
+  % Moreover, Figure~\ref{fig:unthresh-firstlevel} shows the maps of standard deviations on MNI space in WT and BT for subjects 15 and 10.
+  % We can see a significant variability between subjects.
+
+  Moreover, Figure~\ref{fig:unthresh-maps-sbj} shows the maps of standard deviations on MNI space in WT and BT from T-statistics of
+  the subject with the highest WT variability.
+  The average standard deviations in WT and BT are $\approx$ 0.152 and $\approx$ 0.466, respectively.
+  The maps show regions in the brain where the magnitude of standard deviation exceeds 1.0 in WT in \fslafni and \afnispm,
+  such as the parts in the frontal and occipital lobes.
 
@@
 
-  %%%%%%%%%% Var. of Unthresh %%%%%%%%
+  % %%%%%%%%%% Var. of Unthresh %%%%%%%%
+  % \begin{figure*}[b]
+  %   \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  %     \centering
+  %     \includegraphics[width=\textwidth]{figures/sbj-level-bt-wt-unthresh-std.pdf}
+  %   \caption{Maps of standard deviation of unthresholded T-statistics from subject 15 in the rows A and B,
+  %   and subject 10 in the rows C and D.}
+  %   \label{fig:unthresh-firstlevel}
+  %   \end{minipage}}
+  % \end{figure*}
+
+  %%%%%%%%%% Var. of Unthresh sbj05%%%%%%%%
 \begin{figure*}[b]
   \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \begin{subfigure}[t]{\textwidth}
     \centering
-      \includegraphics[width=\textwidth]{figures/sbj-level-bt-wt-unthresh-std.pdf}
-    \caption{Maps of standard deviation of unthresholded T-statistics from subject 15 in the rows A and B,
-    and subject 10 in the rows C and D.}
-    \label{fig:unthresh-firstlevel}
+    \includegraphics[width=\textwidth]{figures/sbj05-bt-wt-unthresh-std.pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figures/sbj05-ratio-unthresh-std.pdf}
+    %\caption{Standard deviation of thresholded t-statistics map on template surface}
+  \end{subfigure}
+  \caption{Maps of standard deviation of unthresholded T-statistics in subject 5. The first and second rows show
+  maps on BT and WT results, respectively, and the third row represents maps of the ratio between them.}
+  \label{fig:unthresh-maps-sbj}
   \end{minipage}}

### 2021-10-08 paper/paper.tex
Update method section

@@
 
-To simulate uncertainty close to the level of machine error,
-the maximum relative error due to rounding in floating-point arithmetic,
-we used the method introduced in~\cite{salari2021accurate}
-called Fuzzy libmath (FL). FL uses MCA to
-% create an instrumented version of the functions embedded in the mathematical library in GNU operating systems (libmath) in which
-introduce a controlled amount of noise in the floating-point operations embedded
-in the mathematical library in GNU operating systems (libmath)
-through the following perturbation model:
+For our analyses, we used the Fuzzy libmath (FL) library introduced in~\cite{salari2021accurate}, an MCA-instrumented 
+version of the mathematical library in GNU operating systems (libmath).
+Using FL, we can simulate numerical variability at the level of machine error, the floating-point rounding error
+caused by floating-point representation limits defined by the hardware.
+
+FL works based on the MCA, a floating-point arithmetic that simulates roundoff and catastrophic cancellation errors
+by introducing a controlled amount of noise in the floating-point operations 
+through the following perturbation model~\cite{Parker1997-qq}:
+
 \begin{equation} \label{eq:mca_inexact}
@@
 \end{equation}
+
 where $e_x$ is the exponent in the floating-point representation of $x$,
@@
 and $\xi$ is a random uniform variable of $(-\frac{1}{2}, \frac{1}{2})$.
-The perturbation is applied in a given number of least-significant bits,
-which models floating-point rounding and catastrophic cancellation errors.
-This is automated using Verificarlo tool~\cite{denis2015verificarlo} that implements MCA at compilation time.
+The MCA perturbations are automated using Verificarlo tool~\cite{denis2015verificarlo} at compilation time.
 
@@
 FSL and AFNI scripts were executed in Python 2.7. We also used a fixed number of 7 threads in AFNI executions
-to produce the similar results to the original study in a feasible execution time.
-We also executed SPM with Octave instead of Matlab to enable GNU mathematical library instrumentations
-since Matlab uses its built-in mathematical functions.
+to reproduce similar results to the original study in a feasible execution time.
 All the analyses were conducted on the same operating system, CentOS 7.3.
@@
 We evaluated WT and BT variabilities in thresholded and unthresholded group-level activation maps.
-We computed voxel-wise standard deviations
-\tristan{did you check standard error vs standard deviation?}\ali{STD shows variability of data in relation to the mean (what we are looking for here),
-while SE is a type of STD (computed as $\frac{\sigma}{\sqrt{n}}$) for distribution of means (we use it when we are interested in the precision of means in different samples).} of T-statistic values for each pair of tools
+We computed voxel-wise standard deviations of T-statistic values for each pair of tools
 and then compared the distribution of standard deviations in both conditions.
@@
 in Human Connectome Project Multi-Modal Parcellation version 1.0 (HCP-MMP1.0)~\cite{glasser2016multi}.
-We computed the WT Dice values as the average pair-wise Dices computed among three Fuzzy samples for each pair of tools.
+Dice values in WT are computed as the average pair-wise Dices among three Fuzzy samples for each pair of tools.
 Also, we compared the correlation of Dice scores normalized by the region sizes in both conditions.
-% This measured the overlap of acitaved voxels which assess the spatial similarity between activated maps.
+
+\tristan{did you check standard error vs standard deviation?}\ali{STD shows variability of data in relation to the mean (what we are looking for here),
+while SE is a type of STD (computed as $\frac{\sigma}{\sqrt{n}}$) for distribution of means (we use it when we are interested in the precision of means in different samples).}
 
@@
 Summary statistics for the group-level (un)thresholded T-statistics are shown in Table~\ref{table:pipeline-stats}.
-The variability between results of each pair of tools in each condition was measured using the mean and standard deviation of absolute differences.
+The variability between results of each pair of tools in BT and indivisual tool in WT was measured using the mean and standard deviation of absolute differences.
 Overall, the distribution of the pairwise variations in WT is an order of magnitude lower than BT in both means and standard deviations.
 While the highest variability was observed for \fslafni, \fslspm made the least variations for all conditions.
-% Overally, we see that values in between tools are comparable to values in within tool results.
+Results show that AFNI generated the most variability in WT out of three tools.
 
@@
         {} & AFNI vs. SPM         &  0.079       & 1.475      & 0.254     & 0.608  \\
-        {WT} & FSL and SPM    &  0.005       & 0.358      & 0.030     & 0.099  \\
-        {} & FSL and AFNI   &  0.011       & 0.475      & 0.038     & 0.155  \\
-        {} & AFNI and SPM   &  0.011       & 0.458      & 0.033     & 0.144  \\
+        {WT} & FSL    &  0.005       & 0.354      & 0.034     & 0.082  \\
+        {}   & SPM    &  0.006       & 0.252      & 0.025     & 0.054  \\
+        {}   & AFNI   &  0.017       & 0.434      & 0.041     & 0.128  \\
         \bottomrule
@@
 on MNI space are shown in Figure~\ref{fig:thresh-maps}.
-
 While we observe substantial variations in BT with the average standard deviation $\approx$ 1.5,
@@
 
-  Table~\ref{table:firstlevel-stats} shows a summary of the statistics from the subject-level analysis results.
-  This table represents the average of the mean and standard deviation of absolute differences of unthresholded T-statistics
-  across 16 subjects for each pair of tools.
-  Results show the subjects that were produced the least and the most variability among all pairs, subjects,
-  and both BT and WT.
-  While the subject with the least variability generated results with the mean of $\approx$ 0.093 and standard deviation of $\approx$ 0.174,
-  the subject with the most variability produced results with the mean of $\approx$ 0.183 and standard deviation of $\approx$ 0.341.
-  This observation shows an order of magnitude of variability between subjects.
+  % Table~\ref{table:firstlevel-stats} shows a summary of the statistics from the subject-level analysis results.
+  % This table represents the average of the mean and standard deviation of absolute differences of unthresholded T-statistics
+  % across 16 subjects for each pair of tools.
+  % Results show the subjects that were produced the least and the most variability among all pairs, subjects,
+  % and both BT and WT.
+  % While the subject with the least variability generated results with the mean of $\approx$ 0.093 and standard deviation of $\approx$ 0.174,
+  % the subject with the most variability produced results with the mean of $\approx$ 0.183 and standard deviation of $\approx$ 0.341.
+  % This observation shows an order of magnitude of variability between subjects.
+
   % The most variability for \fslspm appeared in subject 1 in BT and subject 11 in WT, and for \fslafni
@@
 
-  Moreover, Figure~\ref{fig:unthresh-maps-sbj} shows the maps of standard deviations on MNI space in WT and BT from T-statistics of
+  Figure~\ref{fig:unthresh-maps-sbj} shows the maps of standard deviations on MNI space in WT and BT from T-statistics of
   the subject with the highest WT variability.
@@
   such as the parts in the frontal and occipital lobes.
-
-%%%%%%%%%% Summary of statstics %%%%%%%%
-\setlength{\tabcolsep}{5pt}
-\begin{table*}[h]
-    \centering
-    \begin{tabular}{cccc|cc|cc}
-        \toprule
-        \multirow{2}{*}{} &{} & \multicolumn{2}{c}{All Subjects} & \multicolumn{2}{c}{Least variable} & \multicolumn{2}{c}{Most variable} \\
-        \cmidrule{3-4} \cmidrule{5-6} \cmidrule{7-8} \\
-        {} & {} & Mean  & Std. dev.  & Mean & Std. dev. & Mean  & Std. dev. \\
-        \midrule
-        \rowcolor{lightgray}
-        {BT} & FSL vs. SPM           & 0.245     & 0.366       & 0.166     & 0.255    & 0.273    & 0.405  \\
-        \rowcolor{lightgray}
-        {}   & FSL vs. AFNI          & 0.295     & 0.439      & 0.183     & 0.282     & 0.392    & 0.582  \\
-        \rowcolor{lightgray}
-        {}   & AFNI vs. SPM          & 0.238     & 0.491      & 0.150     & 0.314     & 0.310    & 0.642  \\
-        {WT} & FSL and SPM    & 0.033     & 0.092      & 0.018     & 0.050     & 0.036    & 0.099  \\
-        {}   & FSL and AFNI   & 0.040     & 0.136      & 0.021     & 0.075     & 0.048    & 0.165  \\
-        {}   & AFNI and SPM   & 0.033     & 0.124      & 0.019     & 0.071     & 0.039    & 0.155  \\
-        \bottomrule
-    \end{tabular}
-    \caption{Summary of voxel-wise mean and standard deviation of absolute differences for each pair of tools
-    in subject-level T-statistics.}
-    \label{table:firstlevel-stats}
-\end{table*}
-
-  % %%%%%%%%%% Var. of Unthresh %%%%%%%%
-  % \begin{figure*}[b]
-  %   \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-  %     \centering
-  %     \includegraphics[width=\textwidth]{figures/sbj-level-bt-wt-unthresh-std.pdf}
-  %   \caption{Maps of standard deviation of unthresholded T-statistics from subject 15 in the rows A and B,
-  %   and subject 10 in the rows C and D.}
-  %   \label{fig:unthresh-firstlevel}
-  %   \end{minipage}}
-  % \end{figure*}
 
@@
 \end{figure*}
+
+\subsection{Global nearest precision}
+
+\ali{Add results at global nearest precision.}
 

### 2021-10-11 paper/paper.tex
Update result section

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+\makeatletter
+  \def\footnoterule{\kern-3\p@
+  \hrule \@width 2in \kern 2.6\p@} % the \hrule is .4pt high
+\makeatother
 
@@
 
-We ensured that fMRI analyses were replicated successfully by comparing the result images of the group-level analysis.
-We visually checked the result images to be the same as the original study~\cite{bowring2019exploring}.
-We could replicate the original results with an exception for AFNI with slight differences which might be caused by the hardware variations,
-or the compilation instabilities such as out-of-order execution (dynamic scheduling) paradigm~\cite{duben2014use,demmel2013numerical}.
+We ensured that fMRI analyses were replicated successfully compared to the original results in~\cite{bowring2019exploring}
+by visually checking the overlap of T-statistic images resulted from the group-level analysis.
+We could replicate the analyses across tools with an exception for AFNI that produced results with slight differences; 
+this might be caused by the compiler variations, or different hardware and their optimizations
+such as out-of-order execution (dynamic scheduling) paradigm~\cite{duben2014use,demmel2013numerical}.
 In this paradigm, the processors might execute instructions out of the original order they appear based on
@@
 
-Summary statistics for the group-level (un)thresholded T-statistics are shown in Table~\ref{table:pipeline-stats}.
-The variability between results of each pair of tools in BT and indivisual tool in WT was measured using the mean and standard deviation of absolute differences.
-Overall, the distribution of the pairwise variations in WT is an order of magnitude lower than BT in both means and standard deviations.
-While the highest variability was observed for \fslafni, \fslspm made the least variations for all conditions.
-Results show that AFNI generated the most variability in WT out of three tools.
+Summary statistics for the group-level (un)thresholded T-statistics are reported in Table~\ref{table:pipeline-stats}.
+The variability between results of each pair of tools in BT and individual tools in WT was measured using the mean and standard deviation of absolute differences.
+Overall, the distribution of variations in WT was an order of magnitude lower than BT in both means and standard deviations.
+While the highest variability was observed in \fslafni, \fslspm was made the least variations in BT.
+Results also show that AFNI was generated the most variability in WT among the three tools.
 
@@
     \end{tabular}
-    \caption{Summary of voxel-wise mean and standard deviation of absolute differences for each pair of tools
-    in group-level T-statistics.}
+    \caption{Summary of voxel-wise mean and standard deviation of absolute differences in group-level T-statistics in BT and WT.}
     \label{table:pipeline-stats}
@@
 on MNI space are shown in Figure~\ref{fig:thresh-maps}.
-While we observe substantial variations in BT with the average standard deviation $\approx$ 1.5,
-the order of magnitude of variations in WT is much lower with the average standard deviation $\approx$ 0.5,
-as was anticipated. However, numerical variability is still significant in WT results.
+While we observed substantial variations in BT with the average standard deviation $\approx$ 1.5,
+the magnitude of variations in WT was much lower with the average standard deviation $\approx$ 0.5,
+as was anticipated. However, numerical variability was still significant in WT results.
 %Moreover, the numerical perturbations produces variations in similar order og magnitude in WT compared to BT variations
-Moreover, we see the similar order of magnitude in WT variations compared to BT variations
+Moreover, we obtained a similar order of magnitude in WT variations compared to BT variations
 in some regions in the thresholded images.
-\ali{For instance, some parts of the frontal lobe in the sagittal plane for almost all pairs and the occipital
+For instance, some parts of the frontal lobe in the sagittal plane for all pairs and the occipital
 lobe in the axial plane for the pairs of \fslspm and \fslafni in Figure~\ref{fig:thresh-maps}
-are closely replicated using the numerical perturbations.}
+were closely replicated by the numerical perturbations.
 
 % Fig2
-In Figure~\ref{fig:dice-thresh}, we compare region-by-region Dice coefficients of
+In Figure~\ref{fig:dice-thresh}, we compared region-by-region Dice coefficients of
 the group-level thresholded maps for all pairs of software packages in BT and WT.
 This shows a linear correlation between Dice values in BT and WT,
-which implies that the variability of activated voxels in both conditions is similar.
+which implies that the variability of activated voxels in both conditions was similar.
 Also, small P-values across all three pairs, including \num{1e-10} for \fslafni, \num{6e-04} for \fslspm,
-and \num{2e-05} for \afnispm, confirms this correlation of similarities.
-The vertical line where the Dice score is zero in BT shows regions in the brain with no overlaps between activated voxels in BT but WT,
-including left/right `V1\_ROI' in \fslafni and \fslspm, and left/right `TGd\_ROI' in \afnispm results.
+and \num{2e-05} for \afnispm, confirmed this correlation of similarities.
+The vertical line where the Dice score is zero in BT demonstrates regions in the brain with no overlaps between activated voxels in BT but WT,
+including left/right `V1\_ROI'\footnote{The primary visual cortex} in \fslafni and \fslspm,
+and left/right `TGd\_ROI'\footnote{The area TG dorsal (part of lateral temporal cortex)} in \afnispm results.
 
@@
     \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-    \begin{subfigure}[t]{\textwidth}
       \centering
-      \includegraphics[width=\textwidth]{figures/bt-wt-thresh-std.pdf}
+      \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{figures/ratio-thresh-std.pdf}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \end{subfigure}
     \caption{Maps of standard deviation of thresholded T-statistics. The first and second rows show
-    maps on BT and WT results, respectively, and the third row represents maps of the ratio between them.}
+    maps on BT and WT results, respectively, and the third row represents maps of their differences.}
     % so that bright blue areas indicate more similar order of magnitude of variations in both conditions,
@@
   %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
-  \begin{figure}[b]
+  \begin{figure}[ht]
     \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
@@
 Figure~\ref{fig:unthresh-maps} shows the brain maps of standard deviations for group-level unthresholded T-statistics in WT and BT.
-Results show a different magnitude of
-the order of variations in WT and BT with standard deviation ranges from $\approx$ 0.12 to $\approx$ 0.5 on average, respectively.
-The maps show regions in the brain where the magnitude of standard deviation is close to zero in WT but it exceeds 2.0 in BT,
-such as the limbic and frontal lobes in the sagittal plane.
-However, there are voxels with a significant correlation between WT and BT that are uniformly distributed across the brain maps.
+Results show a different order of magnitude of variations in WT and BT with standard deviation
+of $\approx$ 0.12 and $\approx$ 0.5 on average, respectively.
+We observed regions in the brain where the magnitude of standard deviation was close to zero in WT, but it exceeded 2.0 in BT,
+such as some parts of the limbic and frontal lobes in the sagittal plane.
+However, the brain maps included voxels with approximately zero differences of standard deviations in WT and BT, which are uniformly distributed.
 
 %%%%%%%%%% Var. of Unthresh %%%%%%%%
-\begin{figure*}[b]
+\begin{figure*}[ht]
     \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-    \begin{subfigure}[t]{\textwidth}
       \centering
-      \includegraphics[width=\textwidth]{figures/bt-wt-unthresh-std.pdf}
+      \includegraphics[width=\textwidth]{figures/std/gl-unthresh.png}
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[t]{\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{figures/ratio-unthresh-std.pdf}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \end{subfigure}
     \caption{Maps of standard deviation of unthresholded T-statistics. The first and second rows show
-    maps on BT and WT results, respectively, and the third row represents maps of the ratio between them.}
+    maps on BT and WT results, respectively, and the third row represents maps of their differences.}
     \label{fig:unthresh-maps}
@@
 We found two major clusters, including the identity cluster that corresponds to the correlations
-between BT and WT with the ratio of $0.5 < BT/WT < 2$ where the standard deviations are bigger than 0.1,
+between BT and WT with the ratio of $0.5 < BT/WT < 2$ where the standard deviations were bigger than 0.1,
 and the upper cluster that shows voxels where BT $\approx$ 0.
-The percentage of voxels included in the identity cluster is \%9.9 in \fslspm, \%17.3 in \fslafni, and \%13.8 in \afnispm,
-and in the upper cluster is $\approx$ \%1 for each pair of tools.
+The percentage of voxels included in the identity cluster was \%9.9 in \fslspm, \%17.3 in \fslafni, and \%13.8 in \afnispm,
+and in the upper cluster was $\approx$ \%1 for each pair of tools.
 The identity area is also represented on the MNI space in the second row in Figure~\ref{fig:unthresh-correlation}.
-This figure shows the spatial localization of the parts of the brain that BT variability is correlated with the numerical variability.
+This figure shows the spatial localization of the parts of the brain that BT variability was correlated with the numerical variability.
 This refines the presented results in Figure~\ref{fig:unthresh-maps},
-which indicates how correlation is uniformly distributed across the brain.
+which indicated how the correlation is uniformly distributed across the brain.
 
   %%%%%%%%%% Corr. plot of tstats%%%%%%%%
-  \begin{figure*}[b]
+  \begin{figure*}[ht]
     \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-      \begin{subfigure}[t]{\textwidth}
+      \begin{subfigure}[ht]{\textwidth}
         \centering
@@
       \hfill
-      \begin{subfigure}[t]{\textwidth}
+      \begin{subfigure}[ht]{\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{figures/corr-unthresh-std.pdf}
+        \includegraphics[width=\textwidth]{figures/std/correlated-unthresh.png}
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
@@
 
-  % The most variability for \fslspm appeared in subject 1 in BT and subject 11 in WT, and for \fslafni
-  % and \afnispm subject 10 in BT and subject 5 in WT were the most variable subjects.
-  % Moreover, Figure~\ref{fig:unthresh-firstlevel} shows the maps of standard deviations on MNI space in WT and BT for subjects 15 and 10.
-  % We can see a significant variability between subjects.
-
-  Figure~\ref{fig:unthresh-maps-sbj} shows the maps of standard deviations on MNI space in WT and BT from T-statistics of
-  the subject with the highest WT variability.
-  The average standard deviations in WT and BT are $\approx$ 0.152 and $\approx$ 0.466, respectively.
-  The maps show regions in the brain where the magnitude of standard deviation exceeds 1.0 in WT in \fslafni and \afnispm,
-  such as the parts in the frontal and occipital lobes.
+  In addition to the group-level analysis, we evaluated WT and BT variabilities between subjects individually.
+  Figure~\ref{fig:unthresh-maps-sbj} shows the brain maps of standard deviations in WT and BT from unthresholded T-statistics of
+  the subject with the highest WT variability among all 16 subjects.
+  The average standard deviation for this subject in WT and BT was $\approx$ 0.152 and $\approx$ 0.466, respectively.
+  The maps show regions in the brain where the magnitude of standard deviation exceeded 1.0 in WT in \fslafni and \afnispm,
+  such as areas in the frontal and occipital lobes.
+  This is similar to BT variability, even with higher variations in some voxels.
 
   %%%%%%%%%% Var. of Unthresh sbj05%%%%%%%%
-\begin{figure*}[b]
+\begin{figure*}[ht]
   \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-  \begin{subfigure}[t]{\textwidth}
     \centering
-    \includegraphics[width=\textwidth]{figures/sbj05-bt-wt-unthresh-std.pdf}
+    \includegraphics[width=\textwidth]{figures/std/sbj05-std.png}
     %\caption{Standard deviation of thresholded t-statistics map on template surface}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[t]{\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{figures/sbj05-ratio-unthresh-std.pdf}
-    %\caption{Standard deviation of thresholded t-statistics map on template surface}
-  \end{subfigure}
   \caption{Maps of standard deviation of unthresholded T-statistics in subject 5. The first and second rows show
-  maps on BT and WT results, respectively, and the third row represents maps of the ratio between them.}
+  maps on BT and WT results, respectively, and the third row represents maps of their differences.}
   \label{fig:unthresh-maps-sbj}
@@
 
-\subsection{Global nearest precision}
+\subsection{WT variability across virtual precisions}
 
-\ali{Add results at global nearest precision.}
+We evaluated WT variability across different virtual precisions for FSL tool.
+We changed the virtual precision in steps of 2 between t=1 and t=53 bits.
+Figure~\ref{fig:across-precisions} represents RMSE between standard deviations of each pair of tools in BT and FSL variations across virtual precisions in WT.
+%Consistant with the previous results, 
+RMSE between WT and BT for \fslafni was the highest, and \fslspm was the lowest in all virtual precisions.
+This also shows the similar plateaus were generated in all three pairs of tools.
+Moreover, the analyses crashed for the precisions below t=11 bits during the FSL preprocessing steps. 
+This needs further investigations to understand the exact failure reasons.
 
-\section{Conclusion \& Discussion}
+We determined the virtual precision of t=27 bits as the precision that minimized the RMSE between standard deviations in BT on average and WT.
+This is the precision that numerical perturbations in FSL more closely simulated BT variability.
+Figure~\ref{fig:gnp-mni} shows the brain maps of numerical variability obtained from the analysis with FSL at t=27 bits.
+This represents regions with significant variability in the frontal, parietal, and limbic lobes.
+
+  %%%%%%%%%% plot different precisions%%%%%%%%
+  \begin{figure}[ht]
+    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
+        \centering
+        \includegraphics[width=\columnwidth]{figures/rmse-precisions.png}
+        %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \caption{Comparison of RMSE values computed between BT and WT resulted from FSL tool for different virtual precisions.}
+    \label{fig:across-precisions}
+    \end{minipage}}
+  \end{figure}
+
+  %%%%%%%%%% plot different precisions%%%%%%%%
+  \begin{figure}[ht]
+    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
+        \centering
+        \includegraphics[width=\columnwidth]{figures/bt-wt.png}
+        %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \caption{Comparison of standard deviations in BT averaged across pairs of tools and WT resulted from FSL tool
+      at the virtual precision of t=27 bits.}
+    \label{fig:gnp-mni}
+    \end{minipage}}
+  \end{figure}
+
+\section{Discussion}
+
+\begin{itemize}
+
+  \item[$\bullet$ ] In this study, we represented the magnitude of differences in BT and WT results.
+  We obtained more instability in BT compared to WT. Also we showed how between tool variations
+  are correlated with numerical variability.
+  While we only perturbed basic mathematical functions, perturbing linear algebra, in particular, could increase WT variability.
+
+  \item[$\bullet$ ] Generally, we obtained more uncertainty on thresholded results, probably due to different thresholding
+  methods used in different tools. This can raise further investigations on the thresholding techniques toward stability.
+  Also, we obtained significant instabilities in specific subjects so that healed by averaging in group-level analyses.
+
+  \item[$\bullet$ ] We showed that reducing the number of virtual precision bits leads to more instabnilities in which can exceeds variability compared to BT.
+  We also showed the numerical perturbations can perfectly simulate BT variability in some regions.
+
+\end{itemize}
 
@@
 
+\section{Conclusion}
+
 \begin{itemize}
-    \item[$\bullet$ ] In this study, we represented the magnitude of differences in between tool and within tool results.
-    We obtained more instability in BT compared to WT. Also we showed how between tool variations
-    are correlated with numerical variability.
-
-    \item[$\bullet$ ] Generally, we obtained more uncertainty on thresholded results, probably due to different thresholding
-    methods used in different tools. This can raise further investigations on the thresholding techniques toward stability.
 

### 2021-10-12 paper/paper.tex
Comments on results

@@
 \section{Results}
-All scripts and results to create the figures in this section are available at \url{https://github.com/ali4006/fuzzy-neurotools}.
-The computations were performed on \href{https://www.computecanada.ca}{the Compute Canada's} Béluga cluster
-with 872 available nodes containing 2× Intel Gold 6148 Skylake @ 2.4 GHz (40 cores/node) CPU and node memory ranging from 92 to 752 GB.
+All scripts and data to create the figures presented in this section are available at \url{https://github.com/ali4006/fuzzy-neurotools} \tristan{move to lab org}.
+The computations were performed on \href{https://www.computecanada.ca}{Compute Canada's} Béluga cluster
+with 872 nodes, each with 2× Intel Gold 6148 Skylake @ 2.4 GHz (40 cores/node) CPU and node memory ranging from 92 to 752 GB.
 
-We ensured that fMRI analyses were replicated successfully compared to the original results in~\cite{bowring2019exploring}
-by visually checking the overlap of T-statistic images resulted from the group-level analysis.
-We could replicate the analyses across tools with an exception for AFNI that produced results with slight differences; 
-this might be caused by the compiler variations, or different hardware and their optimizations
+We ensured a successful replication of the analyses initally presented in~\cite{bowring2019exploring}
+by visually checking the overlap \tristan{what do you mean ``visually checking the overlap?'' Afair we had looked at the difference images?} of T-statistic group maps.
+We could replicate the analyses across tools with an exception for AFNI that produced results with slight differences \tristan{this needs discussion on how to present it}. 
+This might be caused by the compiler variations, or different hardware and their optimizations
 such as out-of-order execution (dynamic scheduling) paradigm~\cite{duben2014use,demmel2013numerical}.
@@
 the availability of input data and execution units to use resources efficiently. Therefore, it might
-compute floating-point operations in a different order, which often leads to different results.
+compute floating-point operations in a different order, which often leads to different results \tristan{is this a compiler optimization?
+If so, just mention ``compiler optimizations such as dynamic scheduling'', no need to enter into details}.
 
-Summary statistics for the group-level (un)thresholded T-statistics are reported in Table~\ref{table:pipeline-stats}.
-The variability between results of each pair of tools in BT and individual tools in WT was measured using the mean and standard deviation of absolute differences.
-Overall, the distribution of variations in WT was an order of magnitude lower than BT in both means and standard deviations.
+Summary statistics for the group-level unthresholded and thresholded T-statistics \tristan{harmonize capitalization in ``T-statstics / t-statistics'' (t should be lower case unless it's the first word in the sentence)} are reported in Table~\ref{table:pipeline-stats}.
+% The variability between results of each pair of tools in BT and individual tools in WT was measured using the mean and standard deviation of absolute differences.
+Overall, WT variability was an order of magnitude lower than BT variability for both means and standard deviations.
 While the highest variability was observed in \fslafni, \fslspm was made the least variations in BT.
-Results also show that AFNI was generated the most variability in WT among the three tools.
+Results also show that AFNI was generated the most variability in WT among the three tools \tristan{this needs statistical testing}.
 
@@
         \rowcolor{lightgray}
-        {BT} & FSL vs. SPM        &  0.043       & 1.282      & 0.242     & 0.443  \\
+        {Between Tools} & FSL vs. SPM        &  0.043       & 1.282      & 0.242     & 0.443  \\
         \rowcolor{lightgray}
-        {} & FSL vs. AFNI         &  0.099       & 1.548      & 0.302     & 0.547  \\
+        {(BT)} & FSL vs. AFNI         &  0.099       & 1.548      & 0.302     & 0.547  \\
         \rowcolor{lightgray}
         {} & AFNI vs. SPM         &  0.079       & 1.475      & 0.254     & 0.608  \\
-        {WT} & FSL    &  0.005       & 0.354      & 0.034     & 0.082  \\
-        {}   & SPM    &  0.006       & 0.252      & 0.025     & 0.054  \\
+        {Within Tool} & FSL    &  0.005       & 0.354      & 0.034     & 0.082  \\
+        {(WT)}   & SPM    &  0.006       & 0.252      & 0.025     & 0.054  \\
         {}   & AFNI   &  0.017       & 0.434      & 0.041     & 0.128  \\
@@
     \end{tabular}
-    \caption{Summary of voxel-wise mean and standard deviation of absolute differences in group-level T-statistics in BT and WT.}
+    \caption{Summary of voxel-wise mean and standard deviation of absolute differences in group-level T-statistics in BT and WT. \tristan{discuss this caption}}
     \label{table:pipeline-stats}
@@
 %Fig 1
-Comparisons of standard deviations between thresholded images in WT and BT
+Comparisons of standard deviations between thresholded images \tristan{Table II should show summary statistics from the maps, is it the case?} in WT and BT
 on MNI space are shown in Figure~\ref{fig:thresh-maps}.
-While we observed substantial variations in BT with the average standard deviation $\approx$ 1.5,
-the magnitude of variations in WT was much lower with the average standard deviation $\approx$ 0.5,
-as was anticipated. However, numerical variability was still significant in WT results.
+While we observed substantial BT variations with the average standard deviation $\approx$ 1.5 \tristan{why approx? },
+the magnitude of WT variations was much lower with the average standard deviation $\approx$ 0.5,
+as was anticipated. However, numerical variability was still significant in WT results \tristan{this doesn't mean much. Also, ``significant'' means ``statistically significant''.}.
 %Moreover, the numerical perturbations produces variations in similar order og magnitude in WT compared to BT variations
-Moreover, we obtained a similar order of magnitude in WT variations compared to BT variations
-in some regions in the thresholded images.
-For instance, some parts of the frontal lobe in the sagittal plane for all pairs and the occipital
-lobe in the axial plane for the pairs of \fslspm and \fslafni in Figure~\ref{fig:thresh-maps}
-were closely replicated by the numerical perturbations.
+Moreover, the magnitude of WT variations reached the magnitued of BT variations
+in some regions, shown in white in Figure~\ref{fig:thresh-maps}-\textbf{C}.
 
 % Fig2
-In Figure~\ref{fig:dice-thresh}, we compared region-by-region Dice coefficients of
-the group-level thresholded maps for all pairs of software packages in BT and WT.
-This shows a linear correlation between Dice values in BT and WT,
-which implies that the variability of activated voxels in both conditions was similar.
+Figure~\ref{fig:dice-thresh} compares regional normalized Dice coefficients of
+activated voxels, showing a linear correlation between BT and WT \tristan{report p-value}. 
 Also, small P-values across all three pairs, including \num{1e-10} for \fslafni, \num{6e-04} for \fslspm,
-and \num{2e-05} for \afnispm, confirmed this correlation of similarities.
-The vertical line where the Dice score is zero in BT demonstrates regions in the brain with no overlaps between activated voxels in BT but WT,
-including left/right `V1\_ROI'\footnote{The primary visual cortex} in \fslafni and \fslspm,
-and left/right `TGd\_ROI'\footnote{The area TG dorsal (part of lateral temporal cortex)} in \afnispm results.
+and \num{2e-05} for \afnispm, confirmed this correlation of similarities \tristan{are these the p values of the regressions?}.
+% The vertical line where the Dice score is zero in BT demonstrates regions in the brain with no overlaps between activated voxels in BT but WT,
+% including left/right `V1\_ROI'\footnote{The primary visual cortex} in \fslafni and \fslspm,
+% and left/right `TGd\_ROI'\footnote{The area TG dorsal (part of lateral temporal cortex)} in \afnispm results.
 
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \caption{Maps of standard deviation of thresholded T-statistics. The first and second rows show
-    maps on BT and WT results, respectively, and the third row represents maps of their differences.}
+    \caption{Thresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}). }
     % so that bright blue areas indicate more similar order of magnitude of variations in both conditions,
@@
     \includegraphics[width=\columnwidth]{figures/dices_corr.png}
-    \caption{Correlation of Dice coefficients of activated regions in BT and WT
-    from the thresholded T-statistics. Different pairs are illustrated in different colors.
-    Regions correspond to the 360 areas of cortical parcellation (HCP-MMP1.0)~\cite{glasser2016multi}.}
+    \caption{Normalized, regional Dice coefficients of activated voxels for
+    BT and WT using the HCP-MMP1.0 parcellation of
+    ~\cite{glasser2016multi}.}
     \label{fig:dice-thresh}
@@
 % Fig3
-Figure~\ref{fig:unthresh-maps} shows the brain maps of standard deviations for group-level unthresholded T-statistics in WT and BT.
-Results show a different order of magnitude of variations in WT and BT with standard deviation
-of $\approx$ 0.12 and $\approx$ 0.5 on average, respectively.
-We observed regions in the brain where the magnitude of standard deviation was close to zero in WT, but it exceeded 2.0 in BT,
-such as some parts of the limbic and frontal lobes in the sagittal plane.
-However, the brain maps included voxels with approximately zero differences of standard deviations in WT and BT, which are uniformly distributed.
+Similar conclusions are drawn from the unthresholded t-statistcs maps
+(Figure~\ref{fig:unthresh-maps}). BT variability is an order of magnitude
+higher than WT variability overall, however, BT and WT variability are
+comparable in some regions.
+
+% shows the brain maps of standard deviations for group-level unthresholded
+% T-statistics in WT and BT. Results show a different order of magnitude of
+% variations in WT and BT with standard deviation of $\approx$ 0.12 and
+% $\approx$ 0.5 on average, respectively. We observed regions in the brain
+% where the magnitude of standard deviation was close to zero in WT, but it
+% exceeded 2.0 in BT, such as some parts of the limbic and frontal lobes in
+% the sagittal plane. However, the brain maps included voxels with
+% approximately zero differences of standard deviations in WT and BT, which
+% are uniformly distributed.
 
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \caption{Maps of standard deviation of unthresholded T-statistics. The first and second rows show
-    maps on BT and WT results, respectively, and the third row represents maps of their differences.}
+    \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).}
     \label{fig:unthresh-maps}
@@
 % Fig4
+\tristan{rewrite this paragraph}
 The scatter plot in Figure~\ref{fig:unthresh-correlation} represents the correlation of standard deviation in WT and BT variability.
@@
       for two clusters, including the upper cluster (purple color) and the correlated cluster (green color).
-      The second row maps the correlated area on the MNI space.}
+      The second row maps the correlated area on the MNI space. \tristan{Fix colors and captions (to be discussed)}}
     \label{fig:unthresh-correlation}
@@
 
-  In addition to the group-level analysis, we evaluated WT and BT variabilities between subjects individually.
-  Figure~\ref{fig:unthresh-maps-sbj} shows the brain maps of standard deviations in WT and BT from unthresholded T-statistics of
-  the subject with the highest WT variability among all 16 subjects.
-  The average standard deviation for this subject in WT and BT was $\approx$ 0.152 and $\approx$ 0.466, respectively.
-  The maps show regions in the brain where the magnitude of standard deviation exceeded 1.0 in WT in \fslafni and \afnispm,
-  such as areas in the frontal and occipital lobes.
-  This is similar to BT variability, even with higher variations in some voxels.
+  Figure~\ref{fig:unthresh-maps-sbj} shows BT and WT variability of the
+  unthresholded t-statistics for the subject with the highest WT
+  variability among the 16 subjects. The average standard deviation for
+  this subject was $\approx$ 0.152 for WT and $\approx$ 0.466 for BT
+  \tristan{remove $\approx$, discuss what these numbers represent}.
+  As can be seen in the Figure, WT variability approaches and even surpasses BT variability in some regions.
 
@@
 
-We evaluated WT variability across different virtual precisions for FSL tool.
-We changed the virtual precision in steps of 2 between t=1 and t=53 bits.
-Figure~\ref{fig:across-precisions} represents RMSE between standard deviations of each pair of tools in BT and FSL variations across virtual precisions in WT.
+While the previous results were obtained at the virtual precision of 53~bits for double-precision floating-point values
+and 24~bits for single-precision values, we evaluated WT variability across different virtual precisions for FSL. \tristan{make sure this is described in the methods}
+Figure~\ref{fig:across-precisions} represents the RMSE between standard deviations of each pair of tools in BT and FSL variations across virtual precisions in WT \tristan{clarify what is shown}.
 %Consistant with the previous results, 
@@
 
-We determined the virtual precision of t=27 bits as the precision that minimized the RMSE between standard deviations in BT on average and WT.
+\tristan{make a full figure, similar to Fig 1, 3, and 5. }We determined the virtual precision of t=27 bits as the precision that minimized the RMSE between standard deviations in BT on average and WT.
 This is the precision that numerical perturbations in FSL more closely simulated BT variability.
@@
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \caption{Comparison of RMSE values computed between BT and WT resulted from FSL tool for different virtual precisions.}
+      \caption{Comparison of RMSE values computed between BT and WT resulted from FSL tool for different virtual precisions \tristan{Make a full figure, similar to Fig 5, 3, and 1.}.}
     \label{fig:across-precisions}
@@
 
+  \item[$\bullet$] Numerical instability in individual analyses is attenuated in group analyses. This is an issue for the development of fMRI biomarkers.
+  \item[$\bullet$] Comparision between FSL, SPM and AFNI. Discussion on the instrumentation of math functions only.
 \end{itemize}

### 2021-10-12 paper/paper.tex
Comments in results

@@
 
-\subsection{Fuzzy libmath environment}
-
-For our analyses, we used the Fuzzy libmath (FL) library introduced in~\cite{salari2021accurate}, an MCA-instrumented 
-version of the mathematical library in GNU operating systems (libmath).
-Using FL, we can simulate numerical variability at the level of machine error, the floating-point rounding error
-caused by floating-point representation limits defined by the hardware.
-
-FL works based on the MCA, a floating-point arithmetic that simulates roundoff and catastrophic cancellation errors
-by introducing a controlled amount of noise in the floating-point operations 
-through the following perturbation model~\cite{Parker1997-qq}:
-
-\begin{equation} \label{eq:mca_inexact}
-  inexact(x) = x + 2^{e_x-t}\xi
-\end{equation}
-
-where $e_x$ is the exponent in the floating-point representation of $x$,
-$t$ is the virtual precision, the number of bits in mantissa that will not be perturbed,
-and $\xi$ is a random uniform variable of $(-\frac{1}{2}, \frac{1}{2})$.
-The MCA perturbations are automated using Verificarlo tool~\cite{denis2015verificarlo} at compilation time.
-
-The instrumented functions are loaded in the pipeline using LD\_PRELOAD, a Linux environment variable
-to force load a shared library into an executable. This allows functions defined in FL to transparently
-overload the original ones without the need to modify or recompile the analysis pipeline.
-
-To avoid some pitfalls in deterministic arithmetics like producing results out of the function definition,
-FL instruments the functions by wrapping them so that only the original functions' output
-is perturbed instead of input or their implementation.
-Listing~\ref{algo:wrapper} shows an example of this wrapping for the log function in both single and double precisions.
-In this script, the original functions are called by \texttt{dlsym},
-a function that returns the memory address of a symbol using the handle of \texttt{RTLD\_NEXT}.
-This allows one to provide a wrapper around a function in another shared library.
-Also, the MCA instrumentation is activated by adding a floating-point zero to the output of the original function
-so that the result of this summation is perturbed and returned.
-
-% \lstdefinestyle{customc}{
-%   belowcaptionskip=1\baselineskip,
-%   breaklines=true,
-%   frame=L,
-%   xleftmargin=\parindent,
-%   language=C,
-%   showstringspaces=false,
-%   basicstyle=\footnotesize\ttfamily,
-%   keywordstyle=\bfseries\color{green!40!black},
-%   commentstyle=\itshape\color{purple!40!black},
-%   identifierstyle=\color{blue},
-%   stringstyle=\color{orange},
-% }
-
-\lstdefinestyle{customasm}{
-  belowcaptionskip=1\baselineskip,
-  frame=L,
-  xleftmargin=\parindent,
-  language=[x86masm]Assembler,
-  basicstyle=\footnotesize\ttfamily,
-  commentstyle=\itshape\color{purple!40!black},
-}
-\lstinputlisting[caption=Sample wrapper script, label=algo:wrapper, style=customasm]{wrapper.c}
-%\lstinputlisting[caption=Scheduler, style=customc]{../wrapper2.c}
-
-FL allows measuring the effect of numerical variability by running a program multiple times
-with the feature of controlling the magnitude of the perturbations as perceived by the application.
-FL enables us to assess the software packages that are dynamically linked to the mathematical library.
-So, it is important to trace the tool dependencies of the pipelines to understand the different libraries
-involved during the pipeline executions.
-
 \subsection{fMRI analysis \& Dataset}
 
-We replicated the fMRI analysis described as study `ds000001' in~\cite{bowring2019exploring}, relying on
-the data publicly available in OpenNeuro at \url{https://openneuro.org/datasets/ds000001}
-and using the three main software packages for fMRI data processing, namely
-FMRIB Software Library (FSL)~\cite{jenkinson2012fsl}, Analysis of Functional NeuroImages (AFNI)~\cite{cox1996afni},
-and Statistical Parametric Mapping(SPM)~\cite{penny2011statistical}.
-We selected this analysis because the methods and datasets were explicitly
-written to be accessible and reproducible. This enabled us to reanalyze fMRI experiments using the FL framework and
-compare WT and BT variabilities.
+We replicated the fMRI analysis described as study `ds000001'
+in~\cite{bowring2019exploring} \tristan{check if this dataset was acquired
+and analysed previously, and if so cite the original paper}, relying on the
+data publicly available in OpenNeuro at
+\url{https://openneuro.org/datasets/ds000001} and using the three main
+software packages for fMRI data processing, namely FMRIB Software Library
+(FSL)~\cite{jenkinson2012fsl}, Analysis of Functional NeuroImages
+(AFNI)~\cite{cox1996afni}, and Statistical Parametric
+Mapping(SPM)~\cite{penny2011statistical}. We selected this dataset because
+comparable analysis pipelines implemented in FSL, AFNI and SPM 
+were already published and extensively described in~\cite{bowring2019exploring}.
+Furthermore, the work in~\cite{bowring2019exploring} already evaluated the effect of tool variability for
+this dataset, which we intended to complement with the present quantification of numerical variability.
 
-In the selected study, 16 healthy adult subjects participated in the balloon analog risk task to measure
-risk-taking behavior over three scanning sessions.
-This study included preprocessing, first-level, and second-level analyses that were implemented with all three software.
-Table~\ref{table:pipeline-steps} shows the steps that were taken in the procedure of analyses for each tool in the original study.
-In the original study, a number of preprocessing steps widely accepted within the community, such as motion correction,
-segmentation, brain extraction, and registration, were applied in all analyses to ensure that results from each software
-package could be compared objectively.
-A full description of the pipelines implemented within three packages is presented in~\cite{bowring2019exploring,schonberg2012decreasing}.
+In the selected study, 16 healthy adult subjects participated in the
+balloon analog risk task \tristan{cite the task specifically} to measure
+risk-taking behavior over three scanning sessions \tristan{cite the
+original study (not Alex')}. We reused the preprocessing, first-level, and
+second-level analyses implemented by~\cite{bowring2019exploring} consistently across all three software packages using 
+widely accepted analytical steps. Table~\ref{table:pipeline-steps} summarizes the analytical steps in each pipeline.
+More details are available in~\cite{bowring2019exploring,schonberg2012decreasing} \tristan{cite only one ref, the one that gives the right details}.
 
@@
       \end{tabular}
-    \caption{Software processing steps. Table is adapted from~\cite{bowring2019exploring}.}
+    \caption{Software processing steps (adapted from~\cite{bowring2019exploring}).}
     \label{table:pipeline-steps}
@@
 
+\subsection{Fuzzy libmath environment}
+
+To introduce controlled amounts of numerical error in the analyses, we used the Fuzzy Libmath (FL) library~\cite{salari2021accurate}, an MCA-instrumented 
+version of the GNU mathematical library (libmath).
+Using FL, we can simulate numerical variability at the level of machine error \tristan{you really shouldn't put so much emphasis on machine error so early in the description.
+First, explain how FL works, then, say that you used it to simulate machine error but not only.}, the floating-point rounding error
+caused by floating-point representation limits defined by the hardware \tristan{this is a quite bad definition of machine error}.
+
+FL works based on the MCA, a floating-point arithmetic that simulates roundoff and catastrophic cancellation errors
+by introducing a controlled amount of noise in the floating-point operations 
+through the following perturbation model~\cite{Parker1997-qq}:
+
+\begin{equation} \label{eq:mca_inexact}
+  inexact(x) = x + 2^{e_x-t}\xi
+\end{equation}
+
+where $e_x$ is the exponent in the floating-point representation of $x$,
+$t$ is the virtual precision, the number of bits in mantissa that will not be perturbed,
+and $\xi$ is a random uniform variable of $(-\frac{1}{2}, \frac{1}{2})$.
+The MCA perturbations are automated using Verificarlo tool~\cite{denis2015verificarlo} at compilation time.
+
+The instrumented functions are loaded in the pipeline using LD\_PRELOAD, a Linux environment variable
+to force load a shared library into an executable. This allows functions defined in FL to transparently
+overload the original ones without the need to modify or recompile the analysis pipeline.
+
+FL only introduces perturbations in the output values of mathematical
+functions but not in their implementation. This is done by wrapping the original functions 
+and applying function \texttt{inexact} to their returned values.
+Listing~\ref{algo:wrapper} shows an example of this wrapping for the log function in both single and double precisions.
+In this script, the original functions are called by \texttt{dlsym},
+a function that returns the memory address of a symbol, in our case \texttt{RTLD\_NEXT}, the address of the next occurrence of the function.
+These wrappers are compiled with Verificarlo for each function. The MCA
+instrumentation is activated by adding a floating-point zero to the output
+of the original function so that this summation is instrumented.
+
+% \lstdefinestyle{customc}{
+%   belowcaptionskip=1\baselineskip,
+%   breaklines=true,
+%   frame=L,
+%   xleftmargin=\parindent,
+%   language=C,
+%   showstringspaces=false,
+%   basicstyle=\footnotesize\ttfamily,
+%   keywordstyle=\bfseries\color{green!40!black},
+%   commentstyle=\itshape\color{purple!40!black},
+%   identifierstyle=\color{blue},
+%   stringstyle=\color{orange},
+% }
+
+\lstdefinestyle{customasm}{
+  belowcaptionskip=1\baselineskip,
+  frame=L,
+  xleftmargin=\parindent,
+  language=[x86masm]Assembler,
+  basicstyle=\footnotesize\ttfamily,
+  commentstyle=\itshape\color{purple!40!black},
+}
+\lstinputlisting[caption=Sample wrapper script, label=algo:wrapper, style=customasm]{wrapper.c}
+%\lstinputlisting[caption=Scheduler, style=customc]{../wrapper2.c}
+
+FL allows measuring the effect of numerical variability by running a program multiple times, 
+resulting in multiple independent realizations of the same analysis. Each of these samples 
+are equally plausible estimates of the true numerical result.
+
+FL enables us to assess the software packages that are dynamically linked to the mathematical library.
+So, it is important to trace the tool dependencies of the pipelines to understand the different libraries
+involved during the pipeline executions \tristan{this is not methods. Here you should report how you validated the instrumentation 
+of each pipeline: (1) dependency analysis, (2) runtime checks, etc}.
 \subsection{Data processing}
 
-To capture variability in BT, the fMRI analysis pipeline was processed using three of the most popular software
-packages in neuroimaging, including FSL (version 5.0.10), AFNI (version 18.1.09), and SPM (version SPM12, r7771)
-executed with GNU/Octave (version 5.2). 
-FSL and AFNI scripts were executed in Python 2.7. We also used a fixed number of 7 threads in AFNI executions
-to reproduce similar results to the original study in a feasible execution time.
+To measure between-tool (BT) variability, we executed the pipelines described in~\cite{bowring2019exploring}
+with FSL version 5.0.10, AFNI version 18.1.09, and SPM12 version r7771
+executed with GNU/Octave version 5.2. \tristan{are these versions the same as in Alex' paper?} 
+FSL and AFNI scripts were executed in Python 2.7 \tristan{why?}. We also used a fixed number of 7 threads in AFNI executions,
+to reproduce similar results in~\cite{bowring2019exploring} in a feasible execution time.
 All the analyses were conducted on the same operating system, CentOS 7.3.
-We ensured that the software versions used in all experiments were similar to the original study,
+We ensured that the software versions \tristan{you mentioned versions before, the writing is a bit circular here} used in all experiments were similar to the original study,
 and encapsulated them in Docker container images with available Dockerfiles at \url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}.
 
-In addition, the same subjects and fMRI analysis were processed with the same configurations in the FL environment
-to produce results in WT variability.
-We applied instrumentations at the virtual precision (t) of 53 bits for double-precision floating-point values
-and 24 bits for single-precision values. Three Fuzzy samples were generated, to match the number of tool samples.
+The same subjects and analyses were conducted in the same configurations
+with the FL environment, to measure within-tool (WT) variability. We
+applied instrumentations at the virtual precision t=53 bits for
+double-precision floating-point values and t=24 bits for single-precision
+values. Three fuzzy samples were generated for each subject and tool, to
+match the number of tool samples. \tristan{mention that for FSL you also used more virtual precisions}
 
-We evaluated WT and BT variabilities in thresholded and unthresholded group-level activation maps.
+We evaluated WT and BT variabilities in thresholded and unthresholded group-level and subject-level t-statistics maps.
 We computed voxel-wise standard deviations of T-statistic values for each pair of tools
-and then compared the distribution of standard deviations in both conditions.
-We computed the WT standard deviation as the square root of the summation of variances between samples in each tool.
+and then compared the distribution of \tristan{there's no distribution analysis in your results} standard deviations in both conditions.
+We computed the WT standard deviation as the square root of the summation of variances between samples in each tool. \tristan{write it as a formula, it's important enough and will be clearer}
+
 Moreover, we determined region-by-region Dice coefficients for the thresholded maps for each pair of tools.
@@
 Dice values in WT are computed as the average pair-wise Dices among three Fuzzy samples for each pair of tools.
-Also, we compared the correlation of Dice scores normalized by the region sizes in both conditions.
+Also, we compared the correlation of Dice scores normalized by the region sizes in both conditions \tristan{move to results}.
 

### 2021-10-14 paper/paper.tex
Update figures and result section

@@
 \usepackage{dingbat}
+\usepackage{mathtools}
 
@@
 We replicated the fMRI analysis described as study `ds000001'
-in~\cite{bowring2019exploring} \tristan{check if this dataset was acquired
-and analysed previously, and if so cite the original paper}, relying on the
+in~\cite{schonberg2012decreasing}, relying on the
 data publicly available in OpenNeuro at
@@
 In the selected study, 16 healthy adult subjects participated in the
-balloon analog risk task \tristan{cite the task specifically} to measure
-risk-taking behavior over three scanning sessions \tristan{cite the
-original study (not Alex')}. We reused the preprocessing, first-level, and
+balloon analog risk task~\cite{lejuez2002evaluation} to measure
+risk-taking behavior over three scanning sessions~\cite{schonberg2012decreasing}.
+We reused the preprocessing, first-level, and
 second-level analyses implemented by~\cite{bowring2019exploring} consistently across all three software packages using 
 widely accepted analytical steps. Table~\ref{table:pipeline-steps} summarizes the analytical steps in each pipeline.
-More details are available in~\cite{bowring2019exploring,schonberg2012decreasing} \tristan{cite only one ref, the one that gives the right details}.
+More details are available in~\cite{bowring2019exploring}.
 
@@
 version of the GNU mathematical library (libmath).
-Using FL, we can simulate numerical variability at the level of machine error \tristan{you really shouldn't put so much emphasis on machine error so early in the description.
-First, explain how FL works, then, say that you used it to simulate machine error but not only.}, the floating-point rounding error
-caused by floating-point representation limits defined by the hardware \tristan{this is a quite bad definition of machine error}.
-
 FL works based on the MCA, a floating-point arithmetic that simulates roundoff and catastrophic cancellation errors
@@
 are equally plausible estimates of the true numerical result. 
+We used FL to simulate machine error, the relative error between a real number and its floating-point counterparts
+(e.g., $2^{-53}$ for IEEE-754 double precision).
+Moreover, FL allows simulating any virtual precision
+by controlling the magnitude of the injected error and
+thus to not be limited to the machine precision.
 
-FL enables us to assess the software packages that are dynamically linked to the mathematical library.
-So, it is important to trace the tool dependencies of the pipelines to understand the different libraries
-involved during the pipeline executions \tristan{this is not methods. Here you should report how you validated the instrumentation 
-of each pipeline: (1) dependency analysis, (2) runtime checks, etc}.
+The presented method does not require any
+particular software instrumentation in the data analysis code: it only
+assumes that executables are dynamically linked against GNU libc. For this purpose,
+(1) we captured the list of dynamic library dependencies using the \texttt{ldd} Linux utility for the software executables,
+(2) we traced the system library calls using \texttt{ltrace} Linux program while running the pipeline processes.
+
 \subsection{Data processing}
@@
 with FSL version 5.0.10, AFNI version 18.1.09, and SPM12 version r7771
-executed with GNU/Octave version 5.2. \tristan{are these versions the same as in Alex' paper?} 
-FSL and AFNI scripts were executed in Python 2.7 \tristan{why?}. We also used a fixed number of 7 threads in AFNI executions,
+executed with GNU/Octave version 5.2.
+All these software versions were identical to the original study except for SPM
+that we used Octave instead of MATLAB to enable mathematical function instrumentation using FL,
+while MATLAB uses its built-in functions and does not allow to apply FL.
+We also used a fixed number of 7 threads in AFNI executions,
 to reproduce similar results in~\cite{bowring2019exploring} in a feasible execution time.
 All the analyses were conducted on the same operating system, CentOS 7.3.
-We ensured that the software versions \tristan{you mentioned versions before, the writing is a bit circular here} used in all experiments were similar to the original study,
-and encapsulated them in Docker container images with available Dockerfiles at \url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}.
+%We ensured that the software versions \tristan{you mentioned versions before, the writing is a bit circular here} used in all experiments were similar to the original study,
+We encapsulated the above-mentioned software packages in Docker container images with available Dockerfiles at \url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}.
 
@@
 double-precision floating-point values and t=24 bits for single-precision
-values. Three fuzzy samples were generated for each subject and tool, to
-match the number of tool samples. \tristan{mention that for FSL you also used more virtual precisions}
+values. Three Fuzzy samples were generated for each subject and tool, to
+match the number of tool samples.
+We also captured further instrumentations for FSL tool for the virtual precisions ranged from 53 bits to 1 bit by steps of 2,
+such that only double-precision was changed and single-precision was set to 24 bits for $t >= 24$ bits,
+and both double- and single-precision simultaneously were changed for $t < 24$ bits.
 
 We evaluated WT and BT variabilities in thresholded and unthresholded group-level and subject-level t-statistics maps.
-We computed voxel-wise standard deviations of T-statistic values for each pair of tools
-and then compared the distribution of \tristan{there's no distribution analysis in your results} standard deviations in both conditions.
-We computed the WT standard deviation as the square root of the summation of variances between samples in each tool. \tristan{write it as a formula, it's important enough and will be clearer}
+We computed voxel-wise standard deviations of t-statistic values for each pair of tools
+and then compared the standard deviations in both conditions.
+We computed the WT standard deviation as the square root of the summation of variances between samples in each tool:
+
+\begin{equation} \label{eq:mca_std}
+  \begin{multlined}
+  STD_{WT} = \sqrt{VAR_{tool1} + VAR_{tool2}}
+%  VAR_{x} = \sum_{i=1}^{n} \frac{(x_i - \bar{x})}{n-1}
+  \end{multlined}
+\end{equation}
 
@@
 Dice values in WT are computed as the average pair-wise Dices among three Fuzzy samples for each pair of tools.
-Also, we compared the correlation of Dice scores normalized by the region sizes in both conditions \tristan{move to results}.
 
-\tristan{did you check standard error vs standard deviation?}\ali{STD shows variability of data in relation to the mean (what we are looking for here),
-while SE is a type of STD (computed as $\frac{\sigma}{\sqrt{n}}$) for distribution of means (we use it when we are interested in the precision of means in different samples).}
+% \tristan{did you check standard error vs standard deviation?}\ali{STD shows variability of data in relation to the mean (what we are looking for here),
+% while SE is a type of STD (computed as $\frac{\sigma}{\sqrt{n}}$) for distribution of means (we use it when we are interested in the precision of means in different samples).}
 
@@
 
-We ensured a successful replication of the analyses initally presented in~\cite{bowring2019exploring}
-by visually checking the overlap \tristan{what do you mean ``visually checking the overlap?'' Afair we had looked at the difference images?} of T-statistic group maps.
-We could replicate the analyses across tools with an exception for AFNI that produced results with slight differences \tristan{this needs discussion on how to present it}. 
-This might be caused by the compiler variations, or different hardware and their optimizations
-such as out-of-order execution (dynamic scheduling) paradigm~\cite{duben2014use,demmel2013numerical}.
-In this paradigm, the processors might execute instructions out of the original order they appear based on
-the availability of input data and execution units to use resources efficiently. Therefore, it might
-compute floating-point operations in a different order, which often leads to different results \tristan{is this a compiler optimization?
-If so, just mention ``compiler optimizations such as dynamic scheduling'', no need to enter into details}.
+We ensured a successful replication of the analyses initially presented in~\cite{bowring2019exploring}
+by comparing t-statistic group maps with results in the original study.
+We found identical checksums in the results of FSL.
+Also, we could replicate results with the same SPM version and MATLAB as in the original study with visually imperceptible differences.
+Changes in the SPM version and replacing Octave with MATLAB resulted in visually slight differences which were still hard to distinguish between them.
+For AFNI, the activation maps were similar overall; however, visual differences were noticeable.
+This might be caused by the hardware optimizations such as dynamic scheduling~\cite{demmel2013numerical}.
+We could confirm that AFNI results were passed QC by visually assessing the registration results of each individual subject.
 
-Summary statistics for the group-level unthresholded and thresholded T-statistics \tristan{harmonize capitalization in ``T-statstics / t-statistics'' (t should be lower case unless it's the first word in the sentence)} are reported in Table~\ref{table:pipeline-stats}.
+Summary statistics for the group-level unthresholded and thresholded t-statistics are reported in Table~\ref{table:pipeline-stats}.
 % The variability between results of each pair of tools in BT and individual tools in WT was measured using the mean and standard deviation of absolute differences.
@@
 %%%%%%%%%% Summary of statstics %%%%%%%%
-\setlength{\tabcolsep}{7pt}
+\setlength{\tabcolsep}{5pt}
 \begin{table}[h]
@@
         \rowcolor{lightgray}
-        {Between Tools} & FSL vs. SPM        &  0.043       & 1.282      & 0.242     & 0.443  \\
+        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  \\
         \rowcolor{lightgray}
-        {(BT)} & FSL vs. AFNI         &  0.099       & 1.548      & 0.302     & 0.547  \\
+        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  \\
         \rowcolor{lightgray}
-        {} & AFNI vs. SPM         &  0.079       & 1.475      & 0.254     & 0.608  \\
-        {Within Tool} & FSL    &  0.005       & 0.354      & 0.034     & 0.082  \\
-        {(WT)}   & SPM    &  0.006       & 0.252      & 0.025     & 0.054  \\
-        {}   & AFNI   &  0.017       & 0.434      & 0.041     & 0.128  \\
+        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  \\
+        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  \\
+        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  \\
+        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  \\
         \bottomrule
     \end{tabular}
-    \caption{Summary of voxel-wise mean and standard deviation of absolute differences in group-level T-statistics in BT and WT. \tristan{discuss this caption}}
+    \caption{Summary of voxel-wise mean and standard deviation in group-level t-statistics in BT and WT.}
     \label{table:pipeline-stats}
@@
 %Fig 1
-Comparisons of standard deviations between thresholded images \tristan{Table II should show summary statistics from the maps, is it the case?} in WT and BT
+Comparisons of standard deviations between thresholded images in WT and BT
 on MNI space are shown in Figure~\ref{fig:thresh-maps}.
-While we observed substantial BT variations with the average standard deviation $\approx$ 1.5 \tristan{why approx? },
-the magnitude of WT variations was much lower with the average standard deviation $\approx$ 0.5,
-as was anticipated. However, numerical variability was still significant in WT results \tristan{this doesn't mean much. Also, ``significant'' means ``statistically significant''.}.
-%Moreover, the numerical perturbations produces variations in similar order og magnitude in WT compared to BT variations
+While we observed substantial BT variations with the average standard deviation 1.43,
+the magnitude of WT variations was much lower with the average standard deviation 0.34,
+as was anticipated. 
 Moreover, the magnitude of WT variations reached the magnitued of BT variations
@@
 Figure~\ref{fig:dice-thresh} compares regional normalized Dice coefficients of
-activated voxels, showing a linear correlation between BT and WT \tristan{report p-value}. 
-Also, small P-values across all three pairs, including \num{1e-10} for \fslafni, \num{6e-04} for \fslspm,
-and \num{2e-05} for \afnispm, confirmed this correlation of similarities \tristan{are these the p values of the regressions?}.
+activated voxels, showing a linear correlation between BT and WT with p-value $< 0.05$ in all three pairs.
 % The vertical line where the Dice score is zero in BT demonstrates regions in the brain with no overlaps between activated voxels in BT but WT,
@@
 % Fig3
-Similar conclusions are drawn from the unthresholded t-statistcs maps
+Similar conclusions are drawn from the unthresholded t-statistics maps
 (Figure~\ref{fig:unthresh-maps}). BT variability is an order of magnitude
@@
 comparable in some regions.
-
-% shows the brain maps of standard deviations for group-level unthresholded
-% T-statistics in WT and BT. Results show a different order of magnitude of
-% variations in WT and BT with standard deviation of $\approx$ 0.12 and
-% $\approx$ 0.5 on average, respectively. We observed regions in the brain
-% where the magnitude of standard deviation was close to zero in WT, but it
-% exceeded 2.0 in BT, such as some parts of the limbic and frontal lobes in
-% the sagittal plane. However, the brain maps included voxels with
-% approximately zero differences of standard deviations in WT and BT, which
-% are uniformly distributed.
 
@@
 % Fig4
-\tristan{rewrite this paragraph}
-The scatter plot in Figure~\ref{fig:unthresh-correlation} represents the correlation of standard deviation in WT and BT variability.
-We found two major clusters, including the identity cluster that corresponds to the correlations
-between BT and WT with the ratio of $0.5 < BT/WT < 2$ where the standard deviations were bigger than 0.1,
-and the upper cluster that shows voxels where BT $\approx$ 0.
-The percentage of voxels included in the identity cluster was \%9.9 in \fslspm, \%17.3 in \fslafni, and \%13.8 in \afnispm,
-and in the upper cluster was $\approx$ \%1 for each pair of tools.
-The identity area is also represented on the MNI space in the second row in Figure~\ref{fig:unthresh-correlation}.
-This figure shows the spatial localization of the parts of the brain that BT variability was correlated with the numerical variability.
-This refines the presented results in Figure~\ref{fig:unthresh-maps},
-which indicated how the correlation is uniformly distributed across the brain.
+Figure~\ref{fig:unthresh-correlation} highlights the voxel-wise standard deviations in WT and BT variability
+with the identity lines where separate voxels with the standard deviation ratio of $0.5 < BT/WT < 2$.
+This identity area is represented on MNI space in the second row in Figure~\ref{fig:unthresh-correlation}
+for the voxels with the magnitude of standard deviation $> 0.1$.
+The maps show the spatial localization of parts of the brain where the numerical variability simulated BT variability.
+This refines the presented results in Figure~\ref{fig:unthresh-maps}-\textbf{C},
+indicated voxels with similar magnitude of BT and WT variations were uniformly distributed across the brain.
 
@@
       \end{subfigure}
-      \caption{Correlation of standard deviations in BT and WT from the unthresholded T-statistics.
-      The first row plots the correlations voxel by voxel and is highlighted with different colors
-      for two clusters, including the upper cluster (purple color) and the correlated cluster (green color).
-      The second row maps the correlated area on the MNI space. \tristan{Fix colors and captions (to be discussed)}}
+      \caption{Scatter plots of unthresholded group t-statistics standard deviations computed between tools and within tools.
+        Identity lines distinguish voxels where the standard deviation ratio of BT/WT is in the interval [0.5, 2]
+        and are represented on brain maps in the second row.}
     \label{fig:unthresh-correlation}
@@
 
-  % Table~\ref{table:firstlevel-stats} shows a summary of the statistics from the subject-level analysis results.
-  % This table represents the average of the mean and standard deviation of absolute differences of unthresholded T-statistics
-  % across 16 subjects for each pair of tools.
-  % Results show the subjects that were produced the least and the most variability among all pairs, subjects,
-  % and both BT and WT.
-  % While the subject with the least variability generated results with the mean of $\approx$ 0.093 and standard deviation of $\approx$ 0.174,
-  % the subject with the most variability produced results with the mean of $\approx$ 0.183 and standard deviation of $\approx$ 0.341.
-  % This observation shows an order of magnitude of variability between subjects.
-
   Figure~\ref{fig:unthresh-maps-sbj} shows BT and WT variability of the
   unthresholded t-statistics for the subject with the highest WT
-  variability among the 16 subjects. The average standard deviation for
-  this subject was $\approx$ 0.152 for WT and $\approx$ 0.466 for BT
-  \tristan{remove $\approx$, discuss what these numbers represent}.
+  variability among the 16 subjects.
+  We observed substantial WT variations with the average standard deviation 0.099 compared to 
+  the average standard deviation 0.466 for BT variations.
   As can be seen in the Figure, WT variability approaches and even surpasses BT variability in some regions.
+  This subject also revealed that WT variability mainly concentrated in some regions  
+  contrary to the corresponding variability from unthresholded group-level t-statistics which was uniformly distributed across the brain.
 
@@
     %\caption{Standard deviation of thresholded t-statistics map on template surface}
-  \caption{Maps of standard deviation of unthresholded T-statistics in subject 5. The first and second rows show
-  maps on BT and WT results, respectively, and the third row represents maps of their differences.}
+    \caption{Unthresholded subject t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
+    This is for the subject with the highest WT variability.}
   \label{fig:unthresh-maps-sbj}
@@
 While the previous results were obtained at the virtual precision of 53~bits for double-precision floating-point values
-and 24~bits for single-precision values, we evaluated WT variability across different virtual precisions for FSL. \tristan{make sure this is described in the methods}
-Figure~\ref{fig:across-precisions} represents the RMSE between standard deviations of each pair of tools in BT and FSL variations across virtual precisions in WT \tristan{clarify what is shown}.
-%Consistant with the previous results, 
-RMSE between WT and BT for \fslafni was the highest, and \fslspm was the lowest in all virtual precisions.
-This also shows the similar plateaus were generated in all three pairs of tools.
-Moreover, the analyses crashed for the precisions below t=11 bits during the FSL preprocessing steps. 
-This needs further investigations to understand the exact failure reasons.
+and 24~bits for single-precision values, we evaluated WT variability across different virtual precisions for FSL.
+Figure~\ref{fig:across-precisions} represents the root-mean-square error (RMSE) between the standard deviations per voxel
+in BT and WT resulted from the Fuzzy FSL,
+substantiating that how variabilities in both conditions are close to each other across different virtual precisions.
 
-\tristan{make a full figure, similar to Fig 1, 3, and 5. }We determined the virtual precision of t=27 bits as the precision that minimized the RMSE between standard deviations in BT on average and WT.
+We determined the virtual precision of t=17 bits as the precision that minimized the RMSE between BT and WT on average.
 This is the precision that numerical perturbations in FSL more closely simulated BT variability.
-Figure~\ref{fig:gnp-mni} shows the brain maps of numerical variability obtained from the analysis with FSL at t=27 bits.
-This represents regions with significant variability in the frontal, parietal, and limbic lobes.
+The brain maps of standard deviations between BT and WT obtained from the Fuzzy FSL at t=17 bits (Figure~\ref{fig:gnp-mni})
+show significant WT variability, particularly for some regions in the frontal, parietal, and limbic lobes, close to the BT variability.
 
@@
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \caption{Comparison of RMSE values computed between BT and WT resulted from FSL tool for different virtual precisions \tristan{Make a full figure, similar to Fig 5, 3, and 1.}.}
+      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions. WT is computed from three samples of FSL tool.}
     \label{fig:across-precisions}
@@
   \begin{figure}[ht]
-    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
+    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
         \centering
-        \includegraphics[width=\columnwidth]{figures/bt-wt.png}
+        \includegraphics[width=\textwidth]{figures/bg_global_precision.pdf}
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \caption{Comparison of standard deviations in BT averaged across pairs of tools and WT resulted from FSL tool
-      at the virtual precision of t=27 bits.}
+        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
+        WT is computed from three samples of FSL tool at the virtual precision of t=17 bits.}
     \label{fig:gnp-mni}
@@
   \item[$\bullet$] Numerical instability in individual analyses is attenuated in group analyses. This is an issue for the development of fMRI biomarkers.
+
   \item[$\bullet$] Comparision between FSL, SPM and AFNI. Discussion on the instrumentation of math functions only.
 \end{itemize}
-
-% There are many statistical comparisons, but the neuro-scientific interpretation of results is not on my side.
 

### 2021-10-17 paper/paper.tex
Update result and discussion sections

@@
 All the analyses were conducted on the same operating system, CentOS 7.3.
-%We ensured that the software versions \tristan{you mentioned versions before, the writing is a bit circular here} used in all experiments were similar to the original study,
 We encapsulated the above-mentioned software packages in Docker container images with available Dockerfiles at \url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}.
@@
 
-% \tristan{did you check standard error vs standard deviation?}\ali{STD shows variability of data in relation to the mean (what we are looking for here),
-% while SE is a type of STD (computed as $\frac{\sigma}{\sqrt{n}}$) for distribution of means (we use it when we are interested in the precision of means in different samples).}
-
 \section{Results}
@@
 Also, we could replicate results with the same SPM version and MATLAB as in the original study with visually imperceptible differences.
-Changes in the SPM version and replacing Octave with MATLAB resulted in visually slight differences which were still hard to distinguish between them.
+Changes in the SPM version and replacing Octave with MATLAB resulted in visually small differences which were still hard to distinguish between them.
 For AFNI, the activation maps were similar overall; however, visual differences were noticeable.
 This might be caused by the hardware optimizations such as dynamic scheduling~\cite{demmel2013numerical}.
-We could confirm that AFNI results were passed QC by visually assessing the registration results of each individual subject.
+We could confirm that AFNI results were passed the quality checks by visually assessing the registration results of each individual subject.
 
 Summary statistics for the group-level unthresholded and thresholded t-statistics are reported in Table~\ref{table:pipeline-stats}.
-% The variability between results of each pair of tools in BT and individual tools in WT was measured using the mean and standard deviation of absolute differences.
 Overall, WT variability was an order of magnitude lower than BT variability for both means and standard deviations.
 While the highest variability was observed in \fslafni, \fslspm was made the least variations in BT.
-Results also show that AFNI was generated the most variability in WT among the three tools \tristan{this needs statistical testing}.
+We also computed t-test statistics to examine differences in WT variability between tools.
+Results show that AFNI was generated the most variability in WT among the three tools with 
+the high t-value 39.6 between \fslafni samples and 65.5 between \afnispm samples, and p-value $< 0.05$.
+\ali{I'm checking this with Greg}.
 
@@
 activated voxels, showing a linear correlation between BT and WT with p-value $< 0.05$ in all three pairs.
-% The vertical line where the Dice score is zero in BT demonstrates regions in the brain with no overlaps between activated voxels in BT but WT,
-% including left/right `V1\_ROI'\footnote{The primary visual cortex} in \fslafni and \fslspm,
-% and left/right `TGd\_ROI'\footnote{The area TG dorsal (part of lateral temporal cortex)} in \afnispm results.
 
@@
       \caption{Scatter plots of unthresholded group t-statistics standard deviations computed between tools and within tools.
-        Identity lines distinguish voxels where the standard deviation ratio of BT/WT is in the interval [0.5, 2]
+        Identity lines distinguish voxels where the standard deviation ratio of BT/WT is in the interval (0.5, 2)
         and are represented on brain maps in the second row.}
@@
 The brain maps of standard deviations between BT and WT obtained from the Fuzzy FSL at t=17 bits (Figure~\ref{fig:gnp-mni})
-show significant WT variability, particularly for some regions in the frontal, parietal, and limbic lobes, close to the BT variability.
+show significant WT variability, particularly for some regions in the frontal, parietal, and limbic lobes, close to BT variability.
 
@@
 
-\begin{itemize}
+We represented differences in the results of an fMRI analysis between numerical variability
+and the variability arisen from software package variations.
+Although BT variability was an order of magnitude higher than WT variability on average,
+we demonstrated regions in the brain maps that numerical perturbations could simulate BT variability.
+The correlation of these variabilities suggests that numerical perturbations can be used to evaluate the robustness of the analyses
+to inter-software disparities.
 
-  \item[$\bullet$ ] In this study, we represented the magnitude of differences in BT and WT results.
-  We obtained more instability in BT compared to WT. Also we showed how between tool variations
-  are correlated with numerical variability.
-  While we only perturbed basic mathematical functions, perturbing linear algebra, in particular, could increase WT variability.
+While switching between \fslspm was generated the least BT and WT variabilities consistently, the most level of these variabilities was identified
+between \fslafni and \afnispm. We also found AFNI as the most sensitive tool to numerical perturbations.
+These results do not indicate which software package is better or worse since there is no ground-truth model for the analyses.
+However, this study revealed the importance of numerical instability in the selected tools for doing fMRI analyses.
+It provided a view of related numerical variability of which should be taken into consideration by the software developers.
 
-  \item[$\bullet$ ] Generally, we obtained more uncertainty on thresholded results, probably due to different thresholding
-  methods used in different tools. This can raise further investigations on the thresholding techniques toward stability.
-  Also, we obtained significant instabilities in specific subjects so that healed by averaging in group-level analyses.
+We found that numerical instability in individual analyses was attenuated in group analyses
+since we obtained substantially higher variability in t-statistics at the level of subjects.
+This is consistent with the findings in~\cite{bowring2021isolating} in which identified the first-level signal model as the largest
+source of variability across the three tools for this study.
+This is an issue for the development of fMRI biomarkers.
+As a solution, we can aggregate the results obtained from numerical perturbations to improve biomarkers,
+as suggested in~\cite{kiar2020numerical} where data augmentation using numerical perturbations resulted in a better classification in connectomics.
 
-  \item[$\bullet$ ] We showed that reducing the number of virtual precision bits leads to more instabnilities in which can exceeds variability compared to BT.
-  We also showed the numerical perturbations can perfectly simulate BT variability in some regions.
+It is notable that we obtained more uncertainty on thresholded results than unthresholded maps, %This issue is 
+probably due to different thresholding values used in different tools.
+This is consistent with the observations in~\cite{bowring2021isolating} where identified a high correlation between unthresholded t-statistic maps,
+but substantially low Dice coefficient for activations in the thresholded maps.
+This raises further investigations on thresholding techniques to reduce instabilities.
 
-  \item[$\bullet$] Numerical instability in individual analyses is attenuated in group analyses. This is an issue for the development of fMRI biomarkers.
-
-  \item[$\bullet$] Comparision between FSL, SPM and AFNI. Discussion on the instrumentation of math functions only.
-\end{itemize}
+Given that FL only perturbs basic mathematical functions, we expect more numerical variability by perturbing linear algebra,
+in particular for non-scalar types like vectors or matrices. For the future study, this can be evaluated using MCA-instrumented versions 
+of BLAS and LABACK along with other libraries available in the Fuzzy project in Verificarlo's GitHub repository at github.com/verificarlo/fuzzy.
 

### 2021-10-19 paper/paper.tex
Update results

@@
 analysis remains understudied. This work presents a comparison of
-numerical and software variability for group-level functional MRI analysis
-\tristan{did we give up on individual analyses?}.
+numerical and software variability for group-level and subject-level functional MRI analyses.
 We reproduced a previous comparison between functional MRI analysis
@@
 numerical variability through Monte-Carlo arithmetic.
-We find that between-tool variability is an order of magnitude higher than numerical variability.
-\tristan{summarize conclusions}
+Although We found that between-tool variability was larger than numerical variability,
+we identified brain regions that numerical perturbations simulated between-tool variability.
+Furthermore, we found more numerical instability in thresholded maps than unthresholded ones
+and individual analysis than group-level analysis results.
 
@@
 Summary statistics for the group-level unthresholded and thresholded t-statistics are reported in Table~\ref{table:pipeline-stats}.
-Overall, WT variability was an order of magnitude lower than BT variability for both means and standard deviations.
-While the highest variability was observed in \fslafni, \fslspm was made the least variations in BT.
-We also computed t-test statistics to examine differences in WT variability between tools.
-Results show that AFNI was generated the most variability in WT among the three tools with 
-the high t-value 39.6 between \fslafni samples and 65.5 between \afnispm samples, and p-value $< 0.05$.
-\ali{I'm checking this with Greg}.
+Overall, BT variability was larger than WT variability for both means and standard deviations.
+This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between $BT(A, B)$, and $WT(A)$ and $WT(B)$ for $A$ and $B$ in $[FSL, SPM, AFNI]$.
+We obtained statistically significant values between BT and WT variability with t-value $> 70$ and p-value $< 0.05$ in both thresholded and unthresholded maps.
 
@@
 While we observed substantial BT variations with the average standard deviation 1.43,
-the magnitude of WT variations was much lower with the average standard deviation 0.34,
+the magnitude of WT variations was much smaller with the average standard deviation 0.34,
 as was anticipated. 
@@
 Similar conclusions are drawn from the unthresholded t-statistics maps
-(Figure~\ref{fig:unthresh-maps}). BT variability is an order of magnitude
-higher than WT variability overall, however, BT and WT variability are
-comparable in some regions.
+(Figure~\ref{fig:unthresh-maps}). BT variability is larger than WT variability overall, however,
+BT and WT variability are comparable in some regions.
 
@@
 Figure~\ref{fig:unthresh-correlation} highlights the voxel-wise standard deviations in WT and BT variability
-with the identity lines where separate voxels with the standard deviation ratio of $0.5 < BT/WT < 2$.
-This identity area is represented on MNI space in the second row in Figure~\ref{fig:unthresh-correlation}
-for the voxels with the magnitude of standard deviation $> 0.1$.
+with the identity lines that indicate voxels with the standard deviation of $BT = WT$.
+The identity area is represented on MNI space in the second row in Figure~\ref{fig:unthresh-correlation}
+for the voxels with the magnitude of standard deviation $> 0.1$ and the satndard deviation ratio of $0.5 < BT/WT < 2$.
 The maps show the spatial localization of parts of the brain where the numerical variability simulated BT variability.
@@
       \end{subfigure}
-      \caption{Scatter plots of unthresholded group t-statistics standard deviations computed between tools and within tools.
-        Identity lines distinguish voxels where the standard deviation ratio of BT/WT is in the interval (0.5, 2)
-        and are represented on brain maps in the second row.}
+      \caption{
+        Scatter plots of unthresholded group t-statistics standard deviations computed between tools and within tools.
+        The identity line distinguishes voxels where the standard deviation BT is equal to WT.
+        Voxels with the standard deviation ratio of BT/WT in the interval (0.5, 2) are represented on brain maps in the second row.}
     \label{fig:unthresh-correlation}
@@
 and the variability arisen from software package variations.
-Although BT variability was an order of magnitude higher than WT variability on average,
+Although BT variability was larger than WT variability on average,
 we demonstrated regions in the brain maps that numerical perturbations could simulate BT variability.
@@
 While switching between \fslspm was generated the least BT and WT variabilities consistently, the most level of these variabilities was identified
-between \fslafni and \afnispm. We also found AFNI as the most sensitive tool to numerical perturbations.
+between \fslafni and \afnispm. %We also found AFNI as the most sensitive tool to numerical perturbations.
 These results do not indicate which software package is better or worse since there is no ground-truth model for the analyses.

### 2021-10-25 paper/paper.tex
minor changes

@@
 but substantially low Dice coefficient for activations in the thresholded maps.
-This raises further investigations on thresholding techniques to reduce instabilities.
+This raises further investigations on thresholding techniques to reduce the associated instabilities.
 
@@
 in particular for non-scalar types like vectors or matrices. For the future study, this can be evaluated using MCA-instrumented versions
-of BLAS and LABACK along with other libraries available in the Fuzzy project in Verificarlo's GitHub repository at github.com/verificarlo/fuzzy.
+of BLAS and LAPACK along with other libraries available in the Fuzzy project in Verificarlo's GitHub repository at github.com/verificarlo/fuzzy.
 
@@
 
-\begin{itemize}
+We presented a comparison study between numerical variability introduced by floating-point perturbations and tool variability arised from software package variations.
+For an fMRI analysis, we measured a significant variability in both conditions, which was comparable for some brain regions.
+We showed the FL library as a valuable model based on MCA method for simulating the numerical variability.
+Moreover, we can leverage the MCA-instrumented libraries for simulating the numerical uncertainty in different studies.
 
-    \item[$\bullet$ ] Further studies can be evaluating the numerical stabilities within tool by focusing on the particular parts of
+Further work can be done to evaluate and localize the numerical stabilities within tools by focusing on the particular parts of
 the pipeline that has been identified as the main sources of variations in~\cite{bowring2021isolating}.
-    Also, we can invetigate the precision in WT variability that simulates mostly BT variability in the furure study.
-
-\end{itemize}
-
-\section{Acknowledgments}
+This helps to identify the accurate source of instabilities within pipelines and gradually improve the stability of the pipeline components.
 

### 2021-10-25 computs.py

@@ -12,44 +12,144 @@ import inspect
 from nilearn.image import math_img
 from lib import dice
 from statistics import mean
+import scipy.stats as stat
+from scipy.signal import resample
 import os
 
 
-############# COMPUTES STD. DEV.
+############# Global nearest precision
+
+def calculate_rmse(im1, im2):
+    """Computing the RMSE between two images."""
+    img1 = np.nan_to_num(im1.get_fdata())
+    img2 = np.nan_to_num(im2.get_fdata())
+
+    if img1.shape != img2.shape:
+        im1 = resample_from_to(im1, im2, order=0)
+        img1 = np.nan_to_num(im1.get_fdata())
+
+    bg_ = np.where((np.isnan(im1.get_fdata())) & (np.isnan(im2.get_fdata())), False, True)
+    img1 = img1[bg_]
+    img2 = img2[bg_]
+
+    return np.sqrt(np.mean((img1-img2)**2, dtype=np.float64), dtype=np.float64)
+
+
+def global_nearest_precision():
+    rmse_ = {}
+    all_rmse = {}
+    global_average_rmse = []
+
+    for p in range(11, 54, 2):
+        rmse_[p] = 0
+        all_rmse[str(p)] = []
+        for s in ['fsl-afni', 'fsl-spm', 'afni-spm']:
+            bt_ = nib.load('./data/std/{}-unthresh-std.nii.gz'.format(s))
+            # bt_ = bt_.get_fdata()
+            wt_fsl = nib.load('./data/std/FL-FSL/p{}_fsl_unthresh_std.nii.gz'.format(p))
+            # wt_fsl = wt_fsl.get_fdata()
+            rmse_value = calculate_rmse(bt_, wt_fsl)
+            all_rmse[str(p)].append(rmse_value)
+            rmse_[p] += rmse_value
+
+    all_rmse = np.transpose(np.array(list(all_rmse.values())))
+
+    return min(rmse_, key=rmse_.get), all_rmse
+
+
+def plot_rmse_nearest(all_rmse):
+    import matplotlib.cm as cm
+
+    fig = plt.figure(figsize=(15,10))
+    colors = ['red', 'green', 'blue']
+    tool_pair = ['fsl-afni', 'fsl-spm', 'afni-spm']
+    for s, rmse_ in enumerate(all_rmse):
+        #type_ = ""
[…]

### 2021-11-02 paper/paper.tex
Update minor edits

@@
 All the analyses were conducted on the same operating system, CentOS 7.3.
+The computations were performed on \href{https://www.computecanada.ca}{Compute Canada's} Béluga cluster nodes,
+each with 2× Intel Gold 6148 Skylake @ 2.4 GHz (40 cores/node) CPU and memory amount of 8 GB per core.
 We encapsulated the above-mentioned software packages in Docker container images with available Dockerfiles at \url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}.
@@
   \begin{multlined}
-  STD_{WT} = \sqrt{VAR_{tool1} + VAR_{tool2}}
+  \sigma_{WT} = \sqrt{\sigma_{tool1}^2 + \sigma_{tool2}^2}
 %  VAR_{x} = \sum_{i=1}^{n} \frac{(x_i - \bar{x})}{n-1}
@@
 Dice values in WT are computed as the average pair-wise Dices among three Fuzzy samples for each pair of tools.
+All Dice scores were normalized by the region sizes and remained in the range of 0 to 1.
 
 \section{Results}
-All scripts and data to create the figures presented in this section are available at \url{https://github.com/ali4006/fuzzy-neurotools} \tristan{move to lab org}.
-The computations were performed on \href{https://www.computecanada.ca}{Compute Canada's} Béluga cluster
-with 872 nodes, each with 2× Intel Gold 6148 Skylake @ 2.4 GHz (40 cores/node) CPU and node memory ranging from 92 to 752 GB.
+All scripts and data to create the figures presented in this section are available at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
 
@@
 Also, we could replicate results with the same SPM version and MATLAB as in the original study with visually imperceptible differences.
-Changes in the SPM version and replacing Octave with MATLAB resulted in visually small differences which were still hard to distinguish between them.
+%Changes in the SPM version and replacing Octave with MATLAB resulted in visually small differences which were still hard to distinguish between them.
 For AFNI, the activation maps were similar overall; however, visual differences were noticeable.
@@
 
+  Summary statistics for the subject-level unthresholded t-statistics are reported in Table~\ref{table:unthresh-maps-subjects}.
+  Overall, results represent similar findings with group-level t-statistics between WT and BT variations.
+
   Figure~\ref{fig:unthresh-maps-sbj} shows BT and WT variability of the
@@
   variability among the 16 subjects.
-  We observed substantial WT variations with the average standard deviation 0.099 compared to 
+  For this particular subject, we observed substantial WT variations with the average standard deviation 0.099 compared to 
   the average standard deviation 0.466 for BT variations.
@@
   contrary to the corresponding variability from unthresholded group-level t-statistics which was uniformly distributed across the brain.
+
+  %%%%%%%%%% Summary of statstics %%%%%%%%
+\setlength{\tabcolsep}{5pt}
+\begin{table}[h]
+    \centering
+    \begin{tabular}{cccc}
+        \toprule
+        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Unthresholded} \\
+        \cmidrule{3-4} \\
+        {} & {} & Mean & Std. dev. \\
+        \midrule
+        \rowcolor{lightgray}
+        {Between Tools} & FSL vs. SPM        &  0.366       & 0.293     \\
+        \rowcolor{lightgray}
+        {(BT)} & FSL vs. AFNI                &  0.439       & 0.352     \\
+        \rowcolor{lightgray}
+        {} & AFNI vs. SPM                    &  0.491       & 0.381     \\
+        {Within Tool} & FSL                  &  0.077       & 0.054     \\
+        {(WT)}   & SPM                       &  0.048       & 0.037     \\
+        {}   & AFNI                          &  0.108       & 0.131     \\
+        \bottomrule
+    \end{tabular}
+    \caption{Summary of voxel-wise mean and standard deviation in subject-level t-statistics in BT and WT. Values were averaged across 16 subjects.}
+    \label{table:unthresh-maps-subjects}
+\end{table}
 

### 2021-11-02 computs.py

@@ -643,20 +643,42 @@ def print_sl_stats(path_):
     # Compute Mean of std over subjects (ignore NaNs as bg)
     min_sbj = 100
     max_sbj = 0
+    all_wt_list = {}
+    all_bt_list = {}
     for i in range(1, 17):
         wt_list = []
         bt_list = []
-        for tool_ in ['fsl', 'spm', 'afni']:
-            wt_ = nib.load(os.path.join(path_, 'sbj{}-{}-unthresh-std.nii.gz'.format('%.2d' % i, tool_)))
-            wt_std_data = wt_.get_fdata()
-            wt_std_mean = np.nanmean(wt_std_data)
-            wt_list.append(wt_std_mean)
-
         for pair_ in ['fsl-spm', 'fsl-afni', 'afni-spm']:
             bt_ = nib.load(os.path.join(path_, 'sbj{}-{}-unthresh-std.nii.gz'.format('%.2d' % i, pair_)))
             bt_std_data = bt_.get_fdata()
             bt_std_mean = np.nanmean(bt_std_data)
             bt_list.append(bt_std_mean)
+            bt_std_std = np.nanstd(bt_std_data)
+            if pair_ in all_bt_list.keys():
+                tmp = all_bt_list[pair_]['mean']
+                all_bt_list[pair_]['mean'] = bt_std_mean + tmp
+                tmp = all_bt_list[pair_]['std']
+                all_bt_list[pair_]['std'] = bt_std_std + tmp
+            else:
+                all_bt_list[pair_] = {}
+                all_bt_list[pair_]['mean'] = bt_std_mean
+                all_bt_list[pair_]['std'] = bt_std_std
+
+        for tool_ in ['fsl', 'spm', 'afni']:
+            wt_ = nib.load(os.path.join(path_, 'sbj{}-{}-unthresh-std.nii.gz'.format('%.2d' % i, tool_)))
+            wt_std_data = wt_.get_fdata()
+            wt_std_mean = np.nanmean(wt_std_data)
+            wt_list.append(wt_std_mean)
+            wt_std_std = np.nanstd(wt_std_data)
+            if tool_ in all_wt_list.keys():
+                tmp = all_wt_list[tool_]['mean']
+                all_wt_list[tool_]['mean'] = wt_std_mean + tmp
+                tmp = all_wt_list[tool_]['std']
+                all_wt_list[tool_]['std'] = wt_std_std + tmp
+            else:
[…]

### 2021-11-08 paper/paper.tex
edits in methods, wip in results

@@
 \newcommand{\ali}[2]{\color{green}\textbf{Ali:} #1\color{black}\xspace}
+\newcommand{\discuss}[1]{\uwave{#1}}
 
@@
 We replicated the fMRI analysis described as study `ds000001'
-in~\cite{schonberg2012decreasing}, relying on the
-data publicly available in OpenNeuro at
-\url{https://openneuro.org/datasets/ds000001} and using the three main
-software packages for fMRI data processing, namely FMRIB Software Library
-(FSL)~\cite{jenkinson2012fsl}, Analysis of Functional NeuroImages
-(AFNI)~\cite{cox1996afni}, and Statistical Parametric
-Mapping(SPM)~\cite{penny2011statistical}. We selected this dataset because
-comparable analysis pipelines implemented in FSL, AFNI and SPM 
-were already published and extensively described in~\cite{bowring2019exploring}.
-Furthermore, the work in~\cite{bowring2019exploring} already evaluated the effect of tool variability for
-this dataset, which we intended to complement with the present quantification of numerical variability.
+in~\cite{schonberg2012decreasing}, relying on the data publicly available
+in OpenNeuro at \url{https://openneuro.org/datasets/ds000001} and using the
+three main software packages for fMRI data processing, namely FMRIB
+Software Library (FSL)~\cite{jenkinson2012fsl}, Analysis of Functional
+NeuroImages (AFNI)~\cite{cox1996afni}, and Statistical Parametric
+Mapping (SPM)~\cite{penny2011statistical}. We selected this dataset because
+comparable analysis pipelines implemented in FSL, AFNI and SPM were already 
+publicly available and extensively described in~\cite{bowring2019exploring}.
+Furthermore, the work in~\cite{bowring2019exploring} already evaluated the
+effect of tool variability for this dataset, which we intended to
+complement with the present quantification of numerical variability.
 
 In the selected study, 16 healthy adult subjects participated in the
-balloon analog risk task~\cite{lejuez2002evaluation} to measure
-risk-taking behavior over three scanning sessions~\cite{schonberg2012decreasing}.
-We reused the preprocessing, first-level, and
-second-level analyses implemented by~\cite{bowring2019exploring} consistently across all three software packages using 
-widely accepted analytical steps. Table~\ref{table:pipeline-steps} summarizes the analytical steps in each pipeline.
-More details are available in~\cite{bowring2019exploring}.
+balloon analog risk task~\cite{lejuez2002evaluation} to measure risk-taking
+behavior over three scanning sessions~\cite{schonberg2012decreasing}. We
+reused the preprocessing, first-level, and second-level analyses
+implemented by~\cite{bowring2019exploring} consistently across all three
+software packages. Table~\ref{table:pipeline-steps} summarizes the analytical steps in each
+pipeline. More details are available in~\cite{bowring2019exploring}.
 
@@
 
-\subsection{Fuzzy libmath environment}
+\subsection{Fuzzy Libmath environment}
 
-To introduce controlled amounts of numerical error in the analyses, we used the Fuzzy Libmath (FL) library~\cite{salari2021accurate}, an MCA-instrumented 
-version of the GNU mathematical library (libmath).
-FL works based on the MCA, a floating-point arithmetic that simulates roundoff and catastrophic cancellation errors
-by introducing a controlled amount of noise in the floating-point operations 
-through the following perturbation model~\cite{Parker1997-qq}:
+To introduce controlled amounts of numerical noise in the analyses, we used
+the Fuzzy Libmath library~\cite{salari2021accurate}, a version of the GNU
+mathematical library (libmath) instrumented with Monte-Carlo arithmetic.
+Monte-Carlo arithmetic simulates roundoff and catastrophic cancellation
+errors by introducing a controlled amount of noise in the floating-point
+operations through the following perturbation model~\cite{Parker1997-qq}:
 
@@
 where $e_x$ is the exponent in the floating-point representation of $x$,
-$t$ is the virtual precision, the number of bits in mantissa that will not be perturbed,
-and $\xi$ is a random uniform variable of $(-\frac{1}{2}, \frac{1}{2})$.
-The MCA perturbations are automated using Verificarlo tool~\cite{denis2015verificarlo} at compilation time.
+$t$ is the virtual precision --- the number of unperturbed bits in the
+mantissa of $x$ ---, and $\xi$ is a random uniform variable of
+$(-\frac{1}{2}, \frac{1}{2})$. The perturbation is introduced using 
+Verificarlo~\cite{denis2015verificarlo}, an LLVM compiler supporting Monte-Carlo 
+arithmetic and other types of numerical analyses.
 
-The instrumented functions are loaded in the pipeline using LD\_PRELOAD, a Linux environment variable
-to force load a shared library into an executable. This allows functions defined in FL to transparently
-overload the original ones without the need to modify or recompile the analysis pipeline.
+The instrumented libmath functions are loaded in the pipeline using
+LD\_PRELOAD, a Linux mechanism to force load a shared library into an
+executable. This allows functions defined in Fuzzy Libmath to transparently
+overload the original ones without the need to modify or recompile the
+analysis pipeline.
 
-FL only introduces perturbations in the output values of mathematical
-functions but not in their implementation. This is done by wrapping the original functions 
-and applying function \texttt{inexact} to their returned values.
-Listing~\ref{algo:wrapper} shows an example of this wrapping for the log function in both single and double precisions.
-In this script, the original functions are called by \texttt{dlsym},
-a function that returns the memory address of a symbol, in our case \texttt{RTLD\_NEXT}, the address of the next occurrence of the function.
-These wrappers are compiled with Verificarlo for each function. The MCA
-instrumentation is activated by adding a floating-point zero to the output
-of the original function so that this summation is instrumented.
-
-% \lstdefinestyle{customc}{
-%   belowcaptionskip=1\baselineskip,
-%   breaklines=true,
-%   frame=L,
-%   xleftmargin=\parindent,
-%   language=C,
-%   showstringspaces=false,
-%   basicstyle=\footnotesize\ttfamily,
-%   keywordstyle=\bfseries\color{green!40!black},
-%   commentstyle=\itshape\color{purple!40!black},
-%   identifierstyle=\color{blue},
-%   stringstyle=\color{orange},
-% }
+Fuzzy Libmath only introduces perturbations in the output values of
+mathematical functions but not in their input values or within their
+implementation. This is done by wrapping the original functions and
+applying function \texttt{inexact} to their returned values.
+Listing~\ref{algo:wrapper} shows an example of this wrapping for the
+\texttt{log} function in single and double precision. In this wrapper, the
+original function is called through \texttt{dlsym}, a function that returns
+the memory address of a symbol --- in our case \texttt{RTLD\_NEXT}, the
+address of the next occurrence of the function in memory. Function wrappers
+are compiled with Verificarlo. Verificarlo instruments the result of the
+addition between the original function output and a floating-point zero.
 
@@
 }
-\lstinputlisting[caption=Sample wrapper script, label=algo:wrapper, style=customasm]{wrapper.c}
-%\lstinputlisting[caption=Scheduler, style=customc]{../wrapper2.c}
+\lstinputlisting[caption=Sample wrapper function (C code), label=algo:wrapper, style=customasm]{wrapper.c}
 
-FL allows measuring the effect of numerical variability by running a program multiple times, 
-resulting in multiple independent realizations of the same analysis. Each of these samples 
-are equally plausible estimates of the true numerical result. 
-We used FL to simulate machine error, the relative error between a real number and its floating-point counterparts
-(e.g., $2^{-53}$ for IEEE-754 double precision).
-Moreover, FL allows simulating any virtual precision
-by controlling the magnitude of the injected error and
-thus to not be limited to the machine precision.
-
-The presented method does not require any
-particular software instrumentation in the data analysis code: it only
-assumes that executables are dynamically linked against GNU libc. For this purpose,
-(1) we captured the list of dynamic library dependencies using the \texttt{ldd} Linux utility for the software executables,
-(2) we traced the system library calls using \texttt{ltrace} Linux program while running the pipeline processes.
+\tristan{To be discussed with Ali, this paragraph explains what was done but not 
+the purpose or the result of it.}
+The presented method does not require any particular software
+instrumentation in the data analysis code: it only assumes that executables
+are dynamically linked against GNU libc. For this purpose, (1) we captured
+the list of dynamic library dependencies using the \texttt{ldd} Linux
+utility for the software executables, (2) we traced the system library
+calls using \texttt{ltrace} Linux program while running the pipeline
+processes.
 
@@
 
-To measure between-tool (BT) variability, we executed the pipelines described in~\cite{bowring2019exploring}
-with FSL version 5.0.10, AFNI version 18.1.09, and SPM12 version r7771
-executed with GNU/Octave version 5.2.
-All these software versions were identical to the original study except for SPM
-that we used Octave instead of MATLAB to enable mathematical function instrumentation using FL,
-while MATLAB uses its built-in functions and does not allow to apply FL.
-We also used a fixed number of 7 threads in AFNI executions,
-to reproduce similar results in~\cite{bowring2019exploring} in a feasible execution time.
-All the analyses were conducted on the same operating system, CentOS 7.3.
-The computations were performed on \href{https://www.computecanada.ca}{Compute Canada's} Béluga cluster nodes,
-each with 2× Intel Gold 6148 Skylake @ 2.4 GHz (40 cores/node) CPU and memory amount of 8 GB per core.
-We encapsulated the above-mentioned software packages in Docker container images with available Dockerfiles at \url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}.
+We measured between-tool (BT) variability by running the pipelines
+described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
+version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
+5.2. All these software versions were identical to the study
+in~\cite{bowring2019exploring} except for SPM for which we used Octave
+instead of MATLAB to enable mathematical function instrumentation using
+Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
+which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
+threads to 7 \discuss{to reproduce the results
+in~\cite{bowring2019exploring} in a feasible execution time}. All the
+analyses were conducted on the CentOS 7.3 operating system. The
+computations were performed on \href{https://www.computecanada.ca}{Compute
+Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake
+@ 2.4 GHz (40 cores/node) CPU and 8~GB of RAM per core. We encapsulated the
+above-mentioned software packages in Docker container images available at
+\url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}
+\tristan{Ali, could you put them in the paper repo unless there is a good
+reason to keep them separate?}.
 
-The same subjects and analyses were conducted in the same configurations
-with the FL environment, to measure within-tool (WT) variability. We
-applied instrumentations at the virtual precision t=53 bits for
-double-precision floating-point values and t=24 bits for single-precision
-values. Three Fuzzy samples were generated for each subject and tool, to
-match the number of tool samples.
-We also captured further instrumentations for FSL tool for the virtual precisions ranged from 53 bits to 1 bit by steps of 2,
-such that only double-precision was changed and single-precision was set to 24 bits for $t >= 24$ bits,
-and both double- and single-precision simultaneously were changed for $t < 24$ bits.
+We measured within-tool (WT) variability by running the same analyses three
+times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
+double-precision values and $t=24$~bits for single-precision values. These
+values were chosen such that the numerical perturbation simulates machine
+error, the relative error between a real number and its floating-point
+representation. The resulting samples are equally plausible estimates of
+the true numerical result. Moreover, we repeated the FSL analyses for virtual
+precisions ranging from $t=1$~bit to $t=24$~bits for single-precision
+and double-precision values. We also repeated the FSL analyses for virtual 
+precisions ranging from $t=24$~bits to $t=53$~bits for double-precision values, having 
+set the virtual precision to $t=24$~bits for single-precision values.
 
-We evaluated WT and BT variabilities in thresholded and unthresholded group-level and subject-level t-statistics maps.
-We computed voxel-wise standard deviations of t-statistic values for each pair of tools
-and then compared the standard deviations in both conditions.
-We computed the WT standard deviation as the square root of the summation of variances between samples in each tool:
+We evaluated WT and BT variability for thresholded as well as unthresholded
+group-level and subject-level t-statistics maps, by computing the
+standard deviation of t-statistic maps. For BT, we computed the standard deviation 
+across a given pair of tools.
+For WT, we computed the standard deviation across 
+Fuzzy Libmath samples of a given tool. Moreover, we computed WT for a pair of tools (A, B) as follows:
+\begin{equation}
+  \sigma_{WT(A,B)}^2 = \sigma_{WT(A)}^2 + \sigma_{WT(B)}^2,
+  \label{eq:wt-pair}
+\end{equation}
+where $WT(.)$ is the within-tool variability for a given tool.
 
-\begin{equation} \label{eq:mca_std}
-  \begin{multlined}
-  \sigma_{WT} = \sqrt{\sigma_{tool1}^2 + \sigma_{tool2}^2}
-%  VAR_{x} = \sum_{i=1}^{n} \frac{(x_i - \bar{x})}{n-1}
-  \end{multlined}
-\end{equation}
-
-Moreover, we determined region-by-region Dice coefficients for the thresholded maps for each pair of tools.
-We characterized 360 regions that correspond to the cortical parcellation atlas
-in Human Connectome Project Multi-Modal Parcellation version 1.0 (HCP-MMP1.0)~\cite{glasser2016multi}.
-Dice values in WT are computed as the average pair-wise Dices among three Fuzzy samples for each pair of tools.
-All Dice scores were normalized by the region sizes and remained in the range of 0 to 1.
+Further, from the thresholded maps, we determined regional Dice
+coefficients between activation clusters in the 360 regions in the Human
+Connectome Project Multi-Modal Parcellation atlas version 1.0
+(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, Dice coefficients were
+computed between activation maps produced by any pair of tools. For WT,
+Dice coefficients were computed pair-wise among the three Fuzzy samples of
+a given tool and averaged. All Dice coefficients were normalized by the
+region size \tristan{how?}.
 
 \section{Results}
-All scripts and data to create the figures presented in this section are available at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
+All scripts and data to reproduce the results are
+available at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
 
-We ensured a successful replication of the analyses initially presented in~\cite{bowring2019exploring}
-by comparing t-statistic group maps with results in the original study.
-We found identical checksums in the results of FSL.
-Also, we could replicate results with the same SPM version and MATLAB as in the original study with visually imperceptible differences.
-%Changes in the SPM version and replacing Octave with MATLAB resulted in visually small differences which were still hard to distinguish between them.
-For AFNI, the activation maps were similar overall; however, visual differences were noticeable.
-This might be caused by the hardware optimizations such as dynamic scheduling~\cite{demmel2013numerical}.
-We could confirm that AFNI results were passed the quality checks by visually assessing the registration results of each individual subject.
+\subsection{Sanity check}
 
-Summary statistics for the group-level unthresholded and thresholded t-statistics are reported in Table~\ref{table:pipeline-stats}.
-Overall, BT variability was larger than WT variability for both means and standard deviations.
-This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between $BT(A, B)$, and $WT(A)$ and $WT(B)$ for $A$ and $B$ in $[FSL, SPM, AFNI]$.
-We obtained statistically significant values between BT and WT variability with t-value $> 70$ and p-value $< 0.05$ in both thresholded and unthresholded maps.
+We verified the correctness of our analyses by comparing our unperturbed
+t-statistic group maps with the ones obtained
+in~\cite{bowring2019exploring}. For FSL, we found
+identical checksums. For SPM, the checksums were different but differences
+were visually imperceptible. For AFNI, the activation maps were similar
+overall, however, differences were more noticeable visually. 
+Overall, our results correctly reproduced
+the ones presented in~\cite{bowring2019exploring}. The observed
+differences were small and might be due to the use of Octave vs MATLAB in
+SPM, different operating systems \tristan{had you checked that?}, or
+different hardware. We performed visual quality control of the AFNI and SPM results
+for each individual subject.
+\tristan{add a figure to show the differences for SPM (Octave) and AFNI}
+
+\subsection{Summary group-level statistics}
+
+Summary statistics for the group-level unthresholded and thresholded
+t-statistics are reported in Table~\ref{table:pipeline-stats}.
+\tristan{From here this paragraph needs a full re-write} Overall, BT
+variability was larger than WT variability for both means and standard
+deviations \tristan{I don't think it's the case for stdev}. This was
+confirmed by computing the T-test and Wilcoxon signed-rank statistics
+between $BT(A, B)$, and $WT(A)$ and $WT(B)$ for $A$ and $B$ in $[FSL, SPM,
+AFNI]$. We obtained statistically significant values between BT and WT
+variability with t-value $> 70$ and p-value $< 0.05$ in both thresholded
+and unthresholded maps.
 
@@
     \end{tabular}
-    \caption{Summary of voxel-wise mean and standard deviation in group-level t-statistics in BT and WT.}
+    \caption{Summary of voxel-wise mean and standard deviation in
+    group-level t-statistics in BT and WT \tristan{The caption doesn't
+    reflect what I thought this table represented, this needs
+    discussion. Also in Table III.}.}
     \label{table:pipeline-stats}
 \end{table}
-
-% \subsection{Comparing disparity in BT and WT}
-%\subsection{Spatial localization of disparity in BT and WT}
-\subsection{Group-level thresholded maps}
-
-%Fig 1
-Comparisons of standard deviations between thresholded images in WT and BT
-on MNI space are shown in Figure~\ref{fig:thresh-maps}.
-While we observed substantial BT variations with the average standard deviation 1.43,
-the magnitude of WT variations was much smaller with the average standard deviation 0.34,
-as was anticipated. 
-Moreover, the magnitude of WT variations reached the magnitued of BT variations
-in some regions, shown in white in Figure~\ref{fig:thresh-maps}-\textbf{C}.
-
-% Fig2
-Figure~\ref{fig:dice-thresh} compares regional normalized Dice coefficients of
-activated voxels, showing a linear correlation between BT and WT with p-value $< 0.05$ in all three pairs.
-
-%%%%%%%%%% Var. of Thresh %%%%%%%%
-\begin{figure*}[ht]
-    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-      \centering
-      \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \caption{Thresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}). }
-    % so that bright blue areas indicate more similar order of magnitude of variations in both conditions,
-    %and vise versa for the darkder regions.}
-    \label{fig:thresh-maps}
-    \end{minipage}}
-  \end{figure*}
-
-  %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
-  \begin{figure}[ht]
-    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
-    \centering
-    \includegraphics[width=\columnwidth]{figures/dices_corr.png}
-    \caption{Normalized, regional Dice coefficients of activated voxels for
-    BT and WT using the HCP-MMP1.0 parcellation of
-    ~\cite{glasser2016multi}.}
-    \label{fig:dice-thresh}
-    \end{minipage}}
-  \end{figure}
 
@@
 
-% Fig3
-Similar conclusions are drawn from the unthresholded t-statistics maps
-(Figure~\ref{fig:unthresh-maps}). BT variability is larger than WT variability overall, however,
-BT and WT variability are comparable in some regions.
+Figure~\ref{fig:unthresh-maps} compares t-statistics standard deviation maps
+across different pipelines (BT variability) and across Fuzzy Libmath
+samples (WT variability). While WT variability remains lower than BT
+variability overall, it approaches it in some regions, shown in white in
+Figure~\ref{fig:unthresh-maps}-\textbf{C}.
+
+Interestingly, a group of voxels \tristan{...}
+BT and WT variability appear correlated in some regions
+(Figure~\ref{fig:unthresh-correlation}).
 
@@
   \end{figure*}
-
-% Fig4
-Figure~\ref{fig:unthresh-correlation} highlights the voxel-wise standard deviations in WT and BT variability
-with the identity lines that indicate voxels with the standard deviation of $BT = WT$.
-The identity area is represented on MNI space in the second row in Figure~\ref{fig:unthresh-correlation}
-for the voxels with the magnitude of standard deviation $> 0.1$ and the satndard deviation ratio of $0.5 < BT/WT < 2$.
-The maps show the spatial localization of parts of the brain where the numerical variability simulated BT variability.
-This refines the presented results in Figure~\ref{fig:unthresh-maps}-\textbf{C},
-indicated voxels with similar magnitude of BT and WT variations were uniformly distributed across the brain.
 
@@
       \caption{
-        Scatter plots of unthresholded group t-statistics standard deviations computed between tools and within tools.
-        The identity line distinguishes voxels where the standard deviation BT is equal to WT.
-        Voxels with the standard deviation ratio of BT/WT in the interval (0.5, 2) are represented on brain maps in the second row.}
+        Voxel-wise comparison of BT and WT variabilty. The bottom row represents 
+        voxels where the BT/WT ration is in (0.5, 2).}
     \label{fig:unthresh-correlation}
@@
 
-  Summary statistics for the subject-level unthresholded t-statistics are reported in Table~\ref{table:unthresh-maps-subjects}.
-  Overall, results represent similar findings with group-level t-statistics between WT and BT variations.
+  Summary statistics for subject-level unthresholded t-statistics maps are
+  reported in Table~\ref{table:unthresh-maps-subjects}. Overall, results
+  represent similar findings with group-level t-statistics between WT and
+  BT variations.
 
@@
 
+  \subsection{Group-level thresholded maps}
+
+  Similar conclusions are drawn from the unthresholded t-statistics maps
+  (Figure~\ref{fig:thresh-maps}).  Figure~\ref{fig:dice-thresh} compares regional normalized Dice coefficients of
+  activated voxels, showing a linear correlation between BT and WT with
+  p-value $< 0.05$ in all three pairs.
+
+  %%%%%%%%%% Var. of Thresh %%%%%%%%
+  \begin{figure*}[ht]
+      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+        \centering
+        \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
+      \caption{Thresholded group t-statistics standard deviation maps
+      computed across tools (\textbf{A}) and Fuzzy Libmath samples
+      (\textbf{B}) as defined in Eq~\ref{eq:wt-pair}. \tristan{Change the column headers to (FSL, SPM) instead of FSL - SPM (everywhere).}}
+      \label{fig:thresh-maps}
+      \end{minipage}}
+    \end{figure*}
+
+    % %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
+    \begin{figure*}[ht]
+      \centering
+      \includegraphics[width=\textwidth]{figures/dices_corr.png}
+      \caption{Normalized regional Dice coefficients of activated voxels for
+      BT and WT using the HCP-MMP1.0 parcellation of
+      ~\cite{glasser2016multi}.}
+      \label{fig:dice-thresh}
+    \end{figure*}
+
 \section{Discussion}
@@
 
-Given that FL only perturbs basic mathematical functions, we expect more numerical variability by perturbing linear algebra,
+Given that Fuzzy Libmath only perturbs basic mathematical functions, we expect more numerical variability by perturbing linear algebra,
 in particular for non-scalar types like vectors or matrices. For the future study, this can be evaluated using MCA-instrumented versions
@@
 For an fMRI analysis, we measured a significant variability in both conditions, which was comparable for some brain regions.
-We showed the FL library as a valuable model based on MCA method for simulating the numerical variability.
+We showed the Fuzzy Libmath library as a valuable model based on MCA method for simulating the numerical variability.
 Moreover, we can leverage the MCA-instrumented libraries for simulating the numerical uncertainty in different studies.

### 2021-11-09 paper/paper.tex
edits in method

@@
 
-\tristan{To be discussed with Ali, this paragraph explains what was done but not 
-the purpose or the result of it.}
-The presented method does not require any particular software
-instrumentation in the data analysis code: it only assumes that executables
-are dynamically linked against GNU libc. For this purpose, (1) we captured
-the list of dynamic library dependencies using the \texttt{ldd} Linux
-utility for the software executables, (2) we traced the system library
-calls using \texttt{ltrace} Linux program while running the pipeline
-processes.
+\tristan{
+Explain how the instrumentation was validated:
+\begin{enumerate}
+\item Verify that two consecutive IEEE executions are identical (no random effects)
+\item Verify that all pipelines use libm
+\item List all the dependencies of all the pipelines using ldd 
+\item Verify that no math function is implemented in these dependencies
+\item Verify that fuzzy libmat has an effect on the results
+\end{enumerate}
+}
 
@@
 a given tool and averaged. All Dice coefficients were normalized by the
-region size \tristan{how?}.
+region size \tristan{explain how you did this: x = (dice x region size) ; x = (x-xmin)/(xmax-xmin)}.
 
@@
         Voxel-wise comparison of BT and WT variabilty. The bottom row represents 
-        voxels where the BT/WT ration is in (0.5, 2).}
+        voxels where the BT/WT ratio is in (0.5, 2).}
     \label{fig:unthresh-correlation}

### 2021-11-10 computs.py
wip dice analysis

@@ -10,7 +10,6 @@ import matplotlib.pyplot as plt
 import pickle as pkl
 import inspect
 from nilearn.image import math_img
-from lib import dice
 from statistics import mean
 import scipy.stats as stat
 from scipy.signal import resample
@@ -582,39 +581,39 @@ def plot_dices(dices_):
                 r_sizes.append(s)
                 r_name.append(l_[i])
     
-            # Plot Normalize dice values by region size
-            tool_norm = np.array(tool_list)*np.array(r_sizes)
-            mca_norm = np.array(mca_list)*np.array(r_sizes)
-            # Normalization between [0-1] = x -xmin/ xmax – xmin
-            tool_norm = (tool_norm - np.min(tool_norm)) / (np.max(tool_norm) - np.min(tool_norm))
-            mca_norm = (mca_norm - np.min(mca_norm)) / (np.max(mca_norm) - np.min(mca_norm))
+            # Plot Dice values by region size
+            tool_dice = np.array(tool_list)
+            mca_dice = np.array(mca_list)
+            tool_dice_nonz = [ tool_dice[i] for i in range(len(tool_dice)) if tool_dice[i] != 0 and mca_dice[i] != 0]
+            mca_dice_nonz = [ mca_dice[i] for i in range(len(tool_dice)) if tool_dice[i] != 0 and mca_dice[i] != 0]
+            sizes_nonz = [ r_sizes[i] for i in range(len(tool_dice)) if tool_dice[i] != 0 and mca_dice[i] != 0]
+            tools_nonz = [ tool_list[i] for i in range(len(tool_dice)) if tool_dice[i] != 0 and mca_dice[i] != 0]
+            tool_dice = tool_dice_nonz
+            mca_dice = mca_dice_nonz
+            print(len(tool_dice), len(mca_dice))
 
-            # regions that BT=0 and WT>0.93
-            x = np.where((tool_norm == 0) & (mca_norm > 0.93) , r_name, None)
-            res = [i for i in x if i]
-            print("BT only var regions in {}:\n{}".format(tool_, res))
-                
-            # Compute regression line without zero values
-            nonz_tool_norm = []
-            nonz_mca_norm = []
-            for i in range(len(tool_norm)):
-                if tool_norm[i] != 0  and mca_norm[i] != 0:
-                    nonz_tool_norm.append(tool_norm[i])
[…]

### 2021-11-11 paper/paper.tex
revises in method

@@
 
-\tristan{
-Explain how the instrumentation was validated:
-\begin{enumerate}
-\item Verify that two consecutive IEEE executions are identical (no random effects)
-\item Verify that all pipelines use libm
-\item List all the dependencies of all the pipelines using ldd 
-\item Verify that no math function is implemented in these dependencies
-\item Verify that fuzzy libmat has an effect on the results
-\end{enumerate}
-}
+To validate instrumentations, we verified that two consecutive IEEE executions are identical;
+there are no randomness effects in all pipelines.
+We also listed all the pipeline library dependencies using the ldd Linux utility.
+We ensured that (1) all pipelines are dynamically linked to the libmath library
+(2) there is no alternative implementation for the basic mathematical functions in these dependencies.
+Finally, we verified that Fuzzy libmath affects computational results.
 
@@
 above-mentioned software packages in Docker container images available at
-\url{https://github.com/ali4006/fuzzy-neurotools/tree/main/dockerfile}
-\tristan{Ali, could you put them in the paper repo unless there is a good
-reason to keep them separate?}.
+\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
 

### 2021-11-12 paper/paper.tex
Comment on threads

--- 2021-11-09 paper/paper.tex
@@
 which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
-threads to 7 \discuss{to reproduce the results
-in~\cite{bowring2019exploring} in a feasible execution time}. All the
-analyses were conducted on the CentOS 7.3 operating system. The
+threads to 7 even though AFNI executions
+in~\cite{bowring2019exploring} were single-threaded. This was meant to
+reduce the time overhead resulting from Fuzzy Libmath instrumentation. All
+the analyses were conducted on the CentOS 7.3 operating system. The
 computations were performed on \href{https://www.computecanada.ca}{Compute

### 2021-11-26 paper/paper.tex
Update result section

@@
 
-Further, from the thresholded maps, we determined regional Dice
-coefficients between activation clusters in the 360 regions in the Human
+Further, from the thresholded maps, we determined regional instability 
+between activation clusters in the 360 regions in the Human
 Connectome Project Multi-Modal Parcellation atlas version 1.0
-(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, Dice coefficients were
-computed between activation maps produced by any pair of tools. For WT,
-Dice coefficients were computed pair-wise among the three Fuzzy samples of
-a given tool and averaged. All Dice coefficients were normalized by the
-region size \tristan{explain how you did this: x = (dice x region size) ; x = (x-xmin)/(xmax-xmin)}.
+(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, a region was unstable if it had different activation behavior between pair of tools.
+For WT, we considered a region unstable if it had a blinking activation between Fuzzy samples of a given tool.
 
@@
 differences were small and might be due to the use of Octave vs MATLAB in
-SPM, different operating systems \tristan{had you checked that?}, or
-different hardware. We performed visual quality control of the AFNI and SPM results
+SPM or different hardware. We performed visual quality control of the AFNI and SPM results
 for each individual subject.
@@
 t-statistics are reported in Table~\ref{table:pipeline-stats}.
-\tristan{From here this paragraph needs a full re-write} Overall, BT
-variability was larger than WT variability for both means and standard
-deviations \tristan{I don't think it's the case for stdev}. This was
-confirmed by computing the T-test and Wilcoxon signed-rank statistics
-between $BT(A, B)$, and $WT(A)$ and $WT(B)$ for $A$ and $B$ in $[FSL, SPM,
-AFNI]$. We obtained statistically significant values between BT and WT
-variability with t-value $> 70$ and p-value $< 0.05$ in both thresholded
-and unthresholded maps.
+Overall, BT variability was larger than WT variability in both thresholded and unthresholded maps.
+This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between BT and WT as:
+
+\begin{equation*}
+  \left\{
+    \begin{aligned}
+      & BT(a, b), WT(a),\\
+      & BT(a, b), WT(b)
+    \end{aligned}  
+    \quad  a,b \in [FSL, SPM, AFNI] \;
+  \right\}
+  \label{eq:t-tests}
+\end{equation*}
+
+We obtained statistically significant values between BT and WT
+variability with t-value $> 70$ and p-value $< 0.05$.
 
@@
     \end{tabular}
-    \caption{Summary of voxel-wise mean and standard deviation in
-    group-level t-statistics in BT and WT \tristan{The caption doesn't
-    reflect what I thought this table represented, this needs
-    discussion. Also in Table III.}.}
+    \caption{Summary statistics of voxel-wise standard deviations
+    in group-level t-statistics in BT and WT.}
     \label{table:pipeline-stats}
@@
     \end{tabular} 
-    \caption{Summary of voxel-wise mean and standard deviation in subject-level t-statistics in BT and WT. Values were averaged across 16 subjects.}
+    \caption{Summary statistics of voxel-wise standard deviations in subject-level t-statistics in BT and WT.
+    The voxel-wise standard deviations were averaged across 16 subjects.}
     \label{table:unthresh-maps-subjects}
@@
   Similar conclusions are drawn from the unthresholded t-statistics maps
-  (Figure~\ref{fig:thresh-maps}).  Figure~\ref{fig:dice-thresh} compares regional normalized Dice coefficients of
-  activated voxels, showing a linear correlation between BT and WT with
-  p-value $< 0.05$ in all three pairs.
+  (Figure~\ref{fig:thresh-maps}).
+  Figure~\ref{fig:cm-thresh} compares instability of regional activations,
+  showing that most of the regions have a similar activation pattern in both BT and WT, mostly are stable.
+  However, some regions have a different activation behavior, mainly unstable in BT and stable in WT.
+  % showing more severity of BT instability than WT.
 
@@
       computed across tools (\textbf{A}) and Fuzzy Libmath samples
-      (\textbf{B}) as defined in Eq~\ref{eq:wt-pair}. \tristan{Change the column headers to (FSL, SPM) instead of FSL - SPM (everywhere).}}
+      (\textbf{B}) as defined in Eq~\ref{eq:wt-pair}.}
       \label{fig:thresh-maps}
@@
       \centering
-      \includegraphics[width=\textwidth]{figures/dices_corr.png}
-      \caption{Normalized regional Dice coefficients of activated voxels for
-      BT and WT using the HCP-MMP1.0 parcellation of
-      ~\cite{glasser2016multi}.}
-      \label{fig:dice-thresh}
+      \includegraphics[width=\textwidth]{figures/dice_analysis-plot.png}
+      \caption{Heatmap of confusion matrices for instability of regional activations
+      in BT and WT using the HCP-MMP1.0 parcellation of ~\cite{glasser2016multi}. 
+      A region is unstable (=1) if it has different activation behavior in both tools
+      for BT or different fuzzy samples in each tool for WT; otherwise, it is stable (=0).}
+      \label{fig:cm-thresh}
     \end{figure*}

### 2021-12-01 paper/paper.tex
Edits in methods and results, rewrote discussion.

@@
 
+\tristan{We investigate two questions: (1) how do numerical and between-tool variability compare? (2) are they correlated?}
+
 In this work, we reproduce an fMRI analysis in~\cite{bowring2019exploring} with different neuroimaging software packages in the presence of the Fuzzy environment,
@@
 in~\cite{schonberg2012decreasing}, relying on the data publicly available
-in OpenNeuro at \url{https://openneuro.org/datasets/ds000001} and using the
-three main software packages for fMRI data processing, namely FMRIB
+in OpenNeuro at \url{https://openneuro.org/datasets/ds000001} and using
+three widely-used software packages for fMRI data processing, namely FMRIB
 Software Library (FSL)~\cite{jenkinson2012fsl}, Analysis of Functional
@@
 software packages. Table~\ref{table:pipeline-steps} summarizes the analytical steps in each
-pipeline. More details are available in~\cite{bowring2019exploring}.
+pipeline.
 
@@
 
-To introduce controlled amounts of numerical noise in the analyses, we used
+To introduce numerical noise in the analyses, we used
 the Fuzzy Libmath library~\cite{salari2021accurate}, a version of the GNU
@@
 errors by introducing a controlled amount of noise in the floating-point
-operations through the following perturbation model~\cite{Parker1997-qq}:
+operations through the following perturbation~\cite{Parker1997-qq}:
 
 \begin{equation} \label{eq:mca_inexact}
-  inexact(x) = x + 2^{e_x-t}\xi
+  inexact(x) = x + 2^{e_x-t}\xi,
 \end{equation}
+where $e_x$ is the exponent in the floating-point representation of $x$,
+$t$ is the virtual precision (the number of unperturbed bits in the
+mantissa of $x$), and $\xi$ is a random uniform variable of
+$(-\frac{1}{2}, \frac{1}{2})$. We introduced the perturbation using 
+Verificarlo~\cite{denis2015verificarlo}, an LLVM compiler supporting Monte-Carlo 
+arithmetic and other types of numerical instrumentations.
 
-where $e_x$ is the exponent in the floating-point representation of $x$,
-$t$ is the virtual precision --- the number of unperturbed bits in the
-mantissa of $x$ ---, and $\xi$ is a random uniform variable of
-$(-\frac{1}{2}, \frac{1}{2})$. The perturbation is introduced using 
-Verificarlo~\cite{denis2015verificarlo}, an LLVM compiler supporting Monte-Carlo 
-arithmetic and other types of numerical analyses.
-
-The instrumented libmath functions are loaded in the pipeline using
-LD\_PRELOAD, a Linux mechanism to force load a shared library into an
-executable. This allows functions defined in Fuzzy Libmath to transparently
+We loaded the instrumented libmath functions in the pipeline using
+LD\_PRELOAD, a Linux mechanism to force-load a shared library into an
+executable. This mechanism allows functions defined in Fuzzy Libmath to transparently
 overload the original ones without the need to modify or recompile the
@@
 
-Fuzzy Libmath only introduces perturbations in the output values of
+Fuzzy Libmath introduces numerical perturbations in the values returned by
 mathematical functions but not in their input values or within their
@@
 
-To validate instrumentations, we verified that two consecutive IEEE executions are identical;
-there are no randomness effects in all pipelines.
-We also listed all the pipeline library dependencies using the ldd Linux utility.
-We ensured that (1) all pipelines are dynamically linked to the libmath library
-(2) there is no alternative implementation for the basic mathematical functions in these dependencies.
-Finally, we verified that Fuzzy libmath affects computational results.
+To validate our instrumentations, we first verified that non-instrumented
+executions of the same pipeline on the same dataset led to identical
+results \tristan{did you fix random seeds and if so in which pipelines?}. We also listed the pipeline
+library dependencies using the \texttt{ldd} Linux utility and verified that
+(1) the tested pipelines were dynamically linked to the GNU libmath library, and 
+(2) there was no alternative implementation of elementary mathematical functions in the pipeline dependencies.
+Finally, we verified that the use of Fuzzy libmath affected computational results.
 
@@
 version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
-5.2. All these software versions were identical to the study
-in~\cite{bowring2019exploring} except for SPM for which we used Octave
+5.2. These software versions were identical to the study
+in~\cite{bowring2019exploring} except for SPM for which we used GNU/Octave
 instead of MATLAB to enable mathematical function instrumentation using
@@
 values were chosen such that the numerical perturbation simulates machine
-error, the relative error between a real number and its floating-point
-representation. The resulting samples are equally plausible estimates of
-the true numerical result. Moreover, we repeated the FSL analyses for virtual
+error, the minimal distance between two consecutive floating-point numbers. The resulting samples are equally plausible estimates of
+the true numerical result. Moreover, to evaluate numerical perturbations at different magnitudes, 
+we repeated the FSL analyses for virtual
 precisions ranging from $t=1$~bit to $t=24$~bits for single-precision
@@
 group-level and subject-level t-statistics maps, by computing the
-standard deviation of t-statistic maps. For BT, we computed the standard deviation 
+standard deviation of t-statistic maps across pipelines (BT) or Fuzzy Libmath samples (WT). For BT, we computed the standard deviation 
 across a given pair of tools.
-For WT, we computed the standard deviation across 
-Fuzzy Libmath samples of a given tool. Moreover, we computed WT for a pair of tools (A, B) as follows:
+For WT, we computed the standard deviation across the 3 
+Fuzzy Libmath samples of a given tool. Moreover, we computed WT variability for a pair of tools (A, B) as follows:
 \begin{equation}
@@
 \end{equation}
-where $WT(.)$ is the within-tool variability for a given tool.
+where $\sigma_{WT(.)}$ is the within-tool variability for a given tool.
 
 Further, from the thresholded maps, we determined regional instability
-between activation clusters in the 360 regions in the Human
-Connectome Project Multi-Modal Parcellation atlas version 1.0
-(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, a region was unstable if it had different activation behavior between pair of tools.
-For WT, we considered a region unstable if it had a blinking activation between Fuzzy samples of a given tool.
+between activation clusters in the 360 regions in the Human Connectome
+Project Multi-Modal Parcellation atlas version 1.0
+(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, we considered a region
+unstable for a pair of tools if it contained activated voxels for a tool
+but not for the other one. For WT, we considered a region unstable for a
+pair of tools (A, B) if for tool A or tool B it contained activated voxels only for some Fuzzy Libmath
+samples.
 
@@
 identical checksums. For SPM, the checksums were different but differences
-were visually imperceptible. For AFNI, the activation maps were similar
+were visually unnoticeable. For AFNI, the activation maps were similar
 overall, however, differences were more noticeable visually. 
-Overall, our results correctly reproduced
-the ones presented in~\cite{bowring2019exploring}. The observed
-differences were small and might be due to the use of Octave vs MATLAB in
-SPM or different hardware. We performed visual quality control of the AFNI and SPM results
-for each individual subject.
+The observed
+differences remained small and might be due to the use of Octave vs MATLAB in
+SPM. We performed visual quality control of the AFNI and SPM results
+for each individual subject \tristan{and confirmed that ...}.
 \tristan{add a figure to show the differences for SPM (Octave) and AFNI}
@@
 Summary statistics for the group-level unthresholded and thresholded
-t-statistics are reported in Table~\ref{table:pipeline-stats}.
-Overall, BT variability was larger than WT variability in both thresholded and unthresholded maps.
-This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between BT and WT as:
+t-statistics are reported in Table~\ref{table:pipeline-stats}. BT
+variability for tool pair (A, B) was larger than WT variability for tool A and tool B for any tool pair, in both thresholded and
+unthresholded maps (Wilcoxon signed-rank test, t-test
+p~\textless~$10^{-163}$ for all tests).
+% This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between BT and WT as:
 
-\begin{equation*}
-  \left\{
-    \begin{aligned}
-      & BT(a, b), WT(a),\\
-      & BT(a, b), WT(b)
-    \end{aligned}  
-    \quad  a,b \in [FSL, SPM, AFNI] \;
-  \right\}
-  \label{eq:t-tests}
-\end{equation*}
+% \begin{equation*}
+%   \left\{
+%     \begin{aligned}
+%       & BT(a, b), WT(a),\\
+%       & BT(a, b), WT(b)
+%     \end{aligned}  
+%     \quad  a,b \in [FSL, SPM, AFNI] \;
+%   \right\}
+%   \label{eq:t-tests}
+% \end{equation*}
 
-We obtained statistically significant values between BT and WT
-variability with t-value $> 70$ and p-value $< 0.05$.
+% We obtained statistically significant values between BT and WT
+% variability with t-value $> 70$ and p-value $< 0.05$.
 
@@
     \end{tabular}
-    \caption{Summary statistics of voxel-wise standard deviations
-    in group-level t-statistics in BT and WT.}
+    \caption{Voxel-wise mean and standard deviation of BT and WT variability
+    in group-level t-statistics maps.}
     \label{table:pipeline-stats}
@@
 
-Figure~\ref{fig:unthresh-maps} compares t-statistics standard deviation maps
-across different pipelines (BT variability) and across Fuzzy Libmath
-samples (WT variability). While WT variability remains lower than BT
-variability overall, it approaches it in some regions, shown in white in
-Figure~\ref{fig:unthresh-maps}-\textbf{C}.
-
-Interestingly, a group of voxels \tristan{...}
-BT and WT variability appear correlated in some regions
-(Figure~\ref{fig:unthresh-correlation}).
+Figure~\ref{fig:unthresh-maps} compares BT and WT variability in
+unthresholded maps. WT variability remains lower than BT variability
+overall. Interestingly, BT and WT variability appear correlated in a subset
+of voxels scattered across the brain
+(Figure~\ref{fig:unthresh-correlation}), but the reason for this apparent
+correlation remains unknown.
 
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).}
+    \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).}
     \label{fig:unthresh-maps}
@@
       \caption{
-        Voxel-wise comparison of BT and WT variabilty. The bottom row represents 
+        Voxel-wise comparison of BT and WT variabilty. The bottom row shows 
         voxels where the BT/WT ratio is in (0.5, 2).}
@@
   Summary statistics for subject-level unthresholded t-statistics maps are
-  reported in Table~\ref{table:unthresh-maps-subjects}. Overall, results
-  represent similar findings with group-level t-statistics between WT and
-  BT variations.
+  reported in Table~\ref{table:unthresh-maps-subjects}. As for group-level
+  maps, BT variability was consistently larger than WT variability
+  \tristan{report statistical tests}.
 
-  Figure~\ref{fig:unthresh-maps-sbj} shows BT and WT variability of the
-  unthresholded t-statistics for the subject with the highest WT
-  variability among the 16 subjects.
-  For this particular subject, we observed substantial WT variations with the average standard deviation 0.099 compared to 
-  the average standard deviation 0.466 for BT variations.
-  As can be seen in the Figure, WT variability approaches and even surpasses BT variability in some regions.
-  This subject also revealed that WT variability mainly concentrated in some regions  
-  contrary to the corresponding variability from unthresholded group-level t-statistics which was uniformly distributed across the brain.
+  Figure~\ref{fig:unthresh-maps-sbj} shows BT and WT variability for
+  the subject with the highest WT variability among the 16 subjects. For
+  this particular subject, WT variability approaches and even surpasses BT
+  variability in some regions. This subject also revealed that WT
+  variability mainly concentrated in some regions.
 
@@
     \end{tabular} 
-    \caption{Summary statistics of voxel-wise standard deviations in subject-level t-statistics in BT and WT.
-    The voxel-wise standard deviations were averaged across 16 subjects.}
+    \caption{Voxel-wise mean and standard deviation of BT and WT variability
+    in subject-level t-statistics maps (averages on 16 subjects).}
     \label{table:unthresh-maps-subjects}
@@
     %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \caption{Unthresholded subject t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
-    This is for the subject with the highest WT variability.}
+    \caption{For subject with highest WT variability, unthresholded subject-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).}
   \label{fig:unthresh-maps-sbj}
@@
 
-\subsection{WT variability across virtual precisions}
+\subsection{Group-level untresholded maps at different virtual precisions}
 
-While the previous results were obtained at the virtual precision of 53~bits for double-precision floating-point values
-and 24~bits for single-precision values, we evaluated WT variability across different virtual precisions for FSL.
-Figure~\ref{fig:across-precisions} represents the root-mean-square error (RMSE) between the standard deviations per voxel
-in BT and WT resulted from the Fuzzy FSL,
-substantiating that how variabilities in both conditions are close to each other across different virtual precisions.
-
-We determined the virtual precision of t=17 bits as the precision that minimized the RMSE between BT and WT on average.
-This is the precision that numerical perturbations in FSL more closely simulated BT variability.
-The brain maps of standard deviations between BT and WT obtained from the Fuzzy FSL at t=17 bits (Figure~\ref{fig:gnp-mni})
-show significant WT variability, particularly for some regions in the frontal, parietal, and limbic lobes, close to BT variability.
+While the previous results were obtained at the virtual precision of 53~bits for double-precision values
+and 24~bits for single-precision values, we also evaluated WT variability across different virtual precisions for FSL.
+Figure~\ref{fig:across-precisions} shows the root-mean-square error (RMSE) between BT and WT variability maps.
+The virtual precision of t=17 bits minimized the RMSE between BT and WT.
+Figure~\ref{fig:gnp-mni} shows the corresponding BT and WT maps obtained at t=17 bits, showing 
+that BT and WT reach comparable magnitudes in some regions.
 
@@
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions. WT is computed from three samples of FSL tool.}
+      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions. \tristan{Remove (std) from y label}}
     \label{fig:across-precisions}
@@
         \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
-        WT is computed from three samples of FSL tool at the virtual precision of t=17 bits.}
+        WT is computed at the virtual precision of t=17 bits. \tristan{remove (AFNI,SPM)}}
     \label{fig:gnp-mni}
@@
 
-  Similar conclusions are drawn from the unthresholded t-statistics maps
-  (Figure~\ref{fig:thresh-maps}).
-  Figure~\ref{fig:cm-thresh} compares instability of regional activations,
-  showing that most of the regions have a similar activation pattern in both BT and WT, mostly are stable.
-  However, some regions have a different activation behavior, mainly unstable in BT and stable in WT.
-  % showing more severity of BT instability than WT.
+  Figure~\ref{fig:thresh-maps} compares BT and WT for thresholded group-level maps.
+  While BT is consistently larger than WT, thresholding is an unstable operation 
+  that results in comparable magnitudes for BT and WT within activation clusters where BT variability is low.
+
+  Figure~\ref{fig:cm-thresh} compares regional activation instability for BT and WT. The average ratio
+  of unstable regions was 26\% for BT and 9.2\% for WT. Moreover, the average F1 score was 0.28. Therefore, regional 
+  WT instability does not appear to be a 
+  good predictor of BT instability.
 
@@
       computed across tools (\textbf{A}) and Fuzzy Libmath samples
-      (\textbf{B}) as defined in Eq~\ref{eq:wt-pair}.}
+      (\textbf{B}).}
       \label{fig:thresh-maps}
@@
     \begin{figure*}[ht]
+      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
       \centering
       \includegraphics[width=\textwidth]{figures/dice_analysis-plot.png}
-      \caption{Heatmap of confusion matrices for instability of regional activations
-      in BT and WT using the HCP-MMP1.0 parcellation of ~\cite{glasser2016multi}. 
-      A region is unstable (=1) if it has different activation behavior in both tools
-      for BT or different fuzzy samples in each tool for WT; otherwise, it is stable (=0).}
+      \caption{Confusion matrices of activation instability
+      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation. \tristan{plot a single color map for 3 heatmaps}}
       \label{fig:cm-thresh}
+    \end{minipage}}
     \end{figure*}
@@
 
-We represented differences in the results of an fMRI analysis between numerical variability
-and the variability arisen from software package variations.
-Although BT variability was larger than WT variability on average,
-we demonstrated regions in the brain maps that numerical perturbations could simulate BT variability.
-The correlation of these variabilities suggests that numerical perturbations can be used to evaluate the robustness of the analyses
-to inter-software disparities.
+In fMRI \emph{group analyses}, machine error remains an order of magnitude
+smaller than between-tool variability. Group analyses have a regularization
+effect toward numerical noise, which is expected to amplify as sample size
+increases. Therefore, for fMRI studies with large sample sizes, machine
+error can safely be neglected with respect to between-tool variability. The
+recommendation made in~\cite{botvinik2020variability} to rely on ``multiverse" analyses where
+multiple analysis tools are compared is therefore likely to successfully correct
+for machine error in group studies.
 
-While switching between \fslspm was generated the least BT and WT variabilities consistently, the most level of these variabilities was identified
-between \fslafni and \afnispm. %We also found AFNI as the most sensitive tool to numerical perturbations.
-These results do not indicate which software package is better or worse since there is no ground-truth model for the analyses.
-However, this study revealed the importance of numerical instability in the selected tools for doing fMRI analyses.
-It provided a view of related numerical variability of which should be taken into consideration by the software developers.
+However, machine error remains important in group analyses that are based
+on a single tool, as is commonly the case in current fMRI studies. In
+particular, in our study, the inherent instability of thresholding was
+triggered by machine error in 9\% of 360 brain regions, which indicates
+that machine error might have impacted neuroscientific conclusions related
+to these regions.
 
-We found that numerical instability in individual analyses was attenuated in group analyses
-since we obtained substantially higher variability in t-statistics at the level of subjects.
-This is consistent with the findings in~\cite{bowring2021isolating} in which identified the first-level signal model as the largest
-source of variability across the three tools for this study.
-This is an issue for the development of fMRI biomarkers.
-As a solution, we can aggregate the results obtained from numerical perturbations to improve biomarkers,
-as suggested in~\cite{kiar2020numerical} where data augmentation using numerical perturbations resulted in a better classification in connectomics.
+In \emph{subject analyses}, machine error and between-tool variabilty can
+become comparable for some subjects in some regions. This observation is particularly
+relevant to the development of fMRI-based biomarkers aiming at
+individualized phenotype predictions. Machine error is expected to play
+a non-negligible role in such analyses, even when predictions combine
+results produced by multiple tools.
 
-It is notable that we obtained more uncertainty on thresholded results than unthresholded maps, %This issue is 
-probably due to different thresholding values used in different tools.
-This is consistent with the observations in~\cite{bowring2021isolating} where identified a high correlation between unthresholded t-statistic maps,
-but substantially low Dice coefficient for activations in the thresholded maps.
-This raises further investigations on thresholding techniques to reduce the associated instabilities.
+The observed regularization effect of group analyses toward numerical noise 
+is consistent with observations made in~\cite{kiar2020numerical} from diffusion MRI where 
+connectome graph statistics were found to be substantially unstable at the subject-level 
+while group distributions remained consistent.
 
-Given that Fuzzy Libmath only perturbs basic mathematical functions, we expect more numerical variability by perturbing linear algebra,
-in particular for non-scalar types like vectors or matrices. For the future study, this can be evaluated using MCA-instrumented versions
-of BLAS and LAPACK along with other libraries available in the Fuzzy project in Verificarlo's GitHub repository at github.com/verificarlo/fuzzy.
+\tristan{discuss larger numerical noise}
 
-\section{Conclusion}
+No association was found between
+machine error and between-tool variability at the group or subject level,
+which suggests that they can be investigated separately from each other.
+Even though their effects can be of comparable magnitude, machine error and
+between-tool variability are distinct and most likely involve different
+root causes \tristan{revise this based on correlations}.
 
-We presented a comparison study between numerical variability introduced by floating-point perturbations and tool variability arised from software package variations.
-For an fMRI analysis, we measured a significant variability in both conditions, which was comparable for some brain regions.
-We showed the Fuzzy Libmath library as a valuable model based on MCA method for simulating the numerical variability.
-Moreover, we can leverage the MCA-instrumented libraries for simulating the numerical uncertainty in different studies.
+In conclusion, our results motivate further numerical stability
+investigations in fMRI analysis pipelines. Pipeline-level analyses could be
+conducted to identify specific components that contribute to numerical
+variability, and if possible correct them accordingly. When instability is
+inherent to the analysis, sampling results distributions through numerical
+perturbations might improve stability, as explored in~\cite{kiar2021data}.
+Finally, pipeline-specific statistical corrections might be envisaged to
+account for numerical variability.
 
-Further work can be done to evaluate and localize the numerical stabilities within tools by focusing on the particular parts of
-the pipeline that has been identified as the main sources of variations in~\cite{bowring2021isolating}.
-This helps to identify the accurate source of instabilities within pipelines and gradually improve the stability of the pipeline components.
+% No conclusion on which tool is more/less stable.
 
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
 \bibliographystyle{plain}
@@
 \endinput
-%%
-%% End of file `sample-authordraft.tex'.

### 2021-12-02 paper/paper.tex
Update figures

@@
 
+\begin{figure*}[ht]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+    \begin{subfigure}[ht]{\textwidth}
+      \centering
+      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
+      %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \end{subfigure}
+    \caption{
+      Voxel-wise comparison of BT and WT variabilty subject by subject.}
+  \label{fig:unthresh-correlation-allsbj}
+  \end{minipage}}
+\end{figure*}
+
 \subsection{Group-level untresholded maps at different virtual precisions}
@@
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions. \tristan{Remove (std) from y label}}
+      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions.}
     \label{fig:across-precisions}
@@
         \centering
-        \includegraphics[width=\textwidth]{figures/bg_global_precision.pdf}
+        \includegraphics[width=.75\textwidth]{figures/bg_global_precision.pdf}
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
         \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
-        WT is computed at the virtual precision of t=17 bits. \tristan{remove (AFNI,SPM)}}
+        WT is computed at the virtual precision of t=17 bits.}
     \label{fig:gnp-mni}
@@
   \end{figure}
+
+  \begin{figure*}[ht]
+    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+      \begin{subfigure}[ht]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
+        %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \end{subfigure}
+      \caption{
+        Voxel-wise comparison of BT and WT variabilty. WT is computed with FSL at the virtual precision of t=17 bits.}
+    \label{fig:unthresh-correlation-gvp}
+    \end{minipage}}
+  \end{figure*}
 
@@
       \caption{Confusion matrices of activation instability
-      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation. \tristan{plot a single color map for 3 heatmaps}}
+      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation.}
       \label{fig:cm-thresh}

### 2021-12-03 paper/paper.tex
New introduction

--- 2021-12-01 paper/paper.tex
@@
 
-\title{Comparing tool variability and numerical variability in fMRI analyses}
+\title{Software variability in fMRI analysis:\\ comparing between-tool and numerical errors}
 
@@
 Furthermore, we found more numerical instability in thresholded maps than unthresholded ones
-and individual analysis than group-level analysis results.
+and individual analysis than group-level analysis results. \tristan{Abstract to be fixed}
 
@@
 
-% Data analysis workflows in many scientific domains have become increasingly complex and flexible.
-Recent studies highlighted the instability of the neuroimaging pipelines depending on the computing platform,
-software package, and even tool versions. Changes in the computational
-environment such as compilers, libraries, operating systems may introduce small numerical errors and create
-significantly different results in unstable pipelines~\cite{Glatard2015,Gronenschild2012,salari2020spot}.
-Moreover, the impact of methodological changes on fMRI analyses has been investigated extensively~\cite{bowring2019exploring,botvinik2020variability,bhagwat2021understanding,carp2012plurality}.
-For instance, in related works, it has been shown that running the same fMRI experiments by different teams can substantially affect
-scientific conclusions~\cite{botvinik2020variability,carp2012plurality};
-replication of fMRI experiments using the three most well-known software packages can influence the final determining areas of
-brain activations~\cite{bowring2019exploring}; %bowring2021isolating.
-also, the choice of preprocessing pipelines on neuroimaging cortical surface analyses is compound with instabilities~\cite{bhagwat2021understanding}.
-% In the presence of such instabilities, it is often hard to trust the data processing results. % validity of the computational results.
+Software variability has been highlighted as an important source of error
+in fMRI analysis, originating from mainly two factors: Between-tool
+variability denotes differences observed in results produced by different
+software toolboxes --- such as FSL, AFNI and SPM --- when analyzing the same dataset
+using similar methods. Numerical variability, in contrast, denotes
+differences observed in results produced by the same analytical toolbox
+executed in different environments – such as different operating systems or
+different hardware platforms. This manuscript investigates the extent to
+which both types of variability relate to each other.
 
-In such a heterogeneous environment, numerical instability is an essential issue for reproducibility.
-Numerical instability is a characteristic of pipelines that results from the influence of the floating-point arithmetics
-and iterative convergence of numerical errors~\cite{freitas2002issue}.
-Stochastic arithmetic approaches such as Monte-Carlo arithmetic (MCA)~\cite{Parker1997-qq} have been used to study the impact of numerical errors
-originating in floating-point computations in mathematical libraries.
-In~\cite{salari2021accurate}, we quantified the numerical stability of the HCP preprocessing pipeline~\cite{glasser2013} based on the MCA method
-by creating a Fuzzy environment, so that instrument mathematical functions are implemented in mathematical system libraries.
-As a result of numerical perturbations, we discovered a very low numerical precision in the result images comparable to the operating system variability.
-In a related study~\cite{kiar2020numerical}, the instability of results was explored by instrumenting a connectome estimation pipeline with the MCA technique.
-These works demonstrate the necessity of numerical uncertainty quantification for understanding related issues that hamper the computational reproducibility of analyses.
+Numerical variability stems from errors introduced in floating point
+computations by numerical rounding, cancellation and absorption~\cite{muller2018handbook}. In
+practice, the occurrence of such errors is affected by variations in
+hardware, software dependencies, compilation, parallelization, and most
+likely other factors. In general, the magnitude of such errors and their
+variations is in the range of 1 unit in the last place (ulp) --- also known
+as machine error, the difference between two successive floating-point
+numbers. However, when computations depend on imprecise libraries,
+numerical error may vary by several ulps. For instance, the numerical error
+of the complementary error function (erfc) is larger than 3 ulps in several
+mathematical libraries~\cite{zimmermann:hal-03141101}, implying that an update of this function could introduce
+numerical perturbations larger than 3 ulps. Due to numerical instability,
+machine error may amplify during its propagation through the analysis,
+resulting in considerable loss of precision in final results. In fMRI,
+numerical variability produced by Linux updates was shown to result in Dice
+coefficients ranging from 0.0 to 1.0 for ICA components produced by FSL
+MELODIC~\cite{Glatard2015}.
 
-\tristan{We investigate two questions: (1) how do numerical and between-tool variability compare? (2) are they correlated?}
+Between-tool variability is not a surprising concept for software
+developers: different programs executed on identical data may obviously
+produce different results. However, in fMRI, analysis programs all aim to
+estimate brain activity from measured variations in the BOLD signal, which
+is not expected to be measurably impacted by computational artifacts.
+Therefore, the observation reported in~\cite{bowring2019exploring} that the three
+main fMRI analysis toolboxes may result in marked
+analytical differences, such as Dice coefficients ranging from 0.000 to
+0.684 in comparisons of thresholded group-level statistic maps, has raised
+substantial concern. In a follow-up study~\cite{bowring2021isolating}, the same
+authors isolate the analytical components where the pipelines diverge,
+highlighting a major impact of the signal model and suggesting that the
+root-cause for between-tool variability depends on the analysis design and
+task paradigm.  \tristan{[refer to Xinhui's pre-print].}
 
-In this work, we reproduce an fMRI analysis in~\cite{bowring2019exploring} with different neuroimaging software packages in the presence of the Fuzzy environment,
-and then quantify the variability across tools and the numerical variability in results.
-We call the cross-software variation and numerical variation, between tool (BT) and within tool (WT) variability, respectively.
-In fact, the WT variability shows results across software packages in the Fuzzy environment.
-The primary objective of this study is to answer these two questions: 1) how the fMRI analyses across tools are numerically stable?
-2) how the numerical variability is in comparison with the tool variability?
-This comparative study reveals the importance of numerical variability and motivates research studies to evaluate the numerical uncertainty of the pipelines.
-
-% We start to reproduce an analysis from Bowring, this can be as a practice for reproducibility manner in the community.
-% In particular, we investigate the effect of 1) between software 2) within software (numerical)
-% We present a comparative assessment of group-level analysis of an fMRI pipeline.
+We investigate the relationship between numerical and between-tool
+variability through two main questions: (1) how do both types of
+variability compare in magnitude, and (2) is there an association between
+them. The first question determines the extent to which each variability
+source may impact current fMRI results, and which one should be addressed
+in priority. The second question may provide deeper insights on the origins
+of software variability. Conceptually, both types of variability may
+reflect a single solution space shaped by local minima and
+ill-conditioning, which could be explored through numerical or software
+perturbations.
 

### 2021-12-03 paper/paper.tex
Updates in bibliography, minor edits in methods

@@
 
-\author{Ali Salari$^1$, Other Authors$^1$, Tristan Glatard$^1$ \\
-$^1$ Department of Computer-Science and Software Engineering, Concordia University, Montreal, Canada}
+\author{Ali Salari$^1$, Yohan Chatelain$^1$, [other co-authors], Gregory Kiar$^2$, Tristan Glatard$^1$ \\
+$^1$ Department of Computer-Science and Software Engineering, Concordia University, Montreal, Canada\\
+$^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
 
@@
 
-To validate our instrumentations, we first verified that non-instrumented
+In~\cite{salari2021accurate}, Fuzzy Libmath was shown to accurately
+simulate the effect of Linux operating system updates in structural
+pre-processing pipelines. To validate our pipeline instrumentations for the present study, we first verified that non-instrumented
 executions of the same pipeline on the same dataset led to identical
@@
 
-We measured within-tool (WT) variability by running the same analyses three
+We measured numerical (within-tool -- WT) variability by running the same analyses three
 times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
@@
 values were chosen such that the numerical perturbation simulates machine
-error, the minimal distance between two consecutive floating-point numbers. The resulting samples are equally plausible estimates of
-the true numerical result. Moreover, to evaluate numerical perturbations at different magnitudes, 
+error. The resulting samples are equally plausible estimates of
+the true numerical result at the precision used by the pipelines. Moreover, to evaluate numerical perturbations at different magnitudes, 
 we repeated the FSL analyses for virtual
@@
 across a given pair of tools.
-For WT, we computed the standard deviation across the 3 
+For WT, we computed the standard deviation across the three
 Fuzzy Libmath samples of a given tool. Moreover, we computed WT variability for a pair of tools (A, B) as follows:
@@
 \end{equation}
-where $\sigma_{WT(.)}$ is the within-tool variability for a given tool.
+where $\sigma_{WT(.)}$ is the numerical variability for a given tool
+and $\sigma_{WT(., .)}$ is the numerical variability for a pair of tools.
 

### 2021-12-03 paper/paper.tex
Edits in results

@@
 executions of the same pipeline on the same dataset led to identical
-results \tristan{did you fix random seeds and if so in which pipelines?}. We also listed the pipeline
+results. We also listed the pipeline
 library dependencies using the \texttt{ldd} Linux utility and verified that
@@
 overall, however, differences were more noticeable visually. 
-The observed
-differences remained small and might be due to the use of Octave vs MATLAB in
-SPM. We performed visual quality control of the AFNI and SPM results
-for each individual subject \tristan{and confirmed that ...}.
-\tristan{add a figure to show the differences for SPM (Octave) and AFNI}
+The observed differences remained small and might be due to the use of
+Octave vs MATLAB in SPM. We performed visual quality control of the AFNI
+and SPM results for each individual subject and confirmed that images were
+correctly registered to the MNI template.
 
-\subsection{Summary group-level statistics}
+\subsection{Group-level unthresholded maps}
 
 Summary statistics for the group-level unthresholded and thresholded
-t-statistics are reported in Table~\ref{table:pipeline-stats}. BT
-variability for tool pair (A, B) was larger than WT variability for tool A and tool B for any tool pair, in both thresholded and
-unthresholded maps (Wilcoxon signed-rank test, t-test
-p~\textless~$10^{-163}$ for all tests).
+t-statistics are reported in Table~\ref{table:pipeline-stats}. For each
+tool pair (A, B), BT variability was significantly larger than machine
+error in tool A or B, in both thresholded and unthresholded maps (Wilcoxon
+signed-rank test p=0 for all tests, t-test p~\textless~$10^{-163}$ for all
+tests).
+
 % This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between BT and WT as:
@@
 
-\subsection{Group-level unthresholded maps}
 % \subsection{Variability of unthresholded statistical maps}
@@
 unthresholded maps. WT variability remains lower than BT variability
-overall. Interestingly, BT and WT variability appear correlated in a subset
-of voxels scattered across the brain
-(Figure~\ref{fig:unthresh-correlation}), but the reason for this apparent
-correlation remains unknown.
+overall. Moreover, BT and WT variability appeared moderately correlated (R
+in [0.56, 0.58], p=0.0). The set of voxels exhibiting comparable BT and
+WT values (located around the identity line in the XY plot) does not seem to have 
+any spatial consistency.
 
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).}
+    \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}),
+    and difference between them (\textbf{C}). \tristan{Add XY plots for each map}}
     \label{fig:unthresh-maps}
-    \end{minipage}}
-  \end{figure*}
-
-  %%%%%%%%%% Corr. plot of tstats%%%%%%%%
-  \begin{figure*}[ht]
-    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-      \begin{subfigure}[ht]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures/std-corr-unthresh-plot.png}
-        %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \end{subfigure}
-      \hfill
-      \begin{subfigure}[ht]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures/std/correlated-unthresh.png}
-        %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \end{subfigure}
-      \caption{
-        Voxel-wise comparison of BT and WT variabilty. The bottom row shows 
-        voxels where the BT/WT ratio is in (0.5, 2).}
-    \label{fig:unthresh-correlation}
     \end{minipage}}
@@
   this particular subject, WT variability approaches and even surpasses BT
-  variability in some regions. This subject also revealed that WT
-  variability mainly concentrated in some regions.
+  variability in some regions. Besides, numerical variability appears focal.
+
+  As for the group maps, BT and WT variability appeared moderately
+  correlated for all subjects (Figure~\ref{fig:unthresh-correlation-allsbj}, 
+  R in [0.442, 0.612], p=0.0 for all
+  subjects).
+  \tristan{Add the subject XY plots as supplementary material}
 
@@
 
-\begin{figure*}[ht]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-    \begin{subfigure}[ht]{\textwidth}
-      \centering
-      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \end{subfigure}
-    \caption{
-      Voxel-wise comparison of BT and WT variabilty subject by subject.}
-  \label{fig:unthresh-correlation-allsbj}
-  \end{minipage}}
-\end{figure*}
-
 \subsection{Group-level untresholded maps at different virtual precisions}
 
-While the previous results were obtained at the virtual precision of 53~bits for double-precision values
-and 24~bits for single-precision values, we also evaluated WT variability across different virtual precisions for FSL.
+While the previous results were obtained for machine error, we also evaluated numerical variability across different virtual precisions for FSL.
 Figure~\ref{fig:across-precisions} shows the root-mean-square error (RMSE) between BT and WT variability maps.
@@
         \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
-        WT is computed at the virtual precision of t=17 bits.}
+        WT is computed at the virtual precision of t=17 bits.\tristan{merge with figure with brain maps}}
     \label{fig:gnp-mni}
@@
   Figure~\ref{fig:thresh-maps} compares BT and WT for thresholded group-level maps.
-  While BT is consistently larger than WT, thresholding is an unstable operation 
+  While BT is consistently larger than machine error, thresholding is an unstable operation 
   that results in comparable magnitudes for BT and WT within activation clusters where BT variability is low.
@@
   Figure~\ref{fig:cm-thresh} compares regional activation instability for BT and WT. The average ratio
-  of unstable regions was 26\% for BT and 9.2\% for WT. Moreover, the average F1 score was 0.28. Therefore, regional 
-  WT instability does not appear to be a 
-  good predictor of BT instability.
+  of unstable regions was 26\% for BT and 9.2\% for WT. The average F1 score in these confusion matrics was 0.28. Regional 
+  WT instability appears to moderately explain BT regional BT instability.
 
@@
 
+\appendix
+
+\tristan{Add SPM and AFNI replication figure here.}
+
+\begin{figure*}[ht]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+    \begin{subfigure}[ht]{\textwidth}
+      \centering
+      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
+      %\caption{Standard deviation of thresholded t-statistics map on template surface}
+    \end{subfigure}
+    \caption{
+      Voxel-wise comparison of BT and WT variabilty subject by subject. \tristan{update figure}}
+  \label{fig:unthresh-correlation-allsbj}
+  \end{minipage}}
+\end{figure*}
+
 % No conclusion on which tool is more/less stable.

### 2021-12-03 paper/paper.tex
Update figures

@@
 error in tool A or B, in both thresholded and unthresholded maps (Wilcoxon
-signed-rank test p=0 for all tests, t-test p~\textless~$10^{-163}$ for all
+signed-rank test p~\textless~$10^{-162}$ for all tests, t-test p=0 for all
 tests).
@@
     \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+      \begin{subfigure}[ht]{\textwidth}
       \centering
@@
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \end{subfigure}
+      \hfill
+      \begin{subfigure}[ht]{\textwidth}
+        \centering
+        \includegraphics[width=.9\textwidth]{figures/std-corr-unthresh-plot.png}
+        %\caption{Standard deviation of thresholded t-statistics map on template surface}
+      \end{subfigure}
+
     \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}),
-    and difference between them (\textbf{C}). \tristan{Add XY plots for each map}}
+    and difference between them (\textbf{C}).}
     \label{fig:unthresh-maps}
@@
   reported in Table~\ref{table:unthresh-maps-subjects}. As for group-level
-  maps, BT variability was consistently larger than WT variability
-  \tristan{report statistical tests}.
+  maps, BT variability was consistently larger than WT variability (Wilcoxon
+  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for all
+  tests).
 
@@
   subjects).
-  \tristan{Add the subject XY plots as supplementary material}
 
@@
   %%%%%%%%%% plot different precisions%%%%%%%%
-  \begin{figure}[ht]
-    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-        \centering
-        \includegraphics[width=.75\textwidth]{figures/bg_global_precision.pdf}
-        %\caption{Standard deviation of thresholded t-statistics map on template surface}
-        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
-        WT is computed at the virtual precision of t=17 bits.\tristan{merge with figure with brain maps}}
-    \label{fig:gnp-mni}
-    \end{minipage}}
-  \end{figure}
-
   \begin{figure*}[ht]
@@
         \centering
-        \includegraphics[width=\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
+        \includegraphics[width=.75\textwidth]{figures/bg_global_precision.pdf}
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
         \end{subfigure}
-      \caption{
-        Voxel-wise comparison of BT and WT variabilty. WT is computed with FSL at the virtual precision of t=17 bits.}
-    \label{fig:unthresh-correlation-gvp}
+        \hfill
+        \begin{subfigure}[ht]{\textwidth}
+          \centering
+          \includegraphics[width=.8\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
+          %\caption{Standard deviation of thresholded t-statistics map on template surface}
+        \end{subfigure}
+        %\caption{Standard deviation of thresholded t-statistics map on template surface}
+        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
+        WT is computed at the virtual precision of t=17 bits.}
+    \label{fig:gnp-mni}
     \end{minipage}}
@@
       \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+        \begin{subfigure}[ht]{\textwidth}
           \centering
           \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
+          %\caption{Standard deviation of thresholded t-statistics map on template surface}
+          \end{subfigure}
+          \hfill
+          \begin{subfigure}[ht]{\textwidth}
+            \centering
+            \includegraphics[width=.9\textwidth]{figures/dice_analysis-plot.png}
+            %\caption{Standard deviation of thresholded t-statistics map on template surface}
+          \end{subfigure}
+        \centering
       \caption{Thresholded group t-statistics standard deviation maps
       computed across tools (\textbf{A}) and Fuzzy Libmath samples
-      (\textbf{B}).}
+      (\textbf{B}). The confusion matrices of activation instability
+      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation is represented in the bottom row.}
       \label{fig:thresh-maps}
-      \end{minipage}}
-    \end{figure*}
-
-    % %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
-    \begin{figure*}[ht]
-      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-      \centering
-      \includegraphics[width=\textwidth]{figures/dice_analysis-plot.png}
-      \caption{Confusion matrices of activation instability
-      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation.}
-      \label{fig:cm-thresh}
       \end{minipage}}
@@
 
-\tristan{Add SPM and AFNI replication figure here.}
+\begin{figure*}[ht]
+  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  \centering
+  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
+  \caption{Differences between replicated and original results obtained in~\cite{bowring2019exploring} 
+  of unthresholded group-level t-statistics for SPM (left) and AFNI (right).}
+  \label{fig:replication-diff}
+\end{minipage}}
+\end{figure*}
 
@@
     \end{subfigure}
-    \caption{
-      Voxel-wise comparison of BT and WT variabilty subject by subject. \tristan{update figure}}
+    \caption{Voxel-wise comparison of BT and WT variabilty for 16 subjects.}
   \label{fig:unthresh-correlation-allsbj}

### 2021-12-06 paper/paper.tex
Update figures

@@
       \end{subfigure}
-      \hfill
-      \begin{subfigure}[ht]{\textwidth}
-        \centering
-        \includegraphics[width=.9\textwidth]{figures/std-corr-unthresh-plot.png}
-        %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \end{subfigure}
-
     \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}),
@@
         \end{subfigure}
-        \hfill
-        \begin{subfigure}[ht]{\textwidth}
-          \centering
-          \includegraphics[width=.8\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
-          %\caption{Standard deviation of thresholded t-statistics map on template surface}
-        \end{subfigure}
-        %\caption{Standard deviation of thresholded t-statistics map on template surface}
         \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
@@
           \end{subfigure}
-          \hfill
-          \begin{subfigure}[ht]{\textwidth}
-            \centering
-            \includegraphics[width=.9\textwidth]{figures/dice_analysis-plot.png}
-            %\caption{Standard deviation of thresholded t-statistics map on template surface}
-          \end{subfigure}
         \centering
@@
       (\textbf{B}). The confusion matrices of activation instability
-      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation is represented in the bottom row.}
+      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation is represented in (\textbf{D}).}
       \label{fig:thresh-maps}

### 2021-12-06 paper/paper.tex
Edits in results

--- 2021-12-03 paper/paper.tex
@@
- \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-%\usepackage{hyphenat}
+ \documentclass[11pt,onecolumn]{article}
+ \usepackage[margin=0.5in]{geometry}
+
 \usepackage[ruled,vlined]{algorithm2e}
@@
 \end{abstract}
-
-\begin{IEEEkeywords}
-  Numerical Instability, Reproducibility, Monte-Carlo arithmetic, Neuroimaging
-\end{IEEEkeywords}
 
@@
 All scripts and data to reproduce the results are
-available at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
+available in out GitHub repository at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
 
@@
 overall, however, differences were more noticeable visually. 
-The observed differences remained small and might be due to the use of
-Octave vs MATLAB in SPM. We performed visual quality control of the AFNI
-and SPM results for each individual subject and confirmed that images were
+The observed differences remained small (see Appendix ~\ref{sec:supp-repro}) and might be due to the use of
+Octave vs MATLAB in SPM and of multithreading in AFNI. We performed visual quality control of the AFNI
+and SPM results for each individual subject and confirmed that \tristan{Ali: which ones?} images were
 correctly registered to the MNI template.
 
-\subsection{Group-level unthresholded maps}
+\subsection{In group analysis, BT variability was larger than and correlated with machine error}
 
-Summary statistics for the group-level unthresholded and thresholded
-t-statistics are reported in Table~\ref{table:pipeline-stats}. For each
-tool pair (A, B), BT variability was significantly larger than machine
-error in tool A or B, in both thresholded and unthresholded maps (Wilcoxon
-signed-rank test p~\textless~$10^{-162}$ for all tests, t-test p=0 for all
-tests).
+Table~\ref{table:pipeline-stats} reports on summary statistics for the
+group-level t-statistics. For each tool pair (A, B), BT variability was
+significantly larger than machine error in tool A or B, in both thresholded
+and unthresholded maps (Wilcoxon signed-rank test p~\textless~$10^{-162}$
+for all tests, t-test p=0 for all tests). These global differences were
+confirmed regionally (Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C}). 
+In addition, BT and WT variability appeared moderately correlated (R
+in [0.56, 0.58], p=0.0, Figure~\ref{fig:unthresh-maps}-\textbf{D}). Interestingly, the correlation 
+was driven by a set of voxels exhibiting comparable BT and
+WT values (located around the identity line in the XY plot), which, however, did not seem to have 
+any spatial consistency.
 
-% This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between BT and WT as:
-
-% \begin{equation*}
-%   \left\{
-%     \begin{aligned}
-%       & BT(a, b), WT(a),\\
-%       & BT(a, b), WT(b)
-%     \end{aligned}  
-%     \quad  a,b \in [FSL, SPM, AFNI] \;
-%   \right\}
-%   \label{eq:t-tests}
-% \end{equation*}
-
-% We obtained statistically significant values between BT and WT
-% variability with t-value $> 70$ and p-value $< 0.05$.
-
-%%%%%%%%%% Summary of statstics %%%%%%%%
 \setlength{\tabcolsep}{5pt}
@@
     \centering
-    \begin{tabular}{cccc|cc}
+    \begin{tabular}{cccccc|cc}
         \toprule
-        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c}{Unthresholded} \\
-        \cmidrule{3-4} \cmidrule{5-6} \\
-        {} & {} & Mean & Std. dev. & Mean & Std. dev. \\
+        && \multicolumn{4}{c|}{Group analyses} & \multicolumn{2}{c}{Subject analyses}\\
+        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded} \\
+        % \cmidrule{3-8}
+        {} & {} & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ & $\mu$ & $\sigma$ \\
         \midrule
-        \rowcolor{lightgray}
-        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  \\
-        \rowcolor{lightgray}
-        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  \\
-        \rowcolor{lightgray}
-        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  \\
-        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  \\
-        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  \\
-        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  \\
+        \rowcolor{lightgray!50}
+        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  & 0.366       & 0.293     \\
+        \rowcolor{lightgray!50}
+        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  & 0.439       & 0.352     \\
+        \rowcolor{lightgray!50} 
+        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  & 0.491       & 0.381     \\
+        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  & 0.077       & 0.054     \\
+        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  & 0.048       & 0.037     \\
+        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  & 0.108       & 0.131     \\
         \bottomrule
@@
     \caption{Voxel-wise mean and standard deviation of BT and WT variability
-    in group-level t-statistics maps.}
+    in group and subject t-statistics maps. \tristan{add stats on subject-level thresholded maps}}
     \label{table:pipeline-stats}
@@
 
-% \subsection{Variability of unthresholded statistical maps}
-
-Figure~\ref{fig:unthresh-maps} compares BT and WT variability in
-unthresholded maps. WT variability remains lower than BT variability
-overall. Moreover, BT and WT variability appeared moderately correlated (R
-in [0.56, 0.58], p=0.0). The set of voxels exhibiting comparable BT and
-WT values (located around the identity line in the XY plot) does not seem to have 
-any spatial consistency.
-
-%%%%%%%%%% Var. of Unthresh %%%%%%%%
 \begin{figure*}[ht]
-    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-      \begin{subfigure}[ht]{\textwidth}
   \centering
-      \includegraphics[width=\textwidth]{figures/std/gl-unthresh.png}
+    % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+      \begin{subfigure}[ht]{0.9\textwidth}
+      \centering
+      \includegraphics[width=0.9\textwidth]{figures/std/gl-unthresh.png}
       %\caption{Standard deviation of thresholded t-statistics map on template surface}
@@
       \hfill
-      \begin{subfigure}[ht]{\textwidth}
+      \begin{subfigure}[ht]{0.9\textwidth}
         \centering
@@
       \end{subfigure}
-
-    \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}),
-    and difference between them (\textbf{C}).}
+    \caption{Unthresholded group-level variability computed between tools
+    (\textbf{A}), within tools at machine error (\textbf{B}), difference
+    between them (\textbf{C}), and voxel-wise comparison (\textbf{D}). }
     \label{fig:unthresh-maps}
-    \end{minipage}}
+    % \end{minipage}}
   \end{figure*}
 
-  \subsection{Subject-level unthresholded maps}
+  \subsection{In subject analyses, machine error approached BT variability in some regions}
 
-  Summary statistics for subject-level unthresholded t-statistics maps are
-  reported in Table~\ref{table:unthresh-maps-subjects}. As for group-level
+  Table~\ref{table:pipeline-stats} also reports on summary statistics for subject-level unthresholded t-statistics maps. As for group-level
   maps, BT variability was consistently larger than WT variability (Wilcoxon
   signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for all
-  tests).
-
-  Figure~\ref{fig:unthresh-maps-sbj} shows BT and WT variability for
-  the subject with the highest WT variability among the 16 subjects. For
-  this particular subject, WT variability approaches and even surpasses BT
-  variability in some regions. Besides, numerical variability appears focal.
-
-  As for the group maps, BT and WT variability appeared moderately
-  correlated for all subjects (Figure~\ref{fig:unthresh-correlation-allsbj}, 
-  R in [0.442, 0.612], p=0.0 for all
-  subjects).
-
-  %%%%%%%%%% Summary of statstics %%%%%%%%
-\setlength{\tabcolsep}{5pt}
-\begin{table}[h]
-    \centering
-    \begin{tabular}{cccc}
-        \toprule
-        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Unthresholded} \\
-        \cmidrule{3-4} \\
-        {} & {} & Mean & Std. dev. \\
-        \midrule
-        \rowcolor{lightgray}
-        {Between Tools} & FSL vs. SPM        &  0.366       & 0.293     \\
-        \rowcolor{lightgray}
-        {(BT)} & FSL vs. AFNI                &  0.439       & 0.352     \\
-        \rowcolor{lightgray}
-        {} & AFNI vs. SPM                    &  0.491       & 0.381     \\
-        {Within Tool} & FSL                  &  0.077       & 0.054     \\
-        {(WT)}   & SPM                       &  0.048       & 0.037     \\
-        {}   & AFNI                          &  0.108       & 0.131     \\
-        \bottomrule
-    \end{tabular} 
-    \caption{Voxel-wise mean and standard deviation of BT and WT variability
-    in subject-level t-statistics maps (averages on 16 subjects).}
-    \label{table:unthresh-maps-subjects}
-\end{table}
+  tests). However, for some subjects, machine error (WT variability) approached and even 
+  surpassed BT in some regions (Figure~\ref{fig:unthresh-maps-sbj}).  As for the group maps, BT and WT variability appeared moderately
+  correlated for all subjects (R in [0.442, 0.612], p=0.0 for all
+  subjects, Appendix~\ref{sec:supp-subjects}).
 
@@
 \begin{figure*}[ht]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
     \centering
-    \includegraphics[width=\textwidth]{figures/std/sbj05-std.png}
+    \includegraphics[width=0.9\textwidth]{figures/std/sbj05-std.png}
     %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \caption{For subject with highest WT variability, unthresholded subject-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).}
+    \caption{For subject with highest WT variability,
+    unthresholded subject-level variability computed between tools (\textbf{A}), within tools at machine error (\textbf{B}),
+     and difference between them (\textbf{C}).}
   \label{fig:unthresh-maps-sbj}
-  \end{minipage}}
 \end{figure*}
 
-\subsection{Group-level untresholded maps at different virtual precisions}
+\subsection{At the precision t=17~bits, numerical variability approached BT variability in group analysis}
 
-While the previous results were obtained for machine error, we also evaluated numerical variability across different virtual precisions for FSL.
-Figure~\ref{fig:across-precisions} shows the root-mean-square error (RMSE) between BT and WT variability maps.
-The virtual precision of t=17 bits minimized the RMSE between BT and WT.
-Figure~\ref{fig:gnp-mni} shows the corresponding BT and WT maps obtained at t=17 bits, showing 
-that BT and WT reach comparable magnitudes in some regions.
-
-  %%%%%%%%%% plot different precisions%%%%%%%%
-  \begin{figure}[ht]
-    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
-        \centering
-        \includegraphics[width=\columnwidth]{figures/rmse-precisions.png}
-        %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions.}
-    \label{fig:across-precisions}
-    \end{minipage}}
-  \end{figure}
+While the previous results were obtained for machine error, we also
+evaluated numerical variability across different virtual precisions for FSL
+and found that the virtual precision of t=17 bits minimized the RMSE
+between BT and WT in unthresholded group maps. Figure~\ref{fig:gnp-mni} shows BT
+and WT in the corresponding group maps obtained at t=17 bits, showing that
+BT and WT reach comparable magnitudes in some regions. BT and WT remained
+moderately correlated at this precision. \tristan{In the text, add statistics similar to Table 2.}
 
@@
   \begin{figure*}[ht]
-    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
       \begin{subfigure}[ht]{\textwidth}
@@
         %\caption{Standard deviation of thresholded t-statistics map on template surface}
-        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
-        WT is computed at the virtual precision of t=17 bits.}
+        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}),
+          within tools at the virtual precision of t=17~bits (\textbf{B}), difference between them (\textbf{C}), and 
+          voxel-wise comparison (\textbf{D}).}
     \label{fig:gnp-mni}
-    \end{minipage}}
   \end{figure*}
 
-  \subsection{Group-level thresholded maps}
+  \subsection{Previous results are confirmed in thresholded group maps}
 
-  Figure~\ref{fig:thresh-maps} compares BT and WT for thresholded group-level maps.
-  While BT is consistently larger than machine error, thresholding is an unstable operation 
-  that results in comparable magnitudes for BT and WT within activation clusters where BT variability is low.
-
-  Figure~\ref{fig:cm-thresh} compares regional activation instability for BT and WT. The average ratio
-  of unstable regions was 26\% for BT and 9.2\% for WT. The average F1 score in these confusion matrics was 0.28. Regional 
-  WT instability appears to moderately explain BT regional BT instability.
+  Figure~\ref{fig:thresh-maps}-\textbf{A},\textbf{B},\textbf{C} compares BT
+  and WT for thresholded group maps. Thresholding is an unstable operation
+  that introduced high variability for both BT and WT at the edges of
+  active regions. Except in these regions, BT remained consistently larger
+  than WT. To measure a potential association between BT and WT, we
+  measured WT instability and BT instability in each region of the
+  HCP-MMP1.0 parcellation. The confusion matrices in
+  Figure~\ref{fig:thresh-maps}-\textbf{D} report on such instabilities for
+  the 360 tested regions. The average ratio of unstable regions was 26\%
+  for BT and 9.2\% for WT, which confirmed that BT variability was larger than machine error.
+  The average Cohen's kappa score between WT instability and BT instability was $\kappa=0.17$, indicating 
+  a moderate agreement between WT instability and BT instability (-1 \textless $\kappa$ \textless 1, $\kappa$\leq 0 denotes chance agreement).
 
@@
   \begin{figure*}[ht]
-      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
         \begin{subfigure}[ht]{\textwidth}
@@
       \label{fig:thresh-maps}
-      \end{minipage}}
     \end{figure*}
@@
 
-In fMRI \emph{group analyses}, machine error remains an order of magnitude
+In fMRI group analyses, machine error remains an order of magnitude
 smaller than between-tool variability. Group analyses have a regularization
@@
 
-In \emph{subject analyses}, machine error and between-tool variabilty can
+In subject analyses, machine error and between-tool variabilty can
 become comparable for some subjects in some regions. This observation is particularly
@@
 
-\appendix
-
-\begin{figure*}[ht]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-  \centering
-  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
-  \caption{Differences between replicated and original results obtained in~\cite{bowring2019exploring} 
-  of unthresholded group-level t-statistics for SPM (left) and AFNI (right).}
-  \label{fig:replication-diff}
-\end{minipage}}
-\end{figure*}
-
-\begin{figure*}[ht]
-  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
-    \begin{subfigure}[ht]{\textwidth}
-      \centering
-      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
-      %\caption{Standard deviation of thresholded t-statistics map on template surface}
-    \end{subfigure}
-    \caption{Voxel-wise comparison of BT and WT variabilty for 16 subjects.}
-  \label{fig:unthresh-correlation-allsbj}
-  \end{minipage}}
-\end{figure*}
-
-% No conclusion on which tool is more/less stable.
-
 \bibliographystyle{plain}
@@
 
+\clearpage
+
+\setcounter{equation}{0}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\setcounter{section}{0}
+
+\makeatletter
+\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thesection}{S\arabic{section}}
+
+\textbf{\centering \Large Supplemental Materials}
+
+\section{Reproduced results}
+\label{sec:supp-repro}
+
+Figure~\ref{fig:replication-diff} shows the difference in SPM and AFNI
+group analyses maps between the results in~\cite{bowring2019exploring} and
+our replication. Numerical perturbations of 1 ulp are likely to have been
+introduced by our replication due to the use of Octave vs MATLAB for SPM
+and multithreading for AFNI. However, the group maps remained very similar
+overall, which led us to conclude that our results correctly reproduced 
+the ones in~\cite{bowring2019exploring}.
+\begin{figure*}[ht]
+  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
+  % \centering
+  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
+  \caption{Differences between reproduced and original results obtained in~\cite{bowring2019exploring} 
+  of unthresholded group-level t-statistics for SPM (left) and AFNI (right).}
+  \label{fig:replication-diff}
+% \end{minipage}}
+\end{figure*}
+
+\section{BT and WT correlations for all subjects}
+\label{sec:supp-subjects}
+
+Figure~\ref{fig:unthresh-correlation-allsbj} plots the relationship between
+WT and BT for each subject, showing a consistent moderate correlation between BT and
+WT.
+
+\begin{figure*}[ht]
+      \centering
+      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
+      \caption{Relationship between BT and WT variabilty for 16 subjects.}
+  \label{fig:unthresh-correlation-allsbj}
+\end{figure*}
+
 \end{document}

### 2021-12-06 paper/paper.tex

@@
       \end{subfigure}
-      \hfill
-      \begin{subfigure}[ht]{0.9\textwidth}
-        \centering
-        \includegraphics[width=.9\textwidth]{figures/std-corr-unthresh-plot.png}
-        %\caption{Standard deviation of thresholded t-statistics map on template surface}
-      \end{subfigure}
     \caption{Unthresholded group-level variability computed between tools
@@
         \end{subfigure}
-        \hfill
-        \begin{subfigure}[ht]{\textwidth}
-          \centering
-          \includegraphics[width=.8\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
-          %\caption{Standard deviation of thresholded t-statistics map on template surface}
-        \end{subfigure}
         %\caption{Standard deviation of thresholded t-statistics map on template surface}

### 2021-12-06 paper/paper.tex
More discussion

@@
 Octave vs MATLAB in SPM and of multithreading in AFNI. We performed visual quality control of the AFNI
-and SPM results for each individual subject and confirmed that \tristan{Ali: which ones?} images were
-correctly registered to the MNI template.
+and SPM results for each individual subject and confirmed that T1-weighted images were
+correctly skull-stripped and registered to the MNI template.
 
-\subsection{In group analysis, BT variability was larger than and correlated with machine error}
+\subsection{In the group analysis, BT variability was larger than and correlated with machine error}
 
@@
 for all tests, t-test p=0 for all tests). These global differences were
-confirmed regionally (Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C}). 
-In addition, BT and WT variability appeared moderately correlated (R
+confirmed across the maps (Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C}). 
+In addition, BT and WT variability appeared moderately correlated (Pearson's R
 in [0.56, 0.58], p=0.0, Figure~\ref{fig:unthresh-maps}-\textbf{D}). Interestingly, the correlation 
@@
 WT values (located around the identity line in the XY plot), which, however, did not seem to have 
-any spatial consistency.
+any spatial consistency \tristan{Ali, check for intensity differences between these voxels and the other ones}.
 
@@
 
-  Table~\ref{table:pipeline-stats} also reports on summary statistics for subject-level unthresholded t-statistics maps. As for group-level
-  maps, BT variability was consistently larger than WT variability (Wilcoxon
-  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for all
-  tests). However, for some subjects, machine error (WT variability) approached and even 
-  surpassed BT in some regions (Figure~\ref{fig:unthresh-maps-sbj}).  As for the group maps, BT and WT variability appeared moderately
-  correlated for all subjects (R in [0.442, 0.612], p=0.0 for all
-  subjects, Appendix~\ref{sec:supp-subjects}).
+  Table~\ref{table:pipeline-stats} also reports on summary statistics for
+  subject-level unthresholded t-statistics maps. As for group-level maps,
+  BT variability was consistently larger than WT variability (Wilcoxon
+  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for
+  all tests). However, Figure~\ref{fig:unthresh-maps-sbj} shows that for
+  some subjects, machine error (WT variability) approached and even
+  surpassed BT in some regions. As for the group maps, BT and WT
+  variability appeared moderately correlated for all subjects (R in [0.442,
+  0.612], p=0.0 for all subjects, see Appendix~\ref{sec:supp-subjects}).
 
@@
 
-\subsection{At the precision t=17~bits, numerical variability approached BT variability in group analysis}
+\subsection{At precision t=17~bits, WT variability approached BT variability in the group analysis}
 
@@
 BT and WT reach comparable magnitudes in some regions. BT and WT remained
-moderately correlated at this precision. \tristan{In the text, add statistics similar to Table 2.}
+moderately correlated at this precision. \tristan{In the text, add statistics similar to Table 2: is BT still larger than WT here?}
 
@@
 
-  \subsection{Previous results are confirmed in thresholded group maps}
+  \subsection{Previous results were confirmed in thresholded group maps}
 
@@
   and WT for thresholded group maps. Thresholding is an unstable operation
-  that introduced high variability for both BT and WT at the edges of
+  that introduced variability for both BT and WT at the edges of
   active regions. Except in these regions, BT remained consistently larger
-  than WT. To measure a potential association between BT and WT, we
+  than WT. To measure correlation between BT and WT, we
   measured WT instability and BT instability in each region of the
@@
   for BT and 9.2\% for WT, which confirmed that BT variability was larger than machine error.
-  The average Cohen's kappa score between WT instability and BT instability was $\kappa=0.17$, indicating 
-  a moderate agreement between WT instability and BT instability (-1 \textless $\kappa$ \textless 1, $\kappa$\leq 0 denotes chance agreement).
+  The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, -1 \textless $\kappa$ \textless 1} between WT instability and BT instability was $\kappa=0.17$, indicating 
+  a moderate agreement between WT instability and BT instability.
 
@@
 
-In fMRI group analyses, machine error remains an order of magnitude
-smaller than between-tool variability. Group analyses have a regularization
-effect toward numerical noise, which is expected to amplify as sample size
+In fMRI group analyses, machine error remains an order of magnitude smaller
+than between-tool variability. Group analyses have a regularization effect
+toward numerical noise, which is expected to amplify as sample size
 increases. Therefore, for fMRI studies with large sample sizes, machine
 error can safely be neglected with respect to between-tool variability. The
-recommendation made in~\cite{botvinik2020variability} to rely on ``multiverse" analyses where
-multiple analysis tools are compared is therefore likely to successfully correct
-for machine error in group studies.
+recommendation made in~\cite{botvinik2020variability} to rely on
+``multiverse" analyses where multiple analysis tools are compared is
+therefore likely to successfully correct for machine error in group
+studies. Nevertheless, machine error remains substantial in group analyses
+that are based on a single tool, as is commonly the case in current fMRI
+studies. In particular, in our study, the inherent instability of
+thresholding was triggered by machine error in 9\% of 360 brain regions,
+which indicates that machine error might have impacted neuroscientific
+conclusions related to these regions.
 
-However, machine error remains important in group analyses that are based
-on a single tool, as is commonly the case in current fMRI studies. In
-particular, in our study, the inherent instability of thresholding was
-triggered by machine error in 9\% of 360 brain regions, which indicates
-that machine error might have impacted neuroscientific conclusions related
-to these regions.
-
-In subject analyses, machine error and between-tool variabilty can
-become comparable for some subjects in some regions. This observation is particularly
-relevant to the development of fMRI-based biomarkers aiming at
-individualized phenotype predictions. Machine error is expected to play
+In subject analyses, machine error and between-tool variabilty can become
+of comparable magnitude for some subjects in some regions. This observation
+is particularly relevant to the development of fMRI-based biomarkers aiming
+at individualized phenotype predictions. Machine error is expected to play
 a non-negligible role in such analyses, even when predictions combine
-results produced by multiple tools.
-
-The observed regularization effect of group analyses toward numerical noise 
-is consistent with observations made in~\cite{kiar2020numerical} from diffusion MRI where 
-connectome graph statistics were found to be substantially unstable at the subject-level 
+results produced by multiple tools. The observed regularization effect of
+group analyses toward numerical noise is consistent with observations made
+in~\cite{kiar2020numerical} from diffusion MRI where connectome graph
+statistics were found to be substantially unstable at the subject-level
 while group distributions remained consistent.
 
-\tristan{discuss larger numerical noise}
+For both group and subject analyses, between-tool variability and machine
+error were found to be moderately correlated. Even though between-tool
+variability and numerical variability are different in nature, this result
+suggests that in some cases both sources of variability may have a common
+cause that might be related to the conditioning of the BOLD signal
+estimation problem in a specific dataset. Therefore, in some regions,
+instabilities of similar magnitude may be triggered by small numerical
+perturbations, model variations or implementation differences. For
+instance, the analysis of datasets with high motion may be unstable both 
+across tools and numerically.
 
-No association was found between
-machine error and between-tool variability at the group or subject level,
-which suggests that they can be investigated separately from each other.
-Even though their effects can be of comparable magnitude, machine error and
-between-tool variability are distinct and most likely involve different
-root causes \tristan{revise this based on correlations}.
+Therefore, numerical stability may be suitable as a proxy to study
+between-tool variability. This speculation might be of practical value to
+address software variability at large given that numerical stability refers
+to a consistent mathematical framework whereas between-tool variability
+remains more empirical. Likewise, numerical and between-tool stability may
+be interesting proxies for analysis accuracy, and perhaps useful in quality
+control.
+
+The finding that numerical variability approached tool variability at the
+virtual precision of t=17~bits is interesting too. Indeed, while machine
+error generally introduces differences in the order of 1 ulp --- or
+t=53~bits for double-precision values and t=24~bits for single-precision
+ones --- common scientific software dependencies introduce larger errors.
+For instance, SciPy's 2D spline interpolation was recently found to be
+precise up to t=10~bits~\cite{pytracer} and might therefore introduce
+numerical perturbations leading to errors in the range of between-tool
+variability \tristan{Yohan, please check that sentence}. Such high errors
+might be triggered by updates in operating systems, Python, MATLAB, and
+other software dependencies.
+
+Our results are limited by the type of numerical noise introduced in the
+analyses. Indeed, we only introduced noise in the outputs of elementary
+mathematical functions while numerical noise could creep in any
+floating-point operation. Our estimation of numerical variability should
+therefore be considered a lower bound. Our estimation of tool varability is
+also likely to be underestimated, having tested only 3 analytical pipelines
+among the thousands available~\cite{carp2012plurality}.
 
@@
       \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
-      \caption{Relationship between BT and WT variabilty for 16 subjects.}
+      \caption{Comparison between BT and WT variabilty for 16 subjects.}
   \label{fig:unthresh-correlation-allsbj}

### 2021-12-06 paper/paper.tex
Edited abstract

@@
 
-Numerical and software variability broadly affect structural, diffusion, and functional MRI analyses. Numerical
-variability originates in software updates or code
-parallelization, whereas software variability reflects discrepancies between
-models implemented in different analysis software packages. While numerical
-and software variability were both shown to impact analysis outcomes, the
-extent to which these sources of variability compare for a given
-analysis remains understudied. This work presents a comparison of
-numerical and software variability for group-level and subject-level functional MRI analyses.
-We reproduced a previous comparison between functional MRI analysis
-software packages FSL, AFNI, and SPM, which we extended to measure
-numerical variability through Monte-Carlo arithmetic.
-Although We found that between-tool variability was larger than numerical variability,
-we identified brain regions that numerical perturbations simulated between-tool variability.
-Furthermore, we found more numerical instability in thresholded maps than unthresholded ones
-and individual analysis than group-level analysis results. \tristan{Abstract to be fixed}
-
+Software variability broadly affects functional MRI analyses due to
+differences among analytical tools and numerical instabilities. While
+numerical and between-tool variability were both shown to impact analysis
+outcomes, the extent to which these sources of variability compare for a
+given analysis remains understudied. We extended a previous comparison
+between fMRI analysis tools FSL, AFNI, and SPM, to measure numerical
+variability through Monte-Carlo arithmetic. We found that in group analyses
+between-tool variability was consistently larger than machine error,
+whereas in subject analyses machine error approached between-tool
+variability in some cases. Furthermore, between-tool variability and
+machine error appeared moderately correlated in all tested conditions.
+Finally, we found that numerical error at the precision of 17 bits --- a
+precision level found in commonly-used libraries --- had effects of similar
+magnitude \tristan{check that} than between-tool variability. Our findings motivate the
+continued investigation of numerical instability in neuroimaging, and position it 
+as a possible proxy for between-tool variations.
 \end{abstract}

### 2021-12-07 paper/paper.tex
Updates in introduction

@@
 Software variability broadly affects functional MRI analyses due to
-differences among analytical tools and numerical instabilities. While
-numerical and between-tool variability were both shown to impact analysis
-outcomes, the extent to which these sources of variability compare for a
-given analysis remains understudied. We extended a previous comparison
+differences among analytical tools as well as numerical instabilities. However,
+the extent to which numerical and between-tool variabilities compare for a
+given analysis is unclear. We extended a previous comparison
 between fMRI analysis tools FSL, AFNI, and SPM, to measure numerical
-variability through Monte-Carlo arithmetic. We found that in group analyses
+variability through Monte-Carlo arithmetic. We found that, in group analyses,
 between-tool variability was consistently larger than machine error,
-whereas in subject analyses machine error approached between-tool
+whereas in subject analyses, machine error approached between-tool
 variability in some cases. Furthermore, between-tool variability and
 machine error appeared moderately correlated in all tested conditions.
-Finally, we found that numerical error at the precision of 17 bits --- a
+Finally, we also found that numerical error at the precision of 17 bits --- a
 precision level found in commonly-used libraries --- had effects of similar
-magnitude \tristan{check that} than between-tool variability. Our findings motivate the
+magnitude \tristan{check that} than those of between-tool variability. Our findings motivate the
 continued investigation of numerical instability in neuroimaging, and position it 
@@
 Software variability has been highlighted as an important source of error
-in fMRI analysis, originating from mainly two factors: Between-tool
-variability denotes differences observed in results produced by different
+in fMRI analysis, originating from mainly two factors: between-tool
+variability denotes differences in the outcomes of different
 software toolboxes --- such as FSL, AFNI and SPM --- when analyzing the same dataset
 using similar methods. Numerical variability, in contrast, denotes
-differences observed in results produced by the same analytical toolbox
+differences in outcomes of the same analytical toolbox
 executed in different environments – such as different operating systems or
@@
 machine error may amplify during its propagation through the analysis,
-resulting in considerable loss of precision in final results. In fMRI,
+resulting in considerable loss of precision in final results. For instance, in fMRI,
 numerical variability produced by Linux updates was shown to result in Dice
@@
 
-Between-tool variability is not a surprising concept for software
-developers: different programs executed on identical data may obviously
-produce different results. However, in fMRI, analysis programs all aim to
-estimate brain activity from measured variations in the BOLD signal, which
-is not expected to be measurably impacted by computational artifacts.
-Therefore, the observation reported in~\cite{bowring2019exploring} that the three
-main fMRI analysis toolboxes may result in marked
-analytical differences, such as Dice coefficients ranging from 0.000 to
-0.684 in comparisons of thresholded group-level statistic maps, has raised
-substantial concern. In a follow-up study~\cite{bowring2021isolating}, the same
-authors isolate the analytical components where the pipelines diverge,
+Between-tool variability is not a surprising concept: different programs
+executed on the same data may obviously produce different results. However,
+in fMRI analysis, programs all aim to estimate brain activity from measured
+variations in the BOLD signal, which is not expected to be measurably
+impacted by computational artifacts. Therefore, the observation reported
+in~\cite{bowring2019exploring} that the three main fMRI analysis toolboxes
+may result in marked analytical differences (Dice coefficients ranging from
+0.000 to 0.684 for thresholded activation maps), has raised substantial
+concern. In a follow-up study~\cite{bowring2021isolating}, the same authors
+isolated the analytical components where the pipelines diverge,
 highlighting a major impact of the signal model and suggesting that the
 root-cause for between-tool variability depends on the analysis design and
-task paradigm.  \tristan{[refer to Xinhui's pre-print].}
+task paradigm. Further, the work in~\cite{Li2021.12.01.470790} found
+moderate agreement between results produced by five independent fMRI
+analysis pipelines and analyzed in details the components that led to these
+variations. Between-tool variability is supposedly an important determinant
+of the substantial analytical variability recently observed in
+fMRI~\cite{botvinik2020variability}.
 

### 2021-12-07 paper/paper.tex
Edits throughout

@@
 
-We replicated the fMRI analysis described as study `ds000001'
+We replicated the analysis described as study `ds000001'
 in~\cite{schonberg2012decreasing}, relying on the data publicly available
@@
 effect of tool variability for this dataset, which we intended to
-complement with the present quantification of numerical variability.
+extend with the present quantification of numerical variability.
 
@@
 implemented by~\cite{bowring2019exploring} consistently across all three
-software packages. Table~\ref{table:pipeline-steps} summarizes the analytical steps in each
+software packages. Table~\ref{table:pipeline-steps}, adapted from~\cite{bowring2019exploring},
+summarizes the analytical steps in each
 pipeline.
@@
 To introduce numerical noise in the analyses, we used
-the Fuzzy Libmath library~\cite{salari2021accurate}, a version of the GNU
+Fuzzy Libmath~\cite{salari2021accurate}, a version of the GNU
 mathematical library (libmath) instrumented with Monte-Carlo arithmetic.
-Monte-Carlo arithmetic simulates roundoff and catastrophic cancellation
-errors by introducing a controlled amount of noise in the floating-point
+Monte-Carlo arithmetic simulates numerical errors
+errors by introducing a controlled amount of noise in floating-point
 operations through the following perturbation~\cite{Parker1997-qq}:
@@
 the memory address of a symbol --- in our case \texttt{RTLD\_NEXT}, the
-address of the next occurrence of the function in memory. Function wrappers
-are compiled with Verificarlo. Verificarlo instruments the result of the
-addition between the original function output and a floating-point zero.
+address of the next occurrence of the function in memory. Compiling function wrappers
+with Verificarlo instruments the result of the
+addition between the original function output and the floating-point zero.
 
@@
 simulate the effect of Linux operating system updates in structural
-pre-processing pipelines. To validate our pipeline instrumentations for the present study, we first verified that non-instrumented
+pre-processing pipelines of the Human Connectome Project which are largely based on FSL.
+ To validate our pipeline instrumentations for the present study, we first verified that non-instrumented
 executions of the same pipeline on the same dataset led to identical
@@
 (2) there was no alternative implementation of elementary mathematical functions in the pipeline dependencies.
-Finally, we verified that the use of Fuzzy libmath affected computational results.
+Finally, we verified that the use of Fuzzy Libmath affected computational results.
 
@@
 computations were performed on \href{https://www.computecanada.ca}{Compute
-Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake
-@ 2.4 GHz (40 cores/node) CPU and 8~GB of RAM per core. We encapsulated the
-above-mentioned software packages in Docker container images available at
-\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
+Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake~@~2.4~GHz
+ (40 cores/node) CPU and 8~GB of RAM per core. To facilitate portability and reproducibility,
+ we encapsulated the
+above-mentioned software packages in Docker container images based on CentOS 7.3.
 
@@
 \section{Results}
-All scripts and data to reproduce the results are
-available in out GitHub repository at \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
+The scripts, Docker images, and data to reproduce the results are available
+in out GitHub repository at
+\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
 
@@
 overall, however, differences were more noticeable visually. 
-The observed differences remained small (see Appendix ~\ref{sec:supp-repro}) and might be due to the use of
-Octave vs MATLAB in SPM and of multithreading in AFNI. We performed visual quality control of the AFNI
+The observed differences remained small (see Supplemental Material~\ref{sec:supp-repro}) and might be due to the use of
+GNU/Octave vs MATLAB in SPM and of multithreading in AFNI. We performed visual quality control of the AFNI
 and SPM results for each individual subject and confirmed that T1-weighted images were
@@
 
-Table~\ref{table:pipeline-stats} reports on summary statistics for the
+Table~\ref{table:pipeline-stats} presents summary statistics for the
 group-level t-statistics. For each tool pair (A, B), BT variability was
@@
 and unthresholded maps (Wilcoxon signed-rank test p~\textless~$10^{-162}$
-for all tests, t-test p=0 for all tests). These global differences were
-confirmed across the maps (Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C}). 
-In addition, BT and WT variability appeared moderately correlated (Pearson's R
+for all tests, t-test p=0 for all tests).
+Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C} shows that
+these global differences were confirmed regionally. 
+In addition, BT and WT variability appeared moderately correlated across voxels (Pearson's R
 in [0.56, 0.58], p=0.0, Figure~\ref{fig:unthresh-maps}-\textbf{D}). Interestingly, the correlation 
@@
         \toprule
-        && \multicolumn{4}{c|}{Group analyses} & \multicolumn{2}{c}{Subject analyses}\\
+        && \multicolumn{4}{c|}{Group map} & \multicolumn{2}{c}{Subject maps}\\
         \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded} \\
@@
     \caption{Voxel-wise mean and standard deviation of BT and WT variability
-    in group and subject t-statistics maps. \tristan{add stats on subject-level thresholded maps}}
+    in t-statistics maps. \tristan{add stats on subject-level thresholded maps}}
     \label{table:pipeline-stats}
@@
 
-  Table~\ref{table:pipeline-stats} also reports on summary statistics for
+  Table~\ref{table:pipeline-stats} also presents summary statistics for
   subject-level unthresholded t-statistics maps. As for group-level maps,
@@
   variability appeared moderately correlated for all subjects (R in [0.442,
-  0.612], p=0.0 for all subjects, see Appendix~\ref{sec:supp-subjects}).
+  0.612], p=0.0 for all subjects, see Supplemental Material~\ref{sec:supp-subjects}).
 
@@
   and WT for thresholded group maps. Thresholding is an unstable operation
-  that introduced variability for both BT and WT at the edges of
-  active regions. Except in these regions, BT remained consistently larger
-  than WT. To measure correlation between BT and WT, we
+  that introduced variability at the edges of
+  active regions for both BT and WT. Except in these regions, BT remained consistently larger
+  than WT. Moreover, to measure correlation between BT and WT, we
   measured WT instability and BT instability in each region of the
   HCP-MMP1.0 parcellation. The confusion matrices in
-  Figure~\ref{fig:thresh-maps}-\textbf{D} report on such instabilities for
+  Figure~\ref{fig:thresh-maps}-\textbf{D} report these instabilities for
   the 360 tested regions. The average ratio of unstable regions was 26\%
   for BT and 9.2\% for WT, which confirmed that BT variability was larger than machine error.
-  The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, -1 \textless $\kappa$ \textless 1} between WT instability and BT instability was $\kappa=0.17$, indicating 
+  The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, $-1 \leq \kappa \leq 1$}
+   between WT instability and BT instability was $\kappa=0.17$, indicating 
   a moderate agreement between WT instability and BT instability.
@@
         \centering
-      \caption{Thresholded group t-statistics standard deviation maps
-      computed across tools (\textbf{A}) and Fuzzy Libmath samples
-      (\textbf{B}). The confusion matrices of activation instability
-      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation is represented in (\textbf{D}).}
+      \caption{Thresholded group t-statistics standard deviations computed between tools (\textbf{A}),
+      within tools at the virtual precision of t=17~bits (\textbf{B}), difference between them (\textbf{C}), and 
+      confusion matrices of activation instability
+      in BT and WT among the 360 regions of the HCP-MMP1.0 parcellation (\textbf{D}).}
       \label{fig:thresh-maps}
@@
 instabilities of similar magnitude may be triggered by small numerical
-perturbations, model variations or implementation differences. For
+perturbations, model variations, or implementation differences. For
 instance, the analysis of datasets with high motion may be unstable both 
@@
 
-Therefore, numerical stability may be suitable as a proxy to study
+Therefore, numerical stability may be a suitable proxy to study
 between-tool variability. This speculation might be of practical value to
@@
 to a consistent mathematical framework whereas between-tool variability
-remains more empirical. Likewise, numerical and between-tool stability may
-be interesting proxies for analysis accuracy, and perhaps useful in quality
-control.
+remains more empirical. Likewise, useful quality control metrics may be derived from numerical and between-tool stability.
 
@@
 For instance, SciPy's 2D spline interpolation was recently found to be
-precise up to t=10~bits~\cite{pytracer} and might therefore introduce
+precise up to t=10~bits~\cite{pytracer} \tristan{Fix ref} and might therefore introduce
 numerical perturbations leading to errors in the range of between-tool
@@
 Our results are limited by the type of numerical noise introduced in the
-analyses. Indeed, we only introduced noise in the outputs of elementary
+analyses. We only perturbed the outputs of elementary
 mathematical functions while numerical noise could creep in any
@@
 our replication. Numerical perturbations of 1 ulp are likely to have been
-introduced by our replication due to the use of Octave vs MATLAB for SPM
+introduced by our replication due to the use of GNU/Octave vs MATLAB for SPM
 and multithreading for AFNI. However, the group maps remained very similar

### 2021-12-07 paper/paper.tex
Biblio updates, add-ons to Dice analysis, inviting Camille and Alex as co-authors

@@
 
-\author{Ali Salari$^1$, Yohan Chatelain$^1$, [other co-authors], Gregory Kiar$^2$, Tristan Glatard$^1$ \\
+\author{Ali Salari$^1$, Yohan Chatelain$^1$, Alexander Bowring$^2$, Camille Maumet$^3$, Gregory Kiar$^4$, Tristan Glatard$^1$\\
+\vspace*{0.1cm}\\
 $^1$ Department of Computer-Science and Software Engineering, Concordia University, Montreal, Canada\\
-$^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
+$^2$ Li Ka Shing Centre for Health Information and Discovery, Nuffield Department of Population Health,\\ Big Data Institute, University of Oxford, Oxford, UK\\
+$^3$ Inria, Univ Rennes, CNRS, Inserm, IRISA UMR 6074, Empenn ERL U 1228, Rennes, France\\
+$^4$ Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
 

### 2021-12-07 paper/paper.tex
edits and suggestions

@@
 \newcommand{\discuss}[1]{\uwave{#1}}
+\newcommand{\gk}[1]{\color{purple}#1 \textbf{-GK}\color{black}\xspace}
 
-\title{Software variability in fMRI analysis:\\ comparing between-tool and numerical errors}
+\title{Comparing variability across fMRI analysis software packages and numerical errors}
 
@@
 
-Software variability broadly affects functional MRI analyses due to
-differences among analytical tools as well as numerical instabilities. However,
-the extent to which numerical and between-tool variabilities compare for a
+Variability has been broadly observed in functional MRI analyses across both
+differences in analytic tools and numerical instabilities. However,
+the relationship between numerical (within-tool) and between-tool variabilities for
 given analysis is unclear. We extended a previous comparison
-between fMRI analysis tools FSL, AFNI, and SPM, to measure numerical
-variability through Monte-Carlo arithmetic. We found that, in group analyses,
-between-tool variability was consistently larger than machine error,
-whereas in subject analyses, machine error approached between-tool
-variability in some cases. Furthermore, between-tool variability and
-machine error appeared moderately correlated in all tested conditions.
-Finally, we also found that numerical error at the precision of 17 bits --- a
-precision level found in commonly-used libraries --- had effects of similar
-magnitude \tristan{check that} than those of between-tool variability. Our findings motivate the
+of fMRI analysis software libraries (namely FSL, AFNI, and SPM) and relate the observed differences to the numerical
+variability observed using Monte-Carlo arithmetic. We found that
+between-tool variability was consistently larger than numerical variability in group-level analyses,
+whereas numerical variability approached between-tool variability in some subject-level analyses.
+Interestingly, between-tool variability and
+machine error appeared moderately correlated ($r > 0.5$) in all tested conditions.
+Finally, we found that numerical variability had effects of similar magnitude to between-tool
+variability when errors were introduced at the precision of 17 bits --- a
+precision level found in commonly-used libraries \gk{What does this mean? They only have precision of 17, or they use data that is 17 bits?}. Our findings motivate the
 continued investigation of numerical instability in neuroimaging, and position it 
-as a possible proxy for between-tool variations.
+as a possible proxy for studying arbitrary between-tool variations.
 \end{abstract}
@@
 software toolboxes --- such as FSL, AFNI and SPM --- when analyzing the same dataset
-using similar methods. Numerical variability, in contrast, denotes
+using similar methods \gk{this sentence says "two factors" but then only mentioned between tool. Also, it is too long}. Numerical variability, in contrast, denotes
 differences in outcomes of the same analytical toolbox
 executed in different environments – such as different operating systems or
-different hardware platforms. This manuscript investigates the extent to
+different hardware platforms \gk{you mention these two examples of numerical variability, but you use neither in this paper.
+Why not mention the one you use?}.
+This manuscript investigates the extent to
 which both types of variability relate to each other.
@@
 Numerical variability stems from errors introduced in floating point
-computations by numerical rounding, cancellation and absorption~\cite{muller2018handbook}. In
+computations by numerical rounding, cancellation, and absorption~\cite{muller2018handbook} \gk{only? What about poor conditioning + random effects + noise in data?}. In
 practice, the occurrence of such errors is affected by variations in
 hardware, software dependencies, compilation, parallelization, and most
-likely other factors. In general, the magnitude of such errors and their
+likely other factors \gk{what does "most likely other factors" mean?}. In the best case, the impact of such errors and the induced
 variations is in the range of 1 unit in the last place (ulp) --- also known
@@
 numerical perturbations larger than 3 ulps. Due to numerical instability,
-machine error may amplify during its propagation through the analysis,
-resulting in considerable loss of precision in final results. For instance, in fMRI,
-numerical variability produced by Linux updates was shown to result in Dice
+machine error may amplify during its propagation through analyses,
+resulting in considerable loss of precision in final results. In fMRI analysis,
+numerical variability produced by Linux updates has been shown to result in Dice
 coefficients ranging from 0.0 to 1.0 for ICA components produced by FSL
-MELODIC~\cite{Glatard2015}.
+MELODIC~\cite{Glatard2015} \gk{there isn't really context for what this result means, yet.
+Is this a lot?
+Dice hasn't been explained.
+Also, how are ICA components (weighted vectors) compared via Dice (a measure for binary image/vector comparison)?
+}.
 
 Between-tool variability is not a surprising concept: different programs
-executed on the same data may obviously produce different results. However,
+executed on the same data may obviously produce different results \gk{even when doing conceptually the same thing? Why? Why is this obvious?}. However,
 in fMRI analysis, programs all aim to estimate brain activity from measured
 variations in the BOLD signal, which is not expected to be measurably
-impacted by computational artifacts. Therefore, the observation reported
+impacted by computational artifacts \gk{Why wouldn't it be?
+Especially if you state that it isn't surprising for tools to lead to different results, how come you expect fMRI to not suffer from this?}.
+Therefore, the observation reported
 in~\cite{bowring2019exploring} that the three main fMRI analysis toolboxes
@@
 root-cause for between-tool variability depends on the analysis design and
-task paradigm. Further, the work in~\cite{Li2021.12.01.470790} found
+task paradigm \gk{If you state this finding, you need to unpack what it means a little bit.
+What part of analysis design?
+By task paradigm do you essentially mean the expected effect-size for the task that individuals are performing within the scanner?}.
+Further, the work in~\cite{Li2021.12.01.470790} found
 moderate agreement between results produced by five independent fMRI
 analysis pipelines and analyzed in details the components that led to these
-variations. Between-tool variability is supposedly an important determinant
+variations \gk{This sentence feels inconsistent and counter to the previous, and also doesn't tell us their findings; what components led to variations?}.
+Between-tool variability is supposedly an important determinant
 of the substantial analytical variability recently observed in
-fMRI~\cite{botvinik2020variability}.
+fMRI~\cite{botvinik2020variability} \gk{arguably, one of the larger issues that the NARPS result showed us was that people construct and test ``equivalent'' hypotheses differently, so despite highly similar data they will arrive at different conclusions}.
 
 We investigate the relationship between numerical and between-tool
-variability through two main questions: (1) how do both types of
-variability compare in magnitude, and (2) is there an association between
-them. The first question determines the extent to which each variability
-source may impact current fMRI results, and which one should be addressed
+variability through two main questions: (1) what is the relative magnitude of
+within-tool (numerical) variability and between-tool variability, and (2) is there an association between within- and between-tool variability.
+The first question determines the extent to which each variability
+source may impact current fMRI results, and which one should be addressed or leveraged
 in priority. The second question may provide deeper insights on the origins
@@
 reflect a single solution space shaped by local minima and
-ill-conditioning, which could be explored through numerical or software
+ill-conditioning \gk{this feels a bit clumsily worded, but I don't immediately have a rewrite that comes to mind }, which could be explored through numerical or software
 perturbations.
@@
 }
-\lstinputlisting[caption=Sample wrapper function (C code), label=algo:wrapper, style=customasm]{wrapper.c}
+\lstinputlisting[caption=Sample wrapper function (C code) \gk{I don't think we need this/it adds anything.
+Could go to a supplement if we want it in a paper somewhere}, label=algo:wrapper, style=customasm]{wrapper.c}
 
@@
 in~\cite{bowring2019exploring} were single-threaded. This was meant to
-reduce the time overhead resulting from Fuzzy Libmath instrumentation. All
+reduce the time overhead resulting from Fuzzy Libmath instrumentation \gk{Did we verify that single-threading generally didn't lead to different results than 7-threading?
+As in, were they all ostensibly sampled from the same random distribution?}.
+All
 the analyses were conducted on the CentOS 7.3 operating system. The
@@
  we encapsulated the
-above-mentioned software packages in Docker container images based on CentOS 7.3.
+above-mentioned software packages in Docker\gk{CC doesn't support Docker, so you mean Singularity?} container images based on CentOS 7.3.
 
-We measured numerical (within-tool -- WT) variability by running the same analyses three
+We measured numerical (within-tool; WT) variability by running the same analyses three
 times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
@@
 values were chosen such that the numerical perturbation simulates machine
-error. The resulting samples are equally plausible estimates of
+error. The resulting samples were equally plausible estimates of
 the true numerical result at the precision used by the pipelines. Moreover, to evaluate numerical perturbations at different magnitudes, 
@@
 We evaluated WT and BT variability for thresholded as well as unthresholded
-group-level and subject-level t-statistics maps, by computing the
-standard deviation of t-statistic maps across pipelines (BT) or Fuzzy Libmath samples (WT). For BT, we computed the standard deviation 
+group-level and subject-level t-statistics maps by computing the
+standard deviation of t-statistic maps across pipelines or Fuzzy Libmath samples, respectively. For BT, we computed the standard deviation 
 across a given pair of tools.
 For WT, we computed the standard deviation across the three
-Fuzzy Libmath samples of a given tool. Moreover, we computed WT variability for a pair of tools (A, B) as follows:
+Fuzzy Libmath samples of a given tool. We computed WT variability for a pair of tools (A, B) as follows:
 \begin{equation}
@@
 The scripts, Docker images, and data to reproduce the results are available
-in out GitHub repository at
+in our GitHub repository at
 \url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
 
-\subsection{Sanity check}
+\subsection{Validation of Replication}
 
@@
 in~\cite{bowring2019exploring}. For FSL, we found
-identical checksums. For SPM, the checksums were different but differences
+identical results. For SPM, the files (as measured by checksums) were different but differences
 were visually unnoticeable. For AFNI, the activation maps were similar
-overall, however, differences were more noticeable visually. 
-The observed differences remained small (see Supplemental Material~\ref{sec:supp-repro}) and might be due to the use of
-GNU/Octave vs MATLAB in SPM and of multithreading in AFNI. We performed visual quality control of the AFNI
+overall, however, differences were noticeable visually. 
+The observed differences remained small (see Supplemental Material~\ref{sec:supp-repro}), and might be due to the use of
+GNU/Octave vs MATLAB in SPM, and of multithreading in AFNI. We performed visual quality control of the AFNI
 and SPM results for each individual subject and confirmed that T1-weighted images were
@@
 
-\subsection{In the group analysis, BT variability was larger than and correlated with machine error}
+\subsection{In the group analysis, BT variability was larger than WT variability}
 
@@
 significantly larger than machine error in tool A or B, in both thresholded
-and unthresholded maps (Wilcoxon signed-rank test p~\textless~$10^{-162}$
-for all tests, t-test p=0 for all tests).
+and unthresholded maps (Wilcoxon signed-rank test p~\textless~$10^{-162}$ \gk{we don't have sufficient sample size to say that p is that small, so we should probably say less than $10^{-5}$ or something else we could actually arrive at with our number of repetitions, pipeline pairs, and samples.}
+for all tests, t-test p=0 \gk{similar comment re p value} for all tests).
 Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C} shows that
@@
 in [0.56, 0.58], p=0.0, Figure~\ref{fig:unthresh-maps}-\textbf{D}). Interestingly, the correlation 
-was driven by a set of voxels exhibiting comparable BT and
-WT values (located around the identity line in the XY plot), which, however, did not seem to have 
+appears driven by a set of voxels exhibiting comparable BT and
+WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have 
 any spatial consistency \tristan{Ali, check for intensity differences between these voxels and the other ones}.
@@
 
-  \subsection{In subject analyses, machine error approached BT variability in some regions}
+  \subsection{In subject analyses, WT variability approached BT variability in some regions}
 
@@
   BT variability was consistently larger than WT variability (Wilcoxon
-  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for
+  signed-rank test p~\textless~$10^{-160}$\gk{pval comment} for all tests, t-test p=0 for
   all tests). However, Figure~\ref{fig:unthresh-maps-sbj} shows that for
-  some subjects, machine error (WT variability) approached and even
+  some subjects, WT variability approached and even
   surpassed BT in some regions. As for the group maps, BT and WT
@@
   active regions for both BT and WT. Except in these regions, BT remained consistently larger
-  than WT. Moreover, to measure correlation between BT and WT, we
+  than WT \gk{what regions? This kind of came from nowhere}. Moreover, to measure correlation between BT and WT, we
   measured WT instability and BT instability in each region of the
-  HCP-MMP1.0 parcellation. The confusion matrices in
+  HCP-MMP1.0 parcellation \gk{again, it feels kind of abrupt and I'm not really sure what this section is getting at or how it differs from the previous based on these descriptions.
+Perhaps introduce that thresholding is common, but since it makes things discontinuous we study it through aparcellation, etc...}.
+The confusion matrices in
   Figure~\ref{fig:thresh-maps}-\textbf{D} report these instabilities for
@@
 
-In fMRI group analyses, machine error remains an order of magnitude smaller
-than between-tool variability. Group analyses have a regularization effect
-toward numerical noise, which is expected to amplify as sample size
-increases. Therefore, for fMRI studies with large sample sizes, machine
-error can safely be neglected with respect to between-tool variability. The
+In fMRI group analyses, within-tool variability remains an order of magnitude smaller
+than between-tool variability. Group analyses benefit from regularization
+of numerical noise, which is expected to increase as sample size
+increases. Therefore, for fMRI studies with large sample sizes, within-tool variability may be negligible with respect to between-tool variability. The
 recommendation made in~\cite{botvinik2020variability} to rely on
-``multiverse" analyses where multiple analysis tools are compared is
+``multiverse'' analyses where multiple analysis tools are compared is
 therefore likely to successfully correct for machine error in group
-studies. Nevertheless, machine error remains substantial in group analyses
+studies. Nevertheless, within-tool variability remains substantial in group analyses
 that are based on a single tool, as is commonly the case in current fMRI
@@
 
-In subject analyses, machine error and between-tool variabilty can become
+In subject-level analyses, within-tool and between-tool variabilty can become
 of comparable magnitude for some subjects in some regions. This observation
@@
 statistics were found to be substantially unstable at the subject-level
-while group distributions remained consistent.
+while group distributions remained consistent. \gk{this last sentence feels like it belongs in the previous paragraph, right before mentioning thresholding}
 
-For both group and subject analyses, between-tool variability and machine
-error were found to be moderately correlated. Even though between-tool
-variability and numerical variability are different in nature, this result
+For both group- and subject-level analyses, between-tool variability and within-tool
+variability were found to be moderately correlated. Even though between-tool
+variability and within-tool  variability are different in nature, this result
 suggests that in some cases both sources of variability may have a common
 cause that might be related to the conditioning of the BOLD signal
-estimation problem in a specific dataset. Therefore, in some regions,
+estimation problem \gk{I wouldn't necessarily say it's because of "BOLD signal estimation problem", just "algorithms used to process"} in a specific dataset. Therefore, in some regions,
 instabilities of similar magnitude may be triggered by small numerical

### 2021-12-09 paper/paper.tex
Address a few comments

@@
 in~\cite{bowring2019exploring} were single-threaded. This was meant to
-reduce the time overhead resulting from Fuzzy Libmath instrumentation \gk{Did we verify that single-threading generally didn't lead to different results than 7-threading?
-As in, were they all ostensibly sampled from the same random distribution?}.
-All
-the analyses were conducted on the CentOS 7.3 operating system. The
+reduce the time overhead resulting from Fuzzy Libmath instrumentation 
+\gk{Did we verify that single-threading generally didn't lead to different results than 7-threading? As in, were they all ostensibly sampled from the same random distribution?}. 
+\ali{We verified that multithreading leads to different results (e.g. single-threading vs, 7-threading). 
+However, single-threaded executions couldn't reproduce the original results.}
+All the analyses were conducted on the CentOS 7.3 operating system. The
 computations were performed on \href{https://www.computecanada.ca}{Compute
@@
  we encapsulated the
-above-mentioned software packages in Docker\gk{CC doesn't support Docker, so you mean Singularity?} container images based on CentOS 7.3.
+above-mentioned software packages in Docker container images based on CentOS 7.3.
+Although, we converted Docker containers to Singularity images to enable running on cluster nodes.
 
@@
 significantly larger than machine error in tool A or B, in both thresholded
-and unthresholded maps (Wilcoxon signed-rank test p~\textless~$10^{-162}$ \gk{we don't have sufficient sample size to say that p is that small, so we should probably say less than $10^{-5}$ or something else we could actually arrive at with our number of repetitions, pipeline pairs, and samples.}
-for all tests, t-test p=0 \gk{similar comment re p value} for all tests).
+and unthresholded maps (Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
+% \gk{we don't have sufficient sample size to say that p is that small,
+% so we should probably say less than $10^{-5}$ or something else we could actually
+% arrive at with our number of repetitions, pipeline pairs, and samples.}
+% for all tests, t-test p=0 \gk{similar comment re p value} for all tests).
 Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B},\textbf{C} shows that
@@
 WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have 
-any spatial consistency \tristan{Ali, check for intensity differences between these voxels and the other ones}.
+any spatial consistency.
 
@@
     \caption{Voxel-wise mean and standard deviation of BT and WT variability
-    in t-statistics maps. \tristan{add stats on subject-level thresholded maps}}
+    in t-statistics maps.}
     \label{table:pipeline-stats}
@@
   BT variability was consistently larger than WT variability (Wilcoxon
-  signed-rank test p~\textless~$10^{-160}$\gk{pval comment} for all tests, t-test p=0 for
-  all tests). However, Figure~\ref{fig:unthresh-maps-sbj} shows that for
+  signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
+  However, Figure~\ref{fig:unthresh-maps-sbj} shows that for
   some subjects, WT variability approached and even
@@
 and found that the virtual precision of t=17 bits minimized the RMSE
-between BT and WT in unthresholded group maps. Figure~\ref{fig:gnp-mni} shows BT
+between BT and WT in unthresholded group maps.
+FSL produced group maps with $\mu=0.325$ and $\sigma=0.287$ at this virtual precision,
+which indicates a bit lower variability compared to BT variability
+(Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$ for all tests).
+Figure~\ref{fig:gnp-mni} shows BT
 and WT in the corresponding group maps obtained at t=17 bits, showing that
 BT and WT reach comparable magnitudes in some regions. BT and WT remained
-moderately correlated at this precision. \tristan{In the text, add statistics similar to Table 2: is BT still larger than WT here?}
+moderately correlated at this precision.
 

### 2021-12-13 paper/paper.tex

@@
 \newcommand{\gk}[1]{\color{purple}#1 \textbf{-GK}\color{black}\xspace}
+\newcommand{\yohan}[1]{\color{cyan!75!black} \textbf{Yohan:} #1\color{black}\xspace}
+\newcommand{\yohanmod}[1]{\color{cyan!75!black} \sout{#1}\color{black}\xspace}
 
@@
 \begin{abstract}
-
   Variability has been broadly observed in functional MRI analyses across both
@@
   variability when errors were introduced at the precision of 17 bits --- a
-precision level found in commonly-used libraries \gk{What does this mean? They only have precision of 17, or they use data that is 17 bits?}. Our findings motivate the
+  precision level found in commonly-used libraries \gk{What does this mean?
+They only have precision of 17, or they use data that is 17 bits?}.
+\yohan{agree with Greg, it is unclear and a strong assertion!} Our findings motivate the
   continued investigation of numerical instability in neuroimaging, and position it
@@
 software toolboxes --- such as FSL, AFNI and SPM --- when analyzing the same dataset
-using similar methods \gk{this sentence says "two factors" but then only mentioned between tool. Also, it is too long}. Numerical variability, in contrast, denotes
+using similar methods \gk{this sentence says "two factors" but then only mentioned between tool.
+Also, it is too long}.
+\yohan{What do you mean by methods?
+Numerical schemes?
+If so, are we sure that theses tools are using the same numerical schemes?} Numerical variability, in contrast, denotes
 differences in outcomes of the same analytical toolbox
@@
 Numerical variability stems from errors introduced in floating point
-computations by numerical rounding, cancellation, and absorption~\cite{muller2018handbook} \gk{only? What about poor conditioning + random effects + noise in data?}. In
+computations by \yohanmod{numerical} rounding, cancellation, and absorption~\cite{muller2018handbook} \gk{only? What about poor conditioning + random effects + noise in data?}. In
 practice, the occurrence of such errors is affected by variations in
@@
 likely other factors \gk{what does "most likely other factors" mean?}. In the best case, the impact of such errors and the induced
-variations is in the range of 1 unit in the last place (ulp) --- also known
+variations is in the range of \yohanmod{1} \yohan{1/2 ulp for round-to-nearest} unit in the last place (ulp) --- also known
 as machine error, the difference between two successive floating-point
 numbers. However, when computations depend on imprecise libraries,
-numerical error may vary by several ulps. For instance, the numerical error
+numerical error may vary by several ulps. For instance, the \yohan{maximal} numerical error
 of the complementary error function (erfc) is larger than 3 ulps in several
 mathematical libraries~\cite{zimmermann:hal-03141101}, implying that an update of this function could introduce
-numerical perturbations larger than 3 ulps. Due to numerical instability,
-machine error may amplify during its propagation through analyses,
+numerical \yohanmod{perturbations} \yohan{differences} larger than 3 ulps. Due to numerical instability,
+machine error may amplify during its propagation through analyses \yohan{do you mean calculations?},
 resulting in considerable loss of precision in final results. In fMRI analysis,
@@
 Especially if you state that it isn't surprising for tools to lead to different results, how come you expect fMRI to not suffer from this?}.
-Therefore, the observation reported
+\yohan{+1} Therefore, the observation reported
 in~\cite{bowring2019exploring} that the three main fMRI analysis toolboxes
@@
     \hline
-
   \end{tabular}
@@
 Monte-Carlo arithmetic simulates numerical errors
-errors by introducing a controlled amount of noise in floating-point
+by introducing a controlled amount of noise in floating-point
 operations through the following perturbation~\cite{Parker1997-qq}:
@@
 error. The resulting samples were equally plausible estimates of
-the true numerical result at the precision used by the pipelines. Moreover, to evaluate numerical perturbations at different magnitudes, 
+the true \yohan{How can you assert that when you don't have ground truth?
+Would it be more safe to say "plausible estimates numerical solutions"?} numerical result at the precision used by the pipelines.
+Moreover, to evaluate numerical perturbations at different magnitudes,
 we repeated the FSL analyses for virtual
@@
 pair of tools (A, B) if for tool A or tool B it contained activated voxels only for some Fuzzy Libmath
-samples.
+samples. \yohan{A voxel is activated if its intensity is $>$ 0? If so, the given definition focuses on regions with low intensities while regions with high intensities may be more unstable}
 
@@
     \toprule
-        && \multicolumn{4}{c|}{Group map} & \multicolumn{2}{c}{Subject maps}\\
-        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded} \\
+                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
+    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
     % \cmidrule{3-8}
@@
 virtual precision of t=17~bits is interesting too. Indeed, while machine
-error generally introduces differences in the order of 1 ulp --- or
+error generally introduces differences in the order of \yohanmod{1} \yohan{1/2} ulp
+\yohan{Are we talking about one arithmetic operation? Or an entire execution?}
+--- or
 t=53~bits for double-precision values and t=24~bits for single-precision
-ones --- common scientific software dependencies introduce larger errors.
+ones \yohan{I would not mix virtual precision and error measurement}--- common scientific software dependencies introduce larger errors
+.
 For instance, SciPy's 2D spline interpolation was recently found to be
-precise up to t=10~bits~\cite{pytracer} \tristan{Fix ref} and might therefore introduce
+precise up to t=10~bits~\cite{pytracer} \tristan{Fix ref}
+\yohan{Same as previous, I would talk about significance or relative error, or remove the t= and not talk about virtual precision} and might therefore introduce
 numerical perturbations leading to errors in the range of between-tool
@@
 other software dependencies.
+\yohan{The sentence is ok, just a picky point: the SciPy result you cited describes the precision of the spline implementation while at the end you're talking differences due to updates.
+  The nuance is that two versions may have a similar precision and so when you udpate your
+  system, the difference between both versions is low but each version can be ill-conditionned.}
 
